### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
Loading JMC for g2 folder

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% On jet mass corrections and transversity
%% May 10, 2013
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[preprintnumbers,floatfix,nofootinbib]{revtex4}

\usepackage[tbtags]{amsmath}  % AMS math 
\usepackage{amssymb}          % AMS symbols
\usepackage{bm}               % bold math
\usepackage{graphicx}         % PostScript figures
\usepackage{hhline,multirow}  % for nicer tables
\usepackage{dcolumn}          % Align table columns on decimal point
\usepackage{slashed}
\usepackage{datetime}

%%%%%% for draft
\newcommand{\todo}[1]{\marginpar{$\bullet$}\textbf{#1}}

%%%%%%  Definitions   %%%%%%%%%%%

\newcommand{\Pslash}{P \hspace{-0.24cm} / \,}
\newcommand{\kslash}{k \hspace{-0.21cm} / \,}
\newcommand{\lslash}{l \hspace{-0.19cm} / \,}
\newcommand{\nslash}{n \hspace{-0.24cm} / \,}
\newcommand{\vslash}{v \hspace{-0.21cm} / \,}
\newcommand{\Sslash}{S \hspace{-0.22cm} / \,}
\newcommand{\Dslash}{D \hspace{-0.22cm} / \,}
\newcommand{\epsslash}{\varepsilon \hspace{-0.18cm} / \,}
\newcommand{\Tr}{\operatorname*{Tr}\nolimits} % Trace operator
\newcommand{\xbj}{x}                   % Bjorken variable
\newcommand{\de}{d}                    % differential
\newcommand{\ii}{i}                    % imaginary unit

%\newcommand{\mj}{\langle m_j \rangle}
%\newcommand{\mj}{M_q^\text{jet}}
\newcommand{\mj}{M_q}
\newcommand{\mjs}{\langle m_j^2 \rangle>}

\allowdisplaybreaks[2]

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%   TITLE    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\preprint{JLAB-THY-13-????}

\title{A novel chiral consedate contribution in inclusive deep inelastic scattering}

\author{Alberto~Accardi$^{a}$, Alessandro~Bacchetta$^{b}$} 
\affiliation{
$^a$Jefferson Lab, Newport News, VA 23606, USA, and
Hampton University, Hampton, VA 23668, USA \\
$^b$Dipartimento di Fisica, Universit\`a degli Studi di Pavia, and INFN,
Sez. di Pavia, 27100 Pavia, Italy
}

\date{\today, \currenttime}

\begin{abstract}

\end{abstract}

%\pacs{ }

%\keywords{ }

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Jet correlator and twist-2 structure functions}

Motivated by large-$x$ mass corrections to inclusive DIS structure functions, Accardi and Qiu have introduced in the LO handbag diagram a ``jet correlator'' that accounts for invariant mass production in the current jet, and ensures that leading twist calculations in collinear factorization are consistent with the requirement imposed by baryon number conservation that $x_B<1$ \cite{Accardi-Qiu}. The jet correlator is depicted in Figure~\ref{fig:handbags}(a) and is defined as
\begin{align} 
\Xi_{ij}(l,n_+) =\int
  \frac{\de^4\eta}{(2\pi)^4}\; e^{i l \cdot \eta}\,
    \langle 0|\, {\cal U}^{n_+}_{(+\infty,\eta)}
\,\psi_i(\eta)
             \bar{\psi}_j(0)\,
{\cal U}^{n_+}_{(0,+\infty)}\,   |0 \rangle \ ,
\label{e:xifull}
\end{align} 
In this definition, $l$ is the quark four-momentum, $\Psi$ the quark field operator, and $\|0\rangle$ is the nonperturbative vacuum. Furthermore, we explicitly guarantee the correlator's gauge invariance by introducing two Wilson line operators ${\cal U}^{n_+}$ along a light-cone plus direction determined by the vector $n_+$. This path choice for the Wilson line is required by QCD factorization theorems, and the vector will be determined by the particular hard process to which the jet correlator contributes. For example, in the case of inclusive DIS discussed in this paper, this is determined by the four momentum transfer $q$ and the proton's momentum $p$.

The correlator $\Xi$ can be parametrized in terms of scalar functions, using the vectors $l$ and $n_+$ 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 P \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ .
\label{e:jetexpansion}
\end{equation} 
Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes
only at twist-4 order, and will not be considered further in this paper. We
focus on the role of chiral odd terms in the $g_2$ structure function up to
twist 3.  At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
    + O(\Lambda/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the full quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one.

The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral representation of the cut quark propagator,
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -m_j^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it i.e.}, of the particles going through the cut in the top blob of Fig.\ref{fig:handabgs}(a), and the $J_i$ are the spectral functions of the quark propagator, that have been also called ``jet functions'' in \cite{Accardi-Qiu}. These satisfy \cite{D'Hoker-lecture-notes,Romao-lecture-notes}
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$. This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}. In this paper we limit our attention to effects of order $O(1/Q)$ and therefore can extend the integration to $\mu^2=\infty$. For example, the unpolarized DIS structure function $F_2$ reads
\begin{align}
  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(x_B(1+\mu^2/Q^2),Q^2)  \\
  & = \Big( \int_0^\infty d\mu^2\, J_2(\mu^2) \Big) F_2^{(0)}(x_B,Q^2) 
     + O(\Lambda^2/Q^2) \\
  & = F_2^{(0)}(x_B,Q^2)  + O(\Lambda^2/Q^2) \ ,
\label{eq:F2}
\end{align}
where $F_2^{(0)}$ is the structure function calculated with the handbag diagram sporting a bare quark propagator instead of the jet correlator.
At this order the jet function $J_2$ decouples and thanks to the sum rule \eqref{eq:jetfnsprops} it integrates to 1, so that one recovers the conventional result. The same holds true also for the helicity structure function $g_1$.
%
More in general, the jet correlator decouples from the parton correlator $\Phi$ in inclusive cross section calculation up to $O(1/Q)$, on which we are focusing the attention in this paper, and the inclusive structure functions depend on the integrated jet correlator
\begin{equation} 
  \Xi \equiv \int \frac{dl^2}{2l^-} d^2 l_T \, \Xi(l) 
    =  \frac{\Lambda}{2 l^-}\,\xi_1 {\bm 1}
    +  \xi_2 \frac{\nslash_-}{2} 
    + \text{higher\ twists}
    % +\frac{\Lambda^2}{4 (l^-)^2}\,\xi_3 \nslash_+
    % + i \frac{\Lambda}{2 l^-} \xi_4 
    % \frac{ \bigl[\nslash_-, \nslash_+ \bigr]}{2}.
\end{equation} 
where 
\begin{align}
\xi_1 &= \int d\mu^2 \frac{\mu}{\Lambda} J_1(\mu^2) 
       \equiv \frac{\mj}{\Lambda},
&
\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ .
% \\
% \xi_3 &= 0,
% &
% \xi_4 &= \int d\mu^2 \frac{\mu^2}{\Lambda^2} J_1(\mu^2) = \frac{\mjs}{\Lambda^2}.
\end{align} 
% The $\xi_1$ and $\xi_4$ have an interpretation as average invariant mass (and mass squared) of the current jet, and $l^-=q^- + O(1/Q)$ is imposed by 4-momentum conservation at the hard scattering vertex. The $\xi^4$ term contributes at order $O(1/Q^2)$ and is no further considered in this paper. 
It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < M_q < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of spectral functions we may expect \cite{Accardi-Qiu)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects. Taking into account that $J_1 < J_2$, we may therefore expect 
\begin{align}
  \label{eq:mjet}
  \mj = O(10-100 \text{ MeV}) \ .
\end{align}
Although $\mj$ is in general a nonperturbative quantity, it is interesting to
notice that  
\begin{align}
  \label{eq:xi2_chiral_cond}
  \mj = \frac{\Lambda}{4} \int \Tr \big[ \Xi(l) \bm 1] 
   = \langle 0 | \bar \psi_i(0) \psi_i(0) | 0 \rangle
\end{align}
% \todo{[AA] 2 issues here: (1) possible factors of 4. 
% (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.} 
Calculating this on the perturbative vacuum and limiting oneself to LO
corresponds to taking the trace of the cut bare-quark propagator to obtain 
$\mj = \,_{\text{pert}} \langle 0
|  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = m_q$, recovering the
conventional result. However, we are here considering non perturbative effects
on the quark fragmentation and $\mj \gtrsim m_q$. 
%very importantly, this
%quantity can be computed in lattice QCD. 
%\todo{[AA] Are qe sure that $\mj > m_q$??}
%\todo{[AA] Need to discuss connection to quark condensate and tensor charge.}

\section{Twist-3 analysis}

Extending the analysis of \cite{Accardi-Qiu} to the calculation of twist-3
structure functions requires not only to consider the $\xi_1$ term in the jet
correlator, but also quark-gluon-quark correlators in both the proton and the
vacuum as depicted in Figs.\ref{fig:handbags}(b) and (c), respectively. 
In the former the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up $O(1/Q)$
these give the same contribution as in the conventional handbag calculation.

The novel element in our analysis is the jet quark-gluon quark correlators
$\Xi_A^{\mu}(l,k)$ in diagrams \ref{fig:handbags}(c), 
\begin{equation} 
\begin{split} 
  \left(\Xi_A^{\mu} \right)_{ij} &=
   \frac{1}{2}\, \sum_X \int \frac{\de \eta^+\, \de^2 \bm{\eta}_T}{(2\pi)^{3}}\;
   e^{\ii k \cdot \eta}\,
   \langle 0|\,
   {\cal U}^{n_+}_{(+\infty,\eta)}\,
   g A^{\mu}(\eta)\,
   \,\psi_i(\eta)|X\rangle
   \langle X|
             \bar{\psi}_j(0)\,
   {\cal U}^{n_+}_{(0,+\infty)}
   |0\rangle \bigg|_{\eta^-=0} .
\label{e:xi_A}
\end{split} 
\end{equation}  
These diagrams are not only important to account for all contribution of order $O(1/Q)$, but also in restoring up to twist-3 the gauge invariance broken in diagram \ref{fig:handbags}(a) by the different mass of the incoming and outgoing quark lines, namely, $m_q \neq \mj$.

Rather than directly using the definition \eqref{e:xi_A}, it is convenient to calculate the inclusive cross section as an integral of the semi-inclusive one, utilize the QCD equation of motions and furthermore summed over all hadron flavors, and take advantage of 
\begin{align}
  \label{eq:SIDIS_to_DIS}
  \sum_h \int \frac{d^3p_h}{(2\pi)2E_h} \Delta^h(l,p_h) = \Xi(l) \ , 
\end{align}
where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{New_testament}. 
% As we shall see, an analogous formula for quark-gluon-quark correlators is not needed.
The $\xi_1$ term is chiral-odd and therefore can appear in the inclusive cross section only coupled to the transversity function $h_1$. Therefore, for our analysis the relevant part of the semi-inclusive hadronic tensor is 
\todo{[AA] I am using the notation in Piet Mulder's lecture notes - this will need to be checked. Decide also if we want this at parton or charge-weighted level.}
\begin{align}
  \label{eq:Wsidis_ini}
  2 \Lambda \sum_h \int dz d^2p_{hT} = i \frac{2\Lambda}{Q} 
    \hat t^{[\mu} \epsilon_\perp^{\nu]\rho}S_{\perp\rho} 
    \Big[ 2 x_b g_T(x_B) \sum_h \int dz d^2p_{hT} D_1^h(z)
    + 2 h_1(x_B) \sum_h \int dz d^2p_{hT} \tilde E^h(z) \Big] + \ldots
\end{align}
where $D_1^h$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$, and $\tilde E^h$ is a twist-3 function defined in \cite{New-testament}. The former can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS}:
\begin{align}
  \sum_h \int dz d^2p_{hT} z D_1^h(z) = \xi_2 = 1 \ .
\end{align}
To integrate the latter, we first make use of the relation \cite{New-testament}
$\tilde E(z) = E(z) - m_q z D_1(z)$, which is a consequence of the QCD equations of motion, so that 
\begin{align}
  \sum_h \int dz d^2p_{hT} \tilde E(z) 
    = \sum_h \int dz d^2p_{hT} \Big[ E(z) - \frac{m_q}{\Lambda} z D_1z \Big]
    = \xi_1 - \frac{m_q}{\Lambda} \xi_2 = \frac{\mj - m_q}{\Lambda} \ .
\end{align}
This formula is the single most important result of this paper.

Finally, with suitable projections of the hadronic tensor, the inclusive cross section up to order $M/Q$ turns out to be
\begin{align}
\frac{d\sigma}{d\xbj \, dy\, d\psi}
%&
=
\frac{2 \alpha^2}{\xbj y Q^2}\,
\frac{y^2}{2\,(1-\varepsilon)}\, 
\biggl\{
&F_{UU ,T} + \varepsilon F_{UU ,L}
+ S_\parallel \lambda_e\,
  \sqrt{1-\varepsilon^2}\; 
F_{LL}
%\nonumber 
\\  
&
+ |\bm{S}_\perp| \lambda_e\, \sqrt{2\,\varepsilon (1-\varepsilon)}\, 
  \cos\phi_S\, 
F_{LT}^{\cos \phi_S}
 \biggr\},
\label{e:crossdis}
\end{align}
where the structure functions on the right hand side are defined as
\begin{align}
F_{UU ,T} &= \xbj\,\sum_a e_a^2\,f_1^a(\xbj),
\\
F_{UU ,L} &= 0,
\\
F_{LL} &=\xbj\,\sum_a e_a^2\,g_1^a(\xbj),
\\
F_{UT}^{\sin \phi_S}&=0,
\label{e:FUTint}
\\
F_{LT}^{\cos \phi_S}&=-\xbj\,\sum_a e_a^2\, \frac{2\Lambda}{Q}\,
\biggl(\xbj  g_T^a(\xbj)
   + \frac{\mj -m_q}{\Lambda} \, h_{1}^a(\xbj) \biggr).
\label{e:FLTint}
\end{align}
The second term in the last struture function is a new result from our
analysis; it is not suppressed as an inverse power of $Q$, and therefore
survives even in the Bjorken limit. Note that calculating the jet correlator
on the perturbative vacuum one would obtain, as already discussed, $\mj=m_q$
and the new term vanishes as it should. However, on the non-perturbative
vacuum the jet mass is larger than the quark's, and this contributes a
non-negligible term to the twist-3 part of the $g_2$ function, as we shall
discuss in the next section.

\section{The $g_2$ structure function}

The new term in Eq.{e:FLTint} only appeears in the $g_2$ structure function. Following the derivation in Ref.~\cite{ABMS}, one finds
\begin{align}
\label{e:g2}
  g_2(x_B) = g_2^{WW} + \frac{1}{2}\,\sum_a e_a^2
\biggl(
    \widetilde g_T^{a \star}(x) 
    + \int_x^1\frac{dy}{y} \widehat{g}_T^a(y) 
    + \frac{m_q}{M} (h_1^a/x)^\star(x) 
    + \frac{\mj-m_q}{M} h_1^a(x) 
\Biggr) \ ,
\end{align}
where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$. The first 4
terms coincide with the result obtained in the conventional handbag
approximation \cite{ABMS}, while the fifth is new.

The first term is also known as the Wandzura-Wilczeck function $g_2^{WW} =
g_1^*(x)$ , and contains all the ``pure twist-2'' chiral even contributions to
the $g_2$ structure coming from quark-quark correlators. The second and third
terms contain all ``pure twist-3'' contributions, i.e., those coming from
quark-gluon-quark correlators. The fourth and fifth terms depend on the
transversity parton distribution function, $h_1$. 
The former is usually neglected for
light quarks since it is proportional to $m_q=O$(1 MeV). In the latter term,
new in our analysis, the transversity distribution is multiplied by a constant
of $O$(100 MeV), and cannot be a priori neglected.

To estimate the size of the last two terms in Eq.~\eqref{e:g2}, 
we use a recent parametrization of the transversity distribution from
Ref.~\cite{Radici:2015mwa}, which is comparable also to other
extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. We define the shorthand
notation
\begin{align}
g_2^{\text{quark}} &= \frac{1}{2}\,\sum_a e_a^2 
 \frac{m_q}{M} (h_1^a/x)^\star(x),
&
g_2^{\text{jet}} &= \frac{1}{2}\,\sum_a e_a^2 
\frac{\mj-m_q}{M} h_1^a(x). 
\end{align} 
We choose the values of the mass parameters to be $m_q=5$ MeV and 
$\mj = 50$ MeV.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=8cm]{g2contrib}
\caption{\label{f:g2contrib} 
Different contributions to the $g_2$ structure function. 
}
\end{center}
\end{figure}

\begin{itemize}
\item large-$x$: bridges Braun's pure twist-3 theory and the data
\item samller-$x$: consttrains the small-$x$ behavior of transversity.
\end{itemize}

Another consequence of the new chiral odd term induced by the non-vanishing of
the chiral condensate on the non perturbative vacuum is that the
Burkardt-Cottingham sum rule is broken: 
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \frac{\mj-m_q}{\Lambda} \int dx\, h_1(x) \ ,
\end{align}
where the integral over $h_1$ is related to target's tensor charge.
Consequences:
\begin{itemize}
\item Inclusive DIS become sensitive to the tensor charge; furthermore, teh BC summ rule isolates the effects due to the chiral odd part of the jet correlator. 
\item Both the jet mass $\mj$ and the tensor charge can in principle be calculated on the lattice
\item Comparison to the Burkhardt-Cottingham sum rule can provide experimental verification of lattice calculation
\item in turn these can be used to determine the size of the $h_1$ term in $g_2-g_2^{WW}$ and allow an eperimental extraction of the pure twist-3 terms.
\end{itemize}

It is important to explore in which other process does $\mj$ contribute, as to provide an experimental check of the formalism:
\begin{itemize}
\item inclusive $\Lambda$ production in $e^+ + e^-$
\item same-side dihadrons in $e^+ + e^-$ 
\end{itemize}
\todo{It would be cool to find a process where the $\mj$ contribution is th eonly one (similar to the BC breaking) ...}

\section{Conclusions}

\noindent
------------------------------------------------- \\
Edited down to here\\
--------------------------------------------------\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% ACKNOWLEDGMENTS %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{acknowledgments}
This work was supported by DOE contract No. DE-AC05-06OR23177,
under which Jefferson Science Associates, LLC operates Jefferson Lab, by the DOE contract DE-SC008791 and 
by the Joint Research Activity ``Study of Strongly
Interacting Matter'' (acronym HadronPhysics3, Grant Agreement No. 283286) under
the 7th Framework Programme of the European Community.
\end{acknowledgments}

\bibliographystyle{myrevtex}
\bibliography{mybiblio}

\end{document}

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
New title
Started reviewing typos, and other small things - figure added

@@
 \usepackage{graphicx}         % PostScript figures
+\usepackage[export]{adjustbox}% to align images
 \usepackage{hhline,multirow}  % for nicer tables
@@
 \usepackage{datetime}
+\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
 
@@
 \newcommand{\todo}[1]{\marginpar{$\bullet$}\textbf{#1}}
+\def\AAcom#1{{\bf  \textcolor{Red}{[AA: {#1}]}}}
+\def\AAmod#1{{\textcolor{Green}{#1}}}
 
@@
 
-\title{A novel chiral consedate contribution in inclusive deep inelastic scattering}
+\title{Accessing the nucleon tensor structure in inclusive deep inelastic scattering}
 
@@
 
+\begin{figure*}
+  \centering
+  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0}
+  \hfill
+  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
+  \hfill
+  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
+  \caption{Diagrams contributing to DIS scattering up to twist-3 expansion, including a jet correlator in the top part.
+Note the gluon attaches to both the nucleon and jet correlators.
+The Hermitian conjugates of diagrams (b) and (c), i.e., with gluons attaching to the right of the cut, are not shown.
+  }
+  \label{fig:handbags}
+\end{figure*}
+
 The correlator $\Xi$ can be parametrized in terms of scalar functions, using the vectors $l$ and $n_+$ 
@@
   \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
-    + O(\Lambda/Q^2)
+    + O(\Lambda^2/Q^2)
 \label{e:jetexpansion-tw3}
@@
   \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
-  \delta(l^2 -m_j^2) \ ,
+  \delta(l^2 -\mu_j^2) \ ,
 \label{e:jetspectral}
@@
 When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$.
-This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}.
-In this paper we limit our attention to effects of order $O(1/Q)$ and therefore can extend the integration to $\mu^2=\infty$.
-For example, the unpolarized DIS structure function $F_2$ reads
+This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}; for example,
+teh structure function $F_2$ reads
 \begin{align}
-  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(x_B(1+\mu^2/Q^2),Q^2)  \\
-  & = \Big( \int_0^\infty d\mu^2\, J_2(\mu^2) \Big) F_2^{(0)}(x_B,Q^2) 
-     + O(\Lambda^2/Q^2) \\
-  & = F_2^{(0)}(x_B,Q^2)  + O(\Lambda^2/Q^2) \ ,
+  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(x_B(1+\mu^2/Q^2),Q^2) \ ,
 \label{eq:F2}
 \end{align}
-where $F_2^{(0)}$ is the structure function calculated with the handbag diagram sporting a bare quark propagator instead of the jet correlator.
-At this order the jet function $J_2$ decouples and thanks to the sum rule \eqref{eq:jetfnsprops} it integrates to 1, so that one recovers the conventional result.
+where $F_2^{(0)}$ is the structure function calculated with the handbag diagram sporting a bare quark propagator instead of the jet correlator, and $\xi=2x_B/(1+\sqrt{1+4x_B^2M^2/Q^2})$ with $M$ the nucleon's mass is the Nachtmann scaling variable.
+In this paper we limit our attention to effects of order $O(1/Q)$ and therefore can extend the integration to $\mu^2=\infty$.
+Therefore jet function $J_2$ decouples, and thanks to the sum rule \eqref{eq:jetfnsprops} integrates to 1.
+One then recovers the conventional result.
+\begin{align}
+  F_2(x_B) = \Big[ \int_0^\infty d\mu^2\, J_2(\mu^2) \Big] F_2^{(0)}(x_B,Q^2) 
+     + O(\Lambda^2/Q^2) = F_2^{(0)}(x_B,Q^2)  + O(\Lambda^2/Q^2) \ .
+\end{align}
 The same holds true also for the helicity structure function $g_1$.
 %
-More in general, the jet correlator decouples from the parton correlator $\Phi$ in inclusive cross section calculation up to $O(1/Q)$, on which we are focusing the attention in this paper, and the inclusive structure functions depend on the integrated jet correlator
+More in general, the jet correlator decouples from the parton correlator $\Phi$ in any inclusive cross section calculation up to $O(1/Q)$, and the inclusive structure functions only depend on the integrated jet correlator
 \begin{equation} 
-  \Xi \equiv \int \frac{dl^2}{2l^-} d^2 l_T \, \Xi(l) 
+  \Xi(l^-) \equiv \int \frac{dl^2}{2l^-} d^2 l_T \, \Xi(l) 
     =  \frac{\Lambda}{2 l^-}\,\xi_1 {\bm 1}
@@
 \end{equation} 
+\AAcom{We need to discuss what happens to the B functions!! See e-mail from Jul 7th, 2015, for ideas.}
 where 

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
Intro e Acknowledgements

--- 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 \section{Introduction}
+
+The nucleon tensor charge is a fundamental property of the nucleon that is at
+the moment poorly constrained. There are several estimates based on lattice
+QCD, but only a few estimates based on extractions from data. The main problem
 
@@
 under which Jefferson Science Associates, LLC operates Jefferson Lab, by the DOE contract DE-SC008791 and 
-by the Joint Research Activity ``Study of Strongly
-Interacting Matter'' (acronym HadronPhysics3, Grant Agreement No. 283286) under
-the 7th Framework Programme of the European Community.
+by the European Research Council (ERC) under the European Union's 
+Horizon 2020 research and innovation programme (grant agreement No. 647981,
+3DSPIN)
 \end{acknowledgments}

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
Working on Section III

--- 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
@@
   \hfill
-  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
+  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
   \hfill
-  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
+  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
   \caption{Diagrams contributing to DIS scattering up to twist-3 expansion, including a jet correlator in the top part.
@@
 
-The novel element in our analysis is the jet quark-gluon quark correlators
+The novel element in our analysis is the jet's quark-gluon-quark correlator
 $\Xi_A^{\mu}(l,k)$ in diagrams \ref{fig:handbags}(c), 
@@
 \end{equation}  
-These diagrams are not only important to account for all contribution of order $O(1/Q)$, but also in restoring up to twist-3 the gauge invariance broken in diagram \ref{fig:handbags}(a) by the different mass of the incoming and outgoing quark lines, namely, $m_q \neq \mj$.
+This diagram and its hermitian conugate are not only important to account for all contribution of order $O(1/Q)$, but also in restoring up to twist-3 the gauge invariance broken in diagram \ref{fig:handbags}(a) by the different mass of the incoming and outgoing quark lines, namely, $m_q \neq \mj$.
 
@@
 where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{New_testament}.
+In terms of the TMD fragmentation functions we are interested in, this reads
+\begin{align}
+  \label{eq:SIDIS_to_DIS_TMDlevel}
+  \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
+  \sum_h \int dz d^2p_{hT} E(z,p_{hT}) & = \xi_1 \ ,
+\end{align}
+where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$ and transverse momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function defined in \cite{New-testament}.
+
 % As we shall see, an analogous formula for quark-gluon-quark correlators is not needed.
-The $\xi_1$ term is chiral-odd and therefore can appear in the inclusive cross section only coupled to the transversity function $h_1$.
-Therefore, for our analysis the relevant part of the semi-inclusive hadronic tensor is
+%The $\xi_1$ term is chiral-odd and therefore can appear in the inclusive cross section only coupled to the transversity function $h_1$. Therefore, for our analysis 
+The relevant part of the semi-inclusive hadronic tensor for our analysis is 
 \todo{[AA] I am using the notation in Piet Mulder's lecture notes - this will need to be checked. Decide also if we want this at parton or charge-weighted level.}
@@
   \label{eq:Wsidis_ini}
-  2 \Lambda \sum_h \int dz d^2p_{hT} = i \frac{2\Lambda}{Q} 
+  2 \Lambda \sum_h \int dz d^2p_{hT} W^{\mu\nu}_{\text{SIDIS}}(z,p_{hT}) 
+    & = i \frac{2\Lambda}{Q} 
     \hat t^{[\mu} \epsilon_\perp^{\nu]\rho}S_{\perp\rho} 
-    \Big[ 2 x_b g_T(x_B) \sum_h \int dz d^2p_{hT} D_1^h(z)
-    + 2 h_1(x_B) \sum_h \int dz d^2p_{hT} \tilde E^h(z) \Big] + \ldots
+    \Big[ 2 x_b g_T(x_B) \sum_h \int dz d^2p_{hT} D_1^h(z,p_{hT}) \\
+  & + 2 h_1(x_B,p_{hT}) \sum_h \int dz d^2p_{hT} \tilde E^h(z,p_{hT}) \Big] + \ldots
 \end{align}
-where $D_1^h$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$, and $\tilde E^h$ is a twist-3 function defined in \cite{New-testament}.
-The former can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS}:
+The first term can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS_TMDlevel}.
+To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (m_q/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{New-testament}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
 \begin{align}
-  \sum_h \int dz d^2p_{hT} z D_1^h(z) = \xi_2 = 1 \ .
-\end{align}
-To integrate the latter, we first make use of the relation \cite{New-testament}
-$\tilde E(z) = E(z) - m_q z D_1(z)$, which is a consequence of the QCD equations of motion, so that 
-\begin{align}
-  \sum_h \int dz d^2p_{hT} \tilde E(z) 
-    = \sum_h \int dz d^2p_{hT} \Big[ E(z) - \frac{m_q}{\Lambda} z D_1z \Big]
+  \sum_h \int dz d^2p_{hT} \tilde E(z,p_{hT}) 
+    = \sum_h \int dz d^2p_{hT} \Big[ E(z,p_{hT}) - \frac{m_q}{\Lambda} z D_1(z,p_{hT}) \Big]
     = \xi_1 - \frac{m_q}{\Lambda} \xi_2 = \frac{\mj - m_q}{\Lambda} \ .
@@
 
-Finally, with suitable projections of the hadronic tensor, the inclusive cross section up to order $M/Q$ turns out to be
+Finally, with suitable projections of the hadronic tensor, the inclusive cross section up to order $M/Q$ can be written as
 \begin{align}
@@
 F_{LT}^{\cos \phi_S}
- \biggr\},
+ \biggr\} \ ,
 \label{e:crossdis}
@@
 \end{align}
-The second term in the last struture function is a new result from our
+The second term in the last structure function is a new result from our
 analysis; it is not suppressed as an inverse power of $Q$, and therefore
@@
 on the perturbative vacuum one would obtain, as already discussed, $\mj=m_q$
-and the new term vanishes as it should. However, on the non-perturbative
+and the new term wouls vanishe, as it should. However, on the non-perturbative
 vacuum the jet mass is larger than the quark's, and this contributes a

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
smaller corrections

@@
 
-The new term in Eq.{e:FLTint} only appeears in the $g_2$ structure function. Following the derivation in Ref.~\cite{ABMS}, one finds
+The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function. Following the derivation in Ref.~\cite{ABMS}, one finds
 \begin{align}
@@
 \caption{\label{f:g2contrib} 
-Different contributions to the $g_2$ structure function. 
+Different contributions to the non Wandzura-Wilczek part of the $g_2$ structure function compared to the JAM15 fit of $g_2-g_2^{\text{WW}}$ \cite{JAM15}.
 }
@@
 \item large-$x$: bridges Braun's pure twist-3 theory and the data
-\item samller-$x$: consttrains the small-$x$ behavior of transversity.
+\item smaller-$x$: constrains the small-$x$ behavior of transversity.
+\item in general, $g_2^{\text{quark}}$ is quite smaller than the other contribution, as customarily assumed.
 \end{itemize}

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
Some introduction

--- 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 
-The nucleon tensor charge is a fundamental property of the nucleon that is at
-the moment poorly constrained. There are several estimates based on lattice
-QCD, but only a few estimates based on extractions from data. The main problem
+The nucleon tensor charge is a fundamental property of the nucleon and is at
+present poorly constrained. Several estimates based on lattice
+QCD are available, but only limited information from direct measurements. The
+way to extract the tensor charge from experimental measurements requires first
+the extraction the so-called transversity parton distribution function (PDF),
+denoted by $h_1^q(x)$. The transversity distribution is then integrated over
+$x$ to yield the contribution of flavor $q$ to tensor charge.
+
+In this paper, we discuss the possibility of observing the effect of
+the transversity distribution in totally inclusive Deep Inelastic Scattering.
+
+The transversity distribution is notoriously difficult to access because it is
+a chiral-odd function and needs to be combined with a spin-flip mechanism to
+appear in a scattering process. Usually, this spin flip is provided by another
+nonperturbative distribution or fragmentation function, implying that
+transversity cannot be accessed in inclusive DIS,
+but only in more complex processes such as semi-inclusive DIS or Drell-Yan.
+
+The only other way to attain spin-flip terms in QED and QCD is taking into
+account mass corrections. In fact, it is well known that transversity gives a
+contribution to the structure function $g_2$ in inclusive DIS, and in
+particular to the violation of the so-called Wandzura--Wilczek relation for
+$g_2$. However, this contribution is proportional to the current quark mass
+and can be expected to be very small.
+
+We revisit the standard analysis of inclusive DIS taking into account the fact
+that on-shell quarks cannot be present in the final state, but they rather
+decay into hadrons (ideally, the form jets of hadrons). This is sufficient to modify the structure of the DIS
+cut-diagram, even if none of the hadrons is detected in the final
+state. For a proper description of this effect, we include ``jet
+correlators'' into the analysis. We pay particular attention to insuring that our
+results are gauge invariant. We observe that the inclusion of jet correlators
+introduces a new
+contribution to the inclusive $g_2$ structure function. This term has the
+interesting features that: a) violates the Wandzura--Wilczek relation, b)
+violates the Burkhardt--Cottingham sum rule, c) is
+proportional to the transversity distribution function multiplied by a
+nonperturbative ``jet mass'' parameter. We provide estimates of this
+contribution based on a recent extraction of transversity and show that it
+could be very large.
 

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex

--- 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 \section{Introduction}
+
+The nucleon tensor charge is a fundamental property of the nucleon and is at
+present poorly constrained. Several estimates based on lattice
+QCD are available, but only limited information from direct measurements. The
+way to extract the tensor charge from experimental measurements requires first
+the extraction the so-called transversity parton distribution function (PDF),
+denoted by $h_1^q(x)$. The transversity distribution is then integrated over
+$x$ to yield the contribution of flavor $q$ to tensor charge.
+
+In this paper, we discuss the possibility of observing the effect of
+the transversity distribution in totally inclusive Deep Inelastic Scattering.
+
+The transversity distribution is notoriously difficult to access because it is
+a chiral-odd function and needs to be combined with a spin-flip mechanism to
+appear in a scattering process. Usually, this spin flip is provided by another
+nonperturbative distribution or fragmentation function, implying that
+transversity cannot be accessed in inclusive DIS,
+but only in more complex processes such as semi-inclusive DIS or Drell-Yan.
+
+The only other way to attain spin-flip terms in QED and QCD is taking into
+account mass corrections. In fact, it is well known that transversity gives a
+contribution to the structure function $g_2$ in inclusive DIS, and in
+particular to the violation of the so-called Wandzura--Wilczek relation for
+$g_2$. However, this contribution is proportional to the current quark mass
+and can be expected to be very small.
+
+We revisit the standard analysis of inclusive DIS taking into account the fact
+that on-shell quarks cannot be present in the final state, but they rather
+decay into hadrons (ideally, the form jets of hadrons). This is sufficient to modify the structure of the DIS
+cut-diagram, even if none of the hadrons is detected in the final
+state. For a proper description of this effect, we include ``jet
+correlators'' into the analysis. We pay particular attention to insuring that our
+results are gauge invariant. We observe that the inclusion of jet correlators
+introduces a new
+contribution to the inclusive $g_2$ structure function. This term has the
+interesting features that: a) violates the Wandzura--Wilczek relation, b)
+violates the Burkhardt--Cottingham sum rule, c) is
+proportional to the transversity distribution function multiplied by a
+nonperturbative ``jet mass'' parameter. We provide estimates of this
+contribution based on a recent extraction of transversity and show that it
+could be very large.
 

### 2016-07-20 1607 - JMC for g2/Paper/JMC_dis.tex
Fixed notations, other small work on text

@@
 \newcommand{\mj}{M_q}
+\newcommand{\mq}{m_q}
 \newcommand{\mjs}{\langle m_j^2 \rangle>}
@@
 
-\preprint{JLAB-THY-13-????}
+\preprint{JLAB-THY-16-????}
 
@@
 
-\date{\today, \currenttime}
+\date{\bf \today, \currenttime}
 
@@
 \end{align} 
-In this definition, $l$ is the quark four-momentum, $\Psi$ the quark field operator, and $\|0\rangle$ is the nonperturbative vacuum.
+In this definition, $l$ is the quark four-momentum, $\Psi$ the quark field operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is the nonperturbative vacuum state.
 Furthermore, we explicitly guarantee the correlator's gauge invariance by introducing two Wilson line operators ${\cal U}^{n_+}$ along a light-cone plus direction determined by the vector $n_+$.
-This path choice for the Wilson line is required by QCD factorization theorems, and the vector will be determined by the particular hard process to which the jet correlator contributes.
+This path choice for the Wilson line is required by QCD factorization theorems, and the vector is determined by the particular hard process to which the jet correlator contributes.
 For example, in the case of inclusive DIS discussed in this paper, this is determined by the four momentum transfer $q$ and the proton's momentum $p$.
 
-\begin{figure*}
+The correlator $\Xi$ can be parametrized in terms of scalar functions, using the vectors $l$ and $n_+$: 
+\begin{equation}
+\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
++ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
++ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ .
+\label{e:jetexpansion}
+\end{equation} 
+Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes
+only at twist-4 order, and will not be considered further in this paper. We
+focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3. At this order, 
+\begin{equation}
+  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+    + O(\Lambda^2/Q^2)
+\label{e:jetexpansion-tw3}
+\end{equation} 
+is nothing else than the full quark propagator; note however, that we consider
+here the full QCD vacuum rather than the perturbative one.  
+The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral representation of the cut quark propagator \cite{D'Hoker-lecture-notes,Romao-lecture-notes},
+\begin{align} 
+  \Xi(l) =  
+  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
+  \delta(l^2 -\mu_j^2) \ ,
+\label{e:jetspectral}
+\end{align}
+where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it i.e.}, of the particles going through the cut in the top blob of Fig.\ref{fig:handbags}(a), and the $J_i$ are the spectral functions of the quark propagator, that have been also called ``jet functions'' in \cite{Accardi-Qiu,Collins-book?,SCET?}.
+These satisfy
+\begin{align}
+  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
+  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
+  \int d\mu^2 J_2(\mu^2) = 1 \ .
+\label{eq:jetfnsprops}
+\end{align}
+From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
+\begin{align}
+  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
+  \label{eq:jet_vs_spectral}
+\end{align}
+
+\begin{figure*}[bt]
   \centering
@@
 
-The correlator $\Xi$ can be parametrized in terms of scalar functions, using the vectors $l$ and $n_+$ 
-\begin{equation}
-\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
-+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
-+ \frac{i \Lambda}{2 P \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ .
-\label{e:jetexpansion}
-\end{equation} 
-Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes
-only at twist-4 order, and will not be considered further in this paper. We
-focus on the role of chiral odd terms in the $g_2$ structure function up to
-twist 3.  At this order, 
-\begin{equation}
-  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
-    + O(\Lambda^2/Q^2)
-\label{e:jetexpansion-tw3}
-\end{equation} 
-is nothing else than the full quark propagator; note however, that we consider
-here the full QCD vacuum rather than the perturbative one.
-
-The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral representation of the cut quark propagator,
+When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$.
+This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}:
 \begin{align}
-  \Xi(l) =  
-  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
-  \delta(l^2 -\mu_j^2) \ ,
-\label{e:jetspectral}
-\end{align}
-where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it i.e.}, of the particles going through the cut in the top blob of Fig.\ref{fig:handabgs}(a), and the $J_i$ are the spectral functions of the quark propagator, that have been also called ``jet functions'' in \cite{Accardi-Qiu}.
-These satisfy \cite{D'Hoker-lecture-notes,Romao-lecture-notes}
-\begin{align}
-  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
-  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
-  \int d\mu^2 J_2(\mu^2) = 1 \ .
-\label{eq:jetfnsprops}
-\end{align}
-From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
-\begin{align}
-  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
-  \label{eq:jet_vs_spectral}
-\end{align}
-
-When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$.
-This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}; for example,
-teh structure function $F_2$ reads
-\begin{align}
-  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(x_B(1+\mu^2/Q^2),Q^2) \ ,
+  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(x_B(1+\mu^2/Q^2)) \ ,
 \label{eq:F2}
@@
 where $F_2^{(0)}$ is the structure function calculated with the handbag diagram sporting a bare quark propagator instead of the jet correlator, and $\xi=2x_B/(1+\sqrt{1+4x_B^2M^2/Q^2})$ with $M$ the nucleon's mass is the Nachtmann scaling variable.
+(We also omitted the dependence of the structure function on $Q^2$ for clarity of notation).
 In this paper we limit our attention to effects of order $O(1/Q)$ and therefore can extend the integration to $\mu^2=\infty$.
-Therefore jet function $J_2$ decouples, and thanks to the sum rule \eqref{eq:jetfnsprops} integrates to 1.
-One then recovers the conventional result.
+Therefore, the jet function $J_2$ decouples and, thanks to the sum rule \eqref{eq:jetfnsprops}, integrates to 1.
+One then recovers the conventional result,
 \begin{align}
-  F_2(x_B) = \Big[ \int_0^\infty d\mu^2\, J_2(\mu^2) \Big] F_2^{(0)}(x_B,Q^2) 
-     + O(\Lambda^2/Q^2) = F_2^{(0)}(x_B,Q^2)  + O(\Lambda^2/Q^2) \ .
+  F_2(x_B) = \Big[ \int_0^\infty d\mu^2\, J_2(\mu^2) \Big] F_2^{(0)}(x_B) 
+     + O(\Lambda^2/Q^2) = F_2^{(0)}(x_B)  + O(\Lambda^2/Q^2) \ .
 \end{align}
-The same holds true also for the helicity structure function $g_1$.
+%The same holds true also for the helicity structure function $g_1$.
 %
@@
 \end{equation} 
-\AAcom{We need to discuss what happens to the B functions!! See e-mail from Jul 7th, 2015, for ideas.}
 where 
@@
 \end{align} 
+where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
 % The $\xi_1$ and $\xi_4$ have an interpretation as average invariant mass (and mass squared) of the current jet, and $l^-=q^- + O(1/Q)$ is imposed by 4-momentum conservation at the hard scattering vertex.
 The $\xi^4$ term contributes at order $O(1/Q^2)$ and is no further considered in this paper.
-It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < M_q < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
-From the analytic properties of spectral functions we may expect \cite{Accardi-Qiu)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
+It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
+From the analytic properties of spectral functions we may expect \cite{Accardi-Qiu)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
 Taking into account that $J_1 < J_2$, we may therefore expect
@@
 $\mj = \,_{\text{pert}} \langle 0
-|  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = m_q$, recovering the
+|  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass, recovering the
 conventional result. However, we are here considering non perturbative effects
-on the quark fragmentation and $\mj \gtrsim m_q$. 
+on the quark fragmentation and $\mj \gtrsim \mq$. 
 %very importantly, this
 %quantity can be computed in lattice QCD. 
-%\todo{[AA] Are qe sure that $\mj > m_q$??}
+%\todo{[AA] Are qe sure that $\mj > \mq$??}
 %\todo{[AA] Need to discuss connection to quark condensate and tensor charge.}
@@
 \end{equation}  
-This diagram and its hermitian conugate are not only important to account for all contribution of order $O(1/Q)$, but also in restoring up to twist-3 the gauge invariance broken in diagram \ref{fig:handbags}(a) by the different mass of the incoming and outgoing quark lines, namely, $m_q \neq \mj$.
+This diagram and its hermitian conugate are not only important to account for all contribution of order $O(1/Q)$, but also in restoring up to twist-3 the gauge invariance broken in diagram \ref{fig:handbags}(a) by the different mass of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.
 
@@
 The relevant part of the semi-inclusive hadronic tensor for our analysis is 
-\todo{[AA] I am using the notation in Piet Mulder's lecture notes - this will need to be checked. Decide also if we want this at parton or charge-weighted level.}
+\todo{[AA] I am using the notation in Piet Mulder's lecture notes - this will need to be checked.}
 \begin{align}
   \label{eq:Wsidis_ini}
-  2 \Lambda \sum_h \int dz d^2p_{hT} W^{\mu\nu}_{\text{SIDIS}}(z,p_{hT}) 
-    & = i \frac{2\Lambda}{Q} 
-    \hat t^{[\mu} \epsilon_\perp^{\nu]\rho}S_{\perp\rho} 
-    \Big[ 2 x_b g_T(x_B) \sum_h \int dz d^2p_{hT} D_1^h(z,p_{hT}) \\
-  & + 2 h_1(x_B,p_{hT}) \sum_h \int dz d^2p_{hT} \tilde E^h(z,p_{hT}) \Big] + \ldots
+  2 \Lambda  W^{\mu\nu}
+    & = i \frac{2\Lambda}{Q} \hat t^{[\mu}_{\phantom \perp} 
+    \epsilon_\perp^{\nu]\rho}S_{\perp\rho} 
+    \sum_q e_q^2
+    \bigg[ 2 x_b g_T(x_B) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
+  %\\ &
+  + 2 h_1(x_B) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots
 \end{align}
+Here and we reintroduced the quark flavor $q$ for maximum clarity, and $e_q$ its electric charge.
 The first term can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS_TMDlevel}.
-To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (m_q/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{New-testament}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
+To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{New-testament}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
 \begin{align}
-  \sum_h \int dz d^2p_{hT} \tilde E(z,p_{hT}) 
-    = \sum_h \int dz d^2p_{hT} \Big[ E(z,p_{hT}) - \frac{m_q}{\Lambda} z D_1(z,p_{hT}) \Big]
-    = \xi_1 - \frac{m_q}{\Lambda} \xi_2 = \frac{\mj - m_q}{\Lambda} \ .
+  \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) 
+    = \sum_h \int dz d^2p_{hT} \Big[ E^{q,h}(z,p_{hT}) - \frac{\mq}{\Lambda} z D_1^{q,h}(z,p_{hT}) \Big]
+    = \xi_1 - \frac{\mq}{\Lambda} \xi_2 = \frac{\mj - \mq}{\Lambda} \ .
 \end{align}
-This formula is the single most important result of this paper.
+This formula is the single most important result of this paper, and provides a non perturbative generalization of the commonly used $\int\tilde E =0$ sum rule introduced in \cite{Jaffe-Ji}.
+Indeed, calculating the jet correlator
+on the perturbative vacuum one would obtain, as already discussed, $\mj=\mq$
+and the new term would vanish.
 
-Finally, with suitable projections of the hadronic tensor, the inclusive cross section up to order $M/Q$ can be written as
+Finally, with suitable projections of the hadronic tensor, the inclusive cross section up to order $\Lambda/Q$ can be written as
 \begin{align}
@@
 %\nonumber 
-\\  
-&
+%\\  &
 + |\bm{S}_\perp| \lambda_e\, \sqrt{2\,\varepsilon (1-\varepsilon)}\, 
@@
 \begin{align}
-F_{UU ,T} &= \xbj\,\sum_a e_a^2\,f_1^a(\xbj),
+F_{UU ,T} &= \xbj\,\sum_q e_q^2\,f_1^q(\xbj),
 \\
@@
 \\
-F_{LL} &=\xbj\,\sum_a e_a^2\,g_1^a(\xbj),
+F_{LL} &=\xbj\,\sum_q e_q^2\,g_1^q(\xbj),
 \\
@@
 \\
-F_{LT}^{\cos \phi_S}&=-\xbj\,\sum_a e_a^2\, \frac{2\Lambda}{Q}\,
-\biggl(\xbj  g_T^a(\xbj)
-   + \frac{\mj -m_q}{\Lambda} \, h_{1}^a(\xbj) \biggr).
+F_{LT}^{\cos \phi_S}&=-\xbj\,\sum_q e_q^2\, \frac{2\Lambda}{Q}\,
+\biggl(\xbj  g_T^q(\xbj)
+   + \frac{\mj -\mq}{\Lambda} \, h_{1}^q(\xbj) \biggr).
 \label{e:FLTint}
@@
 analysis; it is not suppressed as an inverse power of $Q$, and therefore
-survives even in the Bjorken limit. Note that calculating the jet correlator
-on the perturbative vacuum one would obtain, as already discussed, $\mj=m_q$
-and the new term wouls vanishe, as it should. However, on the non-perturbative
+survives even in the Bjorken limit. On the non-perturbative
 vacuum the jet mass is larger than the quark's, and this contributes a
-non-negligible term to the twist-3 part of the $g_2$ function, as we shall
+non-negligible term to the twist-3 part of the $g_2$ function, as we will
 discuss in the next section.
@@
     \widetilde g_T^{a \star}(x) 
-    + \int_x^1\frac{dy}{y} \widehat{g}_T^a(y) 
-    + \frac{m_q}{M} (h_1^a/x)^\star(x) 
-    + \frac{\mj-m_q}{M} h_1^a(x) 
+    + \int_x^1\frac{dy}{y} \widehat{g}_T^q(y) 
+    + \frac{\mq}{\Lambda} (h_1^q/x)^\star(x) 
+    + \frac{\mj-\mq}{\Lambda} h_1^q(x) 
 \Biggr) \ ,
@@
 The former is usually neglected for
-light quarks since it is proportional to $m_q=O$(1 MeV). In the latter term,
+light quarks since it is proportional to $\mq=O$(1 MeV). In the latter term,
 new in our analysis, the transversity distribution is multiplied by a constant
@@
 g_2^{\text{quark}} &= \frac{1}{2}\,\sum_a e_a^2 
- \frac{m_q}{M} (h_1^a/x)^\star(x),
+ \frac{\mq}{\Lambda} (h_1^q/x)^\star(x),
 &
 g_2^{\text{jet}} &= \frac{1}{2}\,\sum_a e_a^2 
-\frac{\mj-m_q}{M} h_1^a(x). 
+\frac{\mj-\mq}{\Lambda} h_1^q(x). 
 \end{align} 
-We choose the values of the mass parameters to be $m_q=5$ MeV and 
+We choose the values of the mass parameters to be $\mq=5$ MeV and 
 $\mj = 50$ MeV.
@@
   \label{eq:BC}
-  \int dx\, g_2(x) = \frac{\mj-m_q}{\Lambda} \int dx\, h_1(x) \ ,
+  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, h_1(x) \ ,
 \end{align}

### 2016-07-20 1607 - JMC for g2/Paper/JMC_dis.tex
Some ideas jotted down as discussed these last days

@@
 \end{itemize}
+Some ideas to check:
+\begin{itemize}
+\item JAM13 neutron has almost 0 twist 3, with small positive contribution at small x. Can we use this to highlight teh $g_2^{jet}$ contribution?
+\item In Jam 13, Fig.
+6, it looks like in general the violation of teh BC sum rule is a small-x effect --> constraints on h(x) fits?
+This cannot really be checked vs.
+JAM15, that assumes $g_2^(0)$ respects BC.
+\end{itemize}
 
@@
   \label{eq:BC}
-  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, h_1(x) \ ,
+  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, h_1(x) 
+    =  \frac{\mj-\mq}{\Lambda} g_T \ ,
 \end{align}
-where the integral over $h_1$ is related to target's tensor charge.
+where the integral over $h_1$ is related to target's tensor charge $g_T$.
 Consequences:
@@
 \item in turn these can be used to determine the size of the $h_1$ term in $g_2-g_2^{WW}$ and allow an eperimental extraction of the pure twist-3 terms.
+\item Recent calcs of $g_T^{d-u}$ tensor charge are very precise - can we use this info in our plots?
+(to ``measure'' the quark condenstae $\langle0|\psi\bar\psi|0\rangle>$, for example?
+this would need an estimate of teh BC breaking, that is only availbal efrom JAM13, for all that I know.)
 \end{itemize}
@@
 \todo{It would be cool to find a process where the $\mj$ contribution is th eonly one (similar to the BC breaking) ...}
-
-\section{Conclusions}
-
-\noindent
-------------------------------------------------- \\
-Edited down to here\\
---------------------------------------------------\\
 

### 2016-07-22 1607 - JMC for g2/Paper/JMC_dis.tex
Discussions on g2--g2WW plot added

@@
     + \int_x^1\frac{dy}{y} \widehat{g}_T^q(y) 
-    + \frac{\mq}{\Lambda} (h_1^q/x)^\star(x) 
-    + \frac{\mj-\mq}{\Lambda} h_1^q(x) 
+    + \frac{\mq}{\Lambda} \left(\frac{h_1^q}{x}\right)^\star(x) 
+    + \frac{\mj-\mq}{\Lambda} \frac{h_1^q(x)}{x} 
 \Biggr) \ ,
@@
 
-To estimate the size of the last two terms in Eq.~\eqref{e:g2}, 
-we use a recent parametrization of the transversity distribution from
-Ref.~\cite{Radici:2015mwa}, which is comparable also to other
-extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. We define the shorthand
-notation
+It is important to estimate the size of teh variou scontributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
 \begin{align}
+g_2^{tw3} & = \frac{1}{2}\,\sum_a e_a^2
+    \biggl(
+    \widetilde g_T^{a \star}(x) 
+    + \int_x^1\frac{dy}{y} \widehat{g}_T^q(y) 
+    \biggr) 
+&
 g_2^{\text{quark}} &= \frac{1}{2}\,\sum_a e_a^2 
@@
 g_2^{\text{jet}} &= \frac{1}{2}\,\sum_a e_a^2 
-\frac{\mj-\mq}{\Lambda} h_1^q(x). 
+\frac{\mj-\mq}{\Lambda} \frac{h_1^q(x)}{x}. 
 \end{align} 
-We choose the values of the mass parameters to be $\mq=5$ MeV and 
-$\mj = 50$ MeV.
+These are comapred in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function obtained in the very recent JAM15 fit of polarized DIS asymmetries \cite{JAM15}, that includes a large amount of precise data at large $x$ from Jefferson Lab, and simultaneously fits the higher-twist components of in $g_1$ and $g_2$ to the data.
+For the ``pure twist-3'' contribution, $g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix elements, we show a model calculation by Braun et al.
+\cite{Braun-et-al}; for other estimates, see \cite{Other-tw3-calcs}.
+To estimate the contributions from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral odd quark-quark matrix elements, we use the recent Pavia15 fit of the transversity distribution from Ref.~\cite{Radici:2015mwa}, which is comparable also to other
+extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. Furthermore, we choose the values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV.
 
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[width=8cm]{g2contrib}
-\caption{\label{f:g2contrib} 
-Different contributions to the non Wandzura-Wilczek part of the $g_2$ structure function compared to the JAM15 fit of $g_2-g_2^{\text{WW}}$ \cite{JAM15}.
-}
-\end{center}
-\end{figure}
+As one can see, in the proton case the pure twist-3 contribution is quite smaller in magnitude, and opposite in sign, compared to the JAM15 fit.
+As expected, the quark-mass contribution is essentially negligible and cannot reconcile these two.
+Even though the uncertainties in the $h_1$ extraction and even more the estimate of $M_q$ are large, it is quite clear that the gap between the pure twist-3 $g_2^{tw3}$ function and the JAM15 fit can be explained by the new jet-mass contribution we discussed in this paper.
+
+In the neutron case, the jet contribution is very negative at intermediate to large values of $x$.
+If one trusts the order of magnituse of the $g_2^{tw3}$ calculation by Braun et al., one would conclude that the jet contribution cannot be that large.
+However, the latteris dominated by the $d$ quark's transversity, whose fit suffers from large systematic uncertainties and saturates the negative Soffer bound.Recent deata in $p+p$ collisions indicate, however, that $h_1^d$ is less negative than in the Pavia15 fits, in agreement with the JAM15 fit of the non Wandzura-Wilczek contribution to $g_2$.
 
 \begin{itemize}
-\item large-$x$: bridges Braun's pure twist-3 theory and the data
 \item smaller-$x$: constrains the small-$x$ behavior of transversity.
-\item in general, $g_2^{\text{quark}}$ is quite smaller than the other contribution, as customarily assumed.
 \end{itemize}
@@
 \begin{itemize}
-\item JAM13 neutron has almost 0 twist 3, with small positive contribution at small x. Can we use this to highlight teh $g_2^{jet}$ contribution?
+\item JAM13 neutron has almost 0 twist 3, with small positive contribution at small x.
+Can we use this to highlight teh $g_2^{jet}$ contribution?
+Or maybe as a cnstrain: if Braun is right then $g_2^{jet}(n) \approx -g_2^{tw3}(n)$.
+(still, does not help much for the proton).
 \item In Jam 13, Fig.
@@
 \end{itemize}
+
+\begin{figure}[tbh]
+\begin{center}
+\includegraphics[width=8cm]{g2contrib}
+\caption{\label{f:g2contrib} 
+Different contributions to the non Wandzura-Wilczek part of the proton (left) and neutron (right) $g_2$ structure function compared to the JAM15 fit of the  $g_2-g_2^{\text{WW}}$ (solid black) \cite{JAM15}.
+The quark and jet contributions are shown with a dotted red and a dot-dashed green line respectively, with uncertainty bands coming form the Pavia15 fit of the transversity function \cite{Pavia15}.
+The pure twist-3 contribution calculated by Braun et al.
+\cite{Braun-et-al} is shown as a dashed blue line (no uncertainty estiamte was provided in teh original reference).
+}
+\end{center}
+\end{figure}
 

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex

@@
 
-The nucleon tensor charge is a fundamental property of the nucleon and is at
-present poorly constrained. Several estimates based on lattice
-QCD are available, but only limited information from direct measurements. The
+The tensor charge is a fundamental property of the nucleon, at
+present poorly constrained. It has been estimated in lattice
+QCD (see, e.g.,
+\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015ow}), but
+only limited information is available from direct measurements. The
 way to extract the tensor charge from experimental measurements requires first
-the extraction the so-called transversity parton distribution function (PDF),
-denoted by $h_1^q(x)$. The transversity distribution is then integrated over
-$x$ to yield the contribution of flavor $q$ to tensor charge.
+of all the extraction the so-called transversity parton distribution function,
+denoted by $h_1^q(x)$ \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}. The integral of the transversity distribution
+corresponds to the contribution of flavor $q$ to tensor charge.
 
 In this paper, we discuss the possibility of observing the effect of
-the transversity distribution in totally inclusive Deep Inelastic Scattering.
+the transversity parton distribution function (PDF) in totally inclusive Deep Inelastic Scattering.
 
@@
 a chiral-odd function and needs to be combined with a spin-flip mechanism to
-appear in a scattering process. Usually, this spin flip is provided by another
+appear in a scattering process~\cite{}. Usually, this spin flip is provided by another
 nonperturbative distribution or fragmentation function, implying that
 transversity cannot be accessed in inclusive DIS,
-but only in more complex processes such as semi-inclusive DIS or Drell-Yan.
+but only in more complex processes such as semi-inclusive DIS or Drell-Yan~\cite{Ralston:1979ys,Collins:1992xw}.
 
@@
 that on-shell quarks cannot be present in the final state, but they rather
-decay into hadrons (ideally, the form jets of hadrons). This is sufficient to modify the structure of the DIS
+decay into hadrons (ideally, forming jets of hadrons). This is sufficient to modify the structure of the DIS
 cut-diagram, even if none of the hadrons is detected in the final
 state. For a proper description of this effect, we include ``jet
-correlators'' into the analysis. We pay particular attention to insuring that our
+correlators'' into the analysis. We pay particular attention to ensuring that our
 results are gauge invariant. We observe that the inclusion of jet correlators
@@
 interesting features that: a) violates the Wandzura--Wilczek relation, b)
-violates the Burkhardt--Cottingham sum rule, c) is
+potentially violates the Burkhardt--Cottingham sum rule, c) is
 proportional to the transversity distribution function multiplied by a
-nonperturbative ``jet mass'' parameter. We provide estimates of this
+nonperturbative ``jet mass'' parameter, much larger than the mass of light
+quarks. 
+We provide estimates of this
 contribution based on a recent extraction of transversity and show that it
@@
 
-Motivated by large-$x$ mass corrections to inclusive DIS structure functions, Accardi and Qiu have introduced in the LO handbag diagram a ``jet correlator'' that accounts for invariant mass production in the current jet, and ensures that leading twist calculations in collinear factorization are consistent with the requirement imposed by baryon number conservation that $x_B<1$ \cite{Accardi-Qiu}.
-The jet correlator is depicted in Figure~\ref{fig:handbags}(a) and is defined as
+Motivated by large-$x$ mass corrections to inclusive DIS structure functions,
+Accardi and Qiu have introduced in the LO handbag diagram a ``jet correlator''
+that accounts for invariant mass production in the current jet, and ensures
+that leading twist calculations in collinear factorization are consistent with
+the requirement imposed by baryon number conservation that $x_B<1$
+\cite{Accardi-Qiu}. The jet correlator is depicted in
+Figure~\ref{fig:handbags}(a) and is defined as 
 \begin{align} 
@@
 \end{align} 
-In this definition, $l$ is the quark four-momentum, $\Psi$ the quark field operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is the nonperturbative vacuum state.
-Furthermore, we explicitly guarantee the correlator's gauge invariance by introducing two Wilson line operators ${\cal U}^{n_+}$ along a light-cone plus direction determined by the vector $n_+$.
-This path choice for the Wilson line is required by QCD factorization theorems, and the vector is determined by the particular hard process to which the jet correlator contributes.
-For example, in the case of inclusive DIS discussed in this paper, this is determined by the four momentum transfer $q$ and the proton's momentum $p$.
+In this definition, $l$ is the quark four-momentum, $\Psi$ the quark field
+operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
+the nonperturbative vacuum state. Furthermore, we explicitly guarantee the
+correlator's gauge invariance by introducing two Wilson line operators ${\cal
+  U}^{n_+}$ along a light-cone plus direction determined by the vector
+$n_+$. This path choice for the Wilson line is required by QCD factorization
+theorems, and the vector is determined by the particular hard process to which
+the jet correlator contributes. For example, in the case of inclusive DIS
+discussed in this paper, this is determined by the four momentum transfer $q$
+and the proton's momentum $p$.
 

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
Started discussing moments

@@
 However, the latteris dominated by the $d$ quark's transversity, whose fit suffers from large systematic uncertainties and saturates the negative Soffer bound.Recent deata in $p+p$ collisions indicate, however, that $h_1^d$ is less negative than in the Pavia15 fits, in agreement with the JAM15 fit of the non Wandzura-Wilczek contribution to $g_2$.
+Correspondingly the jet contribution to the proton at $x \approx 0.1$ would become less positive, inproving as well teh agreement with the JAM15 fit.
 
@@
 \includegraphics[width=8cm]{g2contrib}
+\includegraphics[width=8cm]{g2contribN}
 \caption{\label{f:g2contrib} 
@@
 The quark and jet contributions are shown with a dotted red and a dot-dashed green line respectively, with uncertainty bands coming form the Pavia15 fit of the transversity function \cite{Pavia15}.
+The unceratainty in the choice $m_q=5$ GeV and $M_q=100$ GeV is not shown.
 The pure twist-3 contribution calculated by Braun et al.
@@
 
-Another consequence of the new chiral odd term induced by the non-vanishing of
-the chiral condensate on the non perturbative vacuum is that the
-Burkardt-Cottingham sum rule is broken: 
+It is interesting to consider the moments of the non Wandzura-Wilczek contribution to $g-2$,
+\begin{align}
+  d_N = N \int_0^1 x^N \big( g_2(x) - g_2^{WW}(x) \big) \ .
+\end{align}
+For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N-1} f(x)$. It is then straightforward to verify that $f^*[N] = f[N] (N-1)/N$ and  
+\begin{align}
+  d_N & \equiv N g_2[N+1] + (N-1) g_1[N+1] \\
+  & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N+1] + \hat g_T^q[N+1]
+    + \frac{N M_q-m_q}{\Lambda} h_1^q[N+1] \bigg) \ .
+\end{align}
+\AAcom{The notation used in JAM15 with $x^{N-1}$ for the Nth moment is pretty awkward here. Should we use $x^N$ instead?}
+
+The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{BC,Jaffe-lectures}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function:
 \begin{align}
   \label{eq:BC}
-  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, h_1(x) 
-    =  \frac{\mj-\mq}{\Lambda} g_T \ ,
+  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1(x) \ .
 \end{align}
-where the integral over $h_1$ is related to target's tensor charge $g_T$.
+This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
+It explicitly displays the contribution from spin-flip amplitudes that is commented upon in Refs.~\cite{BC,Jaffe-lectures}, but is explicitly shown here in terms of collinear PDFs.
+
 Consequences:

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
Added references, modified pictures

--- 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 of all the extraction the so-called transversity parton distribution function,
-denoted by $h_1^q(x)$ \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}. The integral of the transversity distribution
-corresponds to the contribution of flavor $q$ to tensor charge.
+denoted by $h_1^q(x)$~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}. 
+The integral of the transversity distribution
+corresponds to the contribution of flavor $q$ to the tensor charge.
 
@@
 a chiral-odd function and needs to be combined with a spin-flip mechanism to
-appear in a scattering process~\cite{}. Usually, this spin flip is provided by another
+appear in a scattering process~\cite{Jaffe:1996zw,Barone:2001sp}. Usually, this spin flip is provided by another
 nonperturbative distribution or fragmentation function, implying that
 transversity cannot be accessed in inclusive DIS,
-but only in more complex processes such as semi-inclusive DIS or Drell-Yan~\cite{Ralston:1979ys,Collins:1992xw}.
+but only in more complex processes such as semi-inclusive DIS or Drell-Yan~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1993kk}.
 
@@
 account mass corrections. In fact, it is well known that transversity gives a
-contribution to the structure function $g_2$ in inclusive DIS, and in
+contribution to the structure function $g_2$ in inclusive DIS (see, e.g.,
+\cite{Accardi:2009au} and references therein), and in
 particular to the violation of the so-called Wandzura--Wilczek relation for
-$g_2$. However, this contribution is proportional to the current quark mass
+$g_2$~\cite{Wandzura:1977qf}. However, this contribution is proportional to the current quark mass
 and can be expected to be very small.
@@
 proportional to the transversity distribution function multiplied by a
-nonperturbative ``jet mass'' parameter, much larger than the mass of light
+nonperturbative ``jet mass'' parameter, probably much larger than the mass of light
 quarks. 
@@
 \end{align}
-where $F_2^{(0)}$ is the structure function calculated with the handbag diagram sporting a bare quark propagator instead of the jet correlator, and $\xi=2x_B/(1+\sqrt{1+4x_B^2M^2/Q^2})$ with $M$ the nucleon's mass is the Nachtmann scaling variable.
-(We also omitted the dependence of the structure function on $Q^2$ for clarity of notation).
-In this paper we limit our attention to effects of order $O(1/Q)$ and therefore can extend the integration to $\mu^2=\infty$.
-Therefore, the jet function $J_2$ decouples and, thanks to the sum rule \eqref{eq:jetfnsprops}, integrates to 1.
-One then recovers the conventional result,
+where $F_2^{(0)}$ is the structure function calculated with the handbag
+diagram sporting a bare quark propagator instead of the jet correlator, and
+$\xi=2x_B/(1+\sqrt{1+4x_B^2M^2/Q^2})$ with $M$ the nucleon's mass is the
+Nachtmann scaling variable. (We also omitted the dependence of the structure
+function on $Q^2$ for clarity of notation). In this paper we limit our
+attention to effects of order $O(1/Q)$ and therefore can extend the
+integration to $\mu^2=\infty$. Therefore, the jet function $J_2$ decouples
+and, thanks to the sum rule \eqref{eq:jetfnsprops}, integrates to 1. One then
+recovers the conventional result, 
 \begin{align}

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
BC and AB sum rules discussion

@@
 
+\newcommand{\eg}{{\em e.g.}}
 %\newcommand{\mj}{\langle m_j \rangle}
@@
 present poorly constrained. It has been estimated in lattice
-QCD (see, e.g.,
+QCD (see, \eg,
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015ow}), but
@@
 account mass corrections. In fact, it is well known that transversity gives a
-contribution to the structure function $g_2$ in inclusive DIS (see, e.g.,
+contribution to the structure function $g_2$ in inclusive DIS (see, \eg,
 \cite{Accardi:2009au} and references therein), and in
@@
 This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
-It explicitly displays the contribution from spin-flip amplitudes that is commented upon in Refs.~\cite{BC,Jaffe-lectures}, but is explicitly shown here in terms of collinear PDFs.
+It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{BC} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe-lectures}.
+
+Assuming the Burkhardt-Cottingham sum rule to be strictly valid, we obtain a strong constraint on the transversity function,
+\begin{align}
+   \int dx\, \frac{1}{x} h_1(x) = 0 \ .
+\end{align}
+Even if the BC sun rule is broken by a 
+$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe-lectures}), we obtain that $h_1(x)/x$ must be integrable.
+This entails a bound on the small $x$ behavior of the transversity,
+\begin{align}
+  h_1(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
+\end{align}
+This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is as yet very limited.
+
+{\bf [---------------- AA:  EDITED down here --------------------]}
 

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
fixed first sentences and naming

--- 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 Motivated by large-$x$ mass corrections to inclusive DIS structure functions,
-Accardi and Qiu have introduced in the LO handbag diagram a ``jet correlator''
+Accardi and Qiu have introduced in the LO handbag diagram 
+a ``jet correlator'' (also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph})
 that accounts for invariant mass production in the current jet, and ensures
@@
 the requirement imposed by baryon number conservation that $x_B<1$
-\cite{Accardi-Qiu}. The jet correlator is depicted in
+\cite{Accardi:2008ne}. The jet correlator is depicted in
 Figure~\ref{fig:handbags}(a) and is defined as 
@@
 
-The correlator $\Xi$ can be parametrized in terms of scalar functions, using the vectors $l$ and $n_+$: 
+The correlator $\Xi$ can be parametrized in terms of jet parton correlation
+functions (PCFs), using the vectors $l$ and $n_+$: 
 \begin{equation}
@@
 \end{align}
-where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it i.e.}, of the particles going through the cut in the top blob of Fig.\ref{fig:handbags}(a), and the $J_i$ are the spectral functions of the quark propagator, that have been also called ``jet functions'' in \cite{Accardi-Qiu,Collins-book?,SCET?}.
-These satisfy
+where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it
+  i.e.}, of the particles going through the cut in the top blob of
+Fig.\ref{fig:handbags}(a), and the $J_i$ are the spectral functions of the
+quark propagator, that have been also called ``jet functions'' in
+\cite{Accardi:2008ne,SCET?} or ``jet factors''~\cite{Collins:2007ph}. These satisfy
 \begin{align}
@@
 When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$.
-This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}:
+This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}:
 \begin{align}
@@
 It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
-From the analytic properties of spectral functions we may expect \cite{Accardi-Qiu)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
+From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
 Taking into account that $J_1 < J_2$, we may therefore expect
@@
 
-Extending the analysis of \cite{Accardi-Qiu} to the calculation of twist-3
+Extending the analysis of \cite{Accardi:2008ne} to the calculation of twist-3
 structure functions requires not only to consider the $\xi_1$ term in the jet

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
finished discussing the moments

@@
 \end{align}
-For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N-1} f(x)$. It is then straightforward to verify that $f^*[N] = f[N] (N-1)/N$ and  
+For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = N/(N+1) f[N]$ and  
 \begin{align}
-  d_N & \equiv N g_2[N+1] + (N-1) g_1[N+1] \\
-  & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N+1] + \hat g_T^q[N+1]
-    + \frac{N M_q-m_q}{\Lambda} h_1^q[N+1] \bigg) \ .
+  d_N & \equiv (N+1) g_2[N] + N g_1[N] \\
+  & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N] + \hat g_T^q[N]
+    + \frac{(N+1) M_q-m_q}{\Lambda} h_1^q[N] \bigg) \ .
 \end{align}
@@
    \int dx\, \frac{1}{x} h_1(x) = 0 \ .
+\label{eq:ABsumrule}
 \end{align}
@@
   h_1(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
+\label{eq:ABbound}
 \end{align}
-This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is as yet very limited.
+This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is, as yet, very limited, and in general for proper extrapolations when calculating moments.
+
+The first moment is the first in which a contribution from the pure twist-3 part of $g_2$ appears:
+\begin{align}
+  d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1]
+    + \frac{2M_q-m_q}{\Lambda} h_1^q[1] \bigg)
+\end{align}
+where $h_1^q[1] = \int_0^1 \dx $ is the contribution of a quark $q$ to the tensor charge.
+In this case, the transevrsity contribution is a background to the extraction of teh poure twist-3 piece.
+Fortunately, it is a quantity that can be extracted from the lattice \cite{Bhattacharya:2016zcn} or fitted \cite{Pavia15, others, reviews?}.
+Furthermore the new sum rule \eqref{eq:ABsumrule} and bound \eqref{eq:ABbound} promise to improve future transversity fits.
+What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator.
+We will, however, discuss later perspectives on how to measure it.
+Therefore the pure twist-3 part can, in principle, be properly isolated.
+
+The third moment is interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe-lectures}, and interpreted as as the average color force experienced by the struck quark as it exits teh nucleon \cite{M.Burkardt}.
+As in the previous case, however, the transversity contribution needs to be subtracted:
+\begin{align}
+  d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2]
+    + \frac{3M_q-m_q}{\Lambda} h_1^q[2] \bigg)
+\end{align}
 
 {\bf [---------------- AA:  EDITED down here --------------------]}
-
-Consequences:
-\begin{itemize}
-\item Inclusive DIS become sensitive to the tensor charge; furthermore, teh BC summ rule isolates the effects due to the chiral odd part of the jet correlator. 
-\item Both the jet mass $\mj$ and the tensor charge can in principle be calculated on the lattice
-\item Comparison to the Burkhardt-Cottingham sum rule can provide experimental verification of lattice calculation
-\item in turn these can be used to determine the size of the $h_1$ term in $g_2-g_2^{WW}$ and allow an eperimental extraction of the pure twist-3 terms.
-\item Recent calcs of $g_T^{d-u}$ tensor charge are very precise - can we use this info in our plots?
-(to ``measure'' the quark condenstae $\langle0|\psi\bar\psi|0\rangle>$, for example?
-this would need an estimate of teh BC breaking, that is only availbal efrom JAM13, for all that I know.)
-\end{itemize}
 
@@
 \end{itemize}
-\todo{It would be cool to find a process where the $\mj$ contribution is th eonly one (similar to the BC breaking) ...}
+\todo{It would be cool to find a process where the $\mj$ contribution is the only one (similar to the BC breaking) ...}
 

### 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
fixed some references

--- 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
-From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
+From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
 Taking into account that $J_1 < J_2$, we may therefore expect
@@
 \end{align}
-where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{New_testament}.
+where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}.
 In terms of the TMD fragmentation functions we are interested in, this reads
@@
 \end{align}
-where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$ and transverse momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function defined in \cite{New-testament}.
+where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$ and transverse momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function defined in \cite{Bacchetta:2006tn}.
 
@@
 The first term can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS_TMDlevel}.
-To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{New-testament}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
+To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{Bacchetta:2006tn}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
 \begin{align}
@@
 \end{align}
-This formula is the single most important result of this paper, and provides a non perturbative generalization of the commonly used $\int\tilde E =0$ sum rule introduced in \cite{Jaffe-Ji}.
-Indeed, calculating the jet correlator
+This formula is the single most important result of this paper, and provides a
+non perturbative generalization of the commonly used $\int\tilde E =0$ sum
+rule introduced in \cite{Jaffe:1996zw}. Indeed, calculating the jet correlator 
 on the perturbative vacuum one would obtain, as already discussed, $\mj=\mq$
@@
 \end{align} 
-These are comapred in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function obtained in the very recent JAM15 fit of polarized DIS asymmetries \cite{JAM15}, that includes a large amount of precise data at large $x$ from Jefferson Lab, and simultaneously fits the higher-twist components of in $g_1$ and $g_2$ to the data.
-For the ``pure twist-3'' contribution, $g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix elements, we show a model calculation by Braun et al.
-\cite{Braun-et-al}; for other estimates, see \cite{Other-tw3-calcs}.
-To estimate the contributions from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral odd quark-quark matrix elements, we use the recent Pavia15 fit of the transversity distribution from Ref.~\cite{Radici:2015mwa}, which is comparable also to other
-extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. Furthermore, we choose the values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV.
+These are comapred in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function
+obtained in the very recent JAM15 fit of polarized DIS asymmetries
+\cite{Sato:2016tuz}, that includes a large amount of precise data at large $x$
+from Jefferson Lab, and simultaneously fits the higher-twist components of in
+$g_1$ and $g_2$ to the data. For the ``pure twist-3'' contribution,
+$g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
+elements, we show a model calculation by Braun et al. \cite{Braun-et-al}; for
+other estimates, see \cite{Other-tw3-calcs}. To estimate the contributions
+from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral
+odd quark-quark matrix elements, we use the recent Pavia15 fit of the
+transversity distribution from Ref.~\cite{Radici:2015mwa}, which is comparable
+also to other 
+extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. Furthermore, we choose the
+values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV.
 
@@
 \item In Jam 13, Fig.
-6, it looks like in general the violation of teh BC sum rule is a small-x effect --> constraints on h(x) fits?
+6, it looks like in general the violation of the BC sum rule is a small-x effect --> constraints on h(x) fits?
 This cannot really be checked vs.
@@
 \caption{\label{f:g2contrib} 
-Different contributions to the non Wandzura-Wilczek part of the proton (left) and neutron (right) $g_2$ structure function compared to the JAM15 fit of the  $g_2-g_2^{\text{WW}}$ (solid black) \cite{JAM15}.
-The quark and jet contributions are shown with a dotted red and a dot-dashed green line respectively, with uncertainty bands coming form the Pavia15 fit of the transversity function \cite{Pavia15}.
-The unceratainty in the choice $m_q=5$ GeV and $M_q=100$ GeV is not shown.
-The pure twist-3 contribution calculated by Braun et al.
-\cite{Braun-et-al} is shown as a dashed blue line (no uncertainty estiamte was provided in teh original reference).
+Different contributions to the non Wandzura-Wilczek part of the proton (left)
+and neutron (right) $g_2$ structure function compared to the JAM15 fit of the
+$g_2-g_2^{\text{WW}}$ (solid black) \cite{Sato:2016tuz}. The quark and jet
+contributions are shown with a dotted red and a dot-dashed green line
+respectively, with uncertainty bands coming form the Pavia15 fit of the
+transversity function \cite{Radici:2015mwa}. The unceratainty in the choice
+$m_q=5$ GeV and $M_q=100$ GeV is not shown. The pure twist-3 contribution
+calculated by Braun et al. \cite{Braun:2011aw} is shown as a dashed blue line
+(no uncertainty estiamte was provided in teh original reference). 
 }
@@
 
-The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{BC,Jaffe-lectures}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function:
+The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{Burkhardt:1970ti,Jaffe:1996zw}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function:
 \begin{align}
@@
 This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
-It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{BC} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe-lectures}.
+It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe:1996zw}.
 
@@
 Even if the BC sun rule is broken by a 
-$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe-lectures}), we obtain that $h_1(x)/x$ must be integrable.
+$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe:1996zw}), we obtain that $h_1(x)/x$ must be integrable.
 This entails a bound on the small $x$ behavior of the transversity,

### 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
Fixed some other references

@@
 QCD (see, \eg,
-\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015ow}), but
+\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn}), but
 only limited information is available from direct measurements. The
@@
 of all the extraction the so-called transversity parton distribution function,
-denoted by $h_1^q(x)$~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}. 
+denoted by $h_1^q(x)$ (see Ref.~\cite{Barone:2001sp} for a review on transversity and
+Refs.~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa} for the most recent
+extractions). 
 The integral of the transversity distribution
 corresponds to the contribution of flavor $q$ to the tensor charge.
+The knowledge of the tensor charge can be used also to put constraints on the search of physics beyond the Standard
+Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
 
@@
 a chiral-odd function and needs to be combined with a spin-flip mechanism to
-appear in a scattering process~\cite{Jaffe:1996zw,Barone:2001sp}. Usually, this spin flip is provided by another
+appear in a scattering process~\cite{Jaffe:1996zw}. Usually, this spin flip is provided by another
 nonperturbative distribution or fragmentation function, implying that
@@
 quark propagator, that have been also called ``jet functions'' in
-\cite{Accardi:2008ne,SCET?} or ``jet factors''~\cite{Collins:2007ph}. These satisfy
+\cite{Accardi:2008ne,SCET?}. These satisfy
 \begin{align}
@@
 
-When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$.
-This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}:
+When inserting the jet correlator in the handbag diagram for inclusive DIS,
+the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$. This
+induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the
+$F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}: 
 \begin{align}
@@
 The $\xi^4$ term contributes at order $O(1/Q^2)$ and is no further considered in this paper.
-It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
-From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
-Taking into account that $J_1 < J_2$, we may therefore expect
+It is important to notice that $\xi_2=1$ exactly due to CPT invariance
+\cite{Weinberg:1995mt}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is
+dynamically determined. From the analytic properties of spectral functions we
+may expect \cite{Accardi:2008ne} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2
+(\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the
+mass of the pion, due to color confinement effects. Taking into account that
+$J_1 < J_2$, we may therefore expect  
 \begin{align}
@@
 \end{equation}  
-This diagram and its hermitian conugate are not only important to account for all contribution of order $O(1/Q)$, but also in restoring up to twist-3 the gauge invariance broken in diagram \ref{fig:handbags}(a) by the different mass of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.
+This diagram and its hermitian conugate are not only important to account for
+all contribution of order $O(1/Q)$, but also in restoring up to twist-3 the
+gauge invariance broken in diagram \ref{fig:handbags}(a) by the different mass
+of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.
 
-Rather than directly using the definition \eqref{e:xi_A}, it is convenient to calculate the inclusive cross section as an integral of the semi-inclusive one, utilize the QCD equation of motions and furthermore summed over all hadron flavors, and take advantage of
+Rather than directly using the definition \eqref{e:xi_A}, it is convenient to
+calculate the inclusive cross section as an integral of the semi-inclusive
+one, utilize the QCD equation of motions and furthermore summed over all
+hadron flavors, and take advantage of  
 \begin{align}
@@
 \end{align}
-where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}.
-In terms of the TMD fragmentation functions we are interested in, this reads
+where $\Delta^h$ is the quark fragmentation correlator for production of a
+hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}. In terms of
+the TMD fragmentation functions we are interested in, this reads 
 \begin{align}
@@
 \end{align}
-where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$ and transverse momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function defined in \cite{Bacchetta:2006tn}.
+where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a
+function of the hadron's collinear momentum fraction $z$ and transverse
+momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function
+defined in \cite{Bacchetta:2006tn}.
 
@@
 The relevant part of the semi-inclusive hadronic tensor for our analysis is 
-\todo{[AA] I am using the notation in Piet Mulder's lecture notes - this will need to be checked.}
 \begin{align}
@@
 Here and we reintroduced the quark flavor $q$ for maximum clarity, and $e_q$ its electric charge.
-The first term can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS_TMDlevel}.
-To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{Bacchetta:2006tn}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
+The first term can be easily integrated with the help of the sum rule
+\eqref{eq:SIDIS_to_DIS_TMDlevel}. To integrate the latter, we first need make
+use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a
+consequence of the QCD equations of motion \cite{Bacchetta:2006tn}, then
+utilize the sum rule \eqref{eq:SIDIS_to_DIS}: 
 \begin{align}
@@
 
-The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function. Following the derivation in Ref.~\cite{ABMS}, one finds
+The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
 \begin{align}
@@
 terms coincide with the result obtained in the conventional handbag
-approximation \cite{ABMS}, while the fifth is new.
+approximation \cite{Accardi:2009au}, while the fifth is new.
 
@@
 
-It is important to estimate the size of teh variou scontributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
+It is important to estimate the size of the variou scontributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
 \begin{align}
@@
 $g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
-elements, we show a model calculation by Braun et al. \cite{Braun-et-al}; for
+elements, we show a model calculation by Braun et al.~\cite{Braun:2011aw}; for
 other estimates, see \cite{Other-tw3-calcs}. To estimate the contributions
@@
 
-As one can see, in the proton case the pure twist-3 contribution is quite smaller in magnitude, and opposite in sign, compared to the JAM15 fit.
-As expected, the quark-mass contribution is essentially negligible and cannot reconcile these two.
-Even though the uncertainties in the $h_1$ extraction and even more the estimate of $M_q$ are large, it is quite clear that the gap between the pure twist-3 $g_2^{tw3}$ function and the JAM15 fit can be explained by the new jet-mass contribution we discussed in this paper.
+As one can see, in the proton case the pure twist-3 contribution is quite
+smaller in magnitude, and opposite in sign, compared to the JAM15 fit. As
+expected, the quark-mass contribution is essentially negligible and cannot
+reconcile these two. Even though the uncertainties in the $h_1$ extraction and
+even more the estimate of $M_q$ are large, it is quite clear that the gap
+between the pure twist-3 $g_2^{tw3}$ function and the JAM15 fit can be
+explained by the new jet-mass contribution we discussed in this paper.
 
-In the neutron case, the jet contribution is very negative at intermediate to large values of $x$.
-If one trusts the order of magnituse of the $g_2^{tw3}$ calculation by Braun et al., one would conclude that the jet contribution cannot be that large.
-However, the latteris dominated by the $d$ quark's transversity, whose fit suffers from large systematic uncertainties and saturates the negative Soffer bound.Recent deata in $p+p$ collisions indicate, however, that $h_1^d$ is less negative than in the Pavia15 fits, in agreement with the JAM15 fit of the non Wandzura-Wilczek contribution to $g_2$.
-Correspondingly the jet contribution to the proton at $x \approx 0.1$ would become less positive, inproving as well teh agreement with the JAM15 fit.
+In the neutron case, the jet contribution is very negative at intermediate to
+large values of $x$. If one trusts the order of magnituse of the $g_2^{tw3}$
+calculation by Braun et al., one would conclude that the jet contribution
+cannot be that large. However, the latteris dominated by the $d$ quark's
+transversity, whose fit suffers from large systematic uncertainties and
+saturates the negative Soffer bound.Recent deata in $p+p$ collisions indicate,
+however, that $h_1^d$ is less negative than in the Pavia15 fits, in agreement
+with the JAM15 fit of the non Wandzura-Wilczek contribution to
+$g_2$. Correspondingly the jet contribution to the proton at $x \approx 0.1$
+would become less positive, inproving as well the agreement with the JAM15
+fit.
 
@@
 \begin{itemize}
-\item JAM13 neutron has almost 0 twist 3, with small positive contribution at small x.
-Can we use this to highlight teh $g_2^{jet}$ contribution?
-Or maybe as a cnstrain: if Braun is right then $g_2^{jet}(n) \approx -g_2^{tw3}(n)$.
-(still, does not help much for the proton).
-\item In Jam 13, Fig.
-6, it looks like in general the violation of the BC sum rule is a small-x effect --> constraints on h(x) fits?
-This cannot really be checked vs.
-JAM15, that assumes $g_2^(0)$ respects BC.
+\item JAM13 neutron has almost 0 twist 3, with small positive contribution at
+  small x. Can we use this to highlight the $g_2^{jet}$ contribution? Or maybe
+  as a cnstrain: if Braun is right then $g_2^{jet}(n) \approx
+  -g_2^{tw3}(n)$. (still, does not help much for the proton). 
+\item In Jam 13, Fig. 6, it looks like in general the violation of the BC sum
+  rule is a small-x effect --> constraints on h(x) fits? This cannot really be
+  checked vs. JAM15, that assumes $g_2^(0)$ respects BC.  
 \end{itemize}
@@
 calculated by Braun et al. \cite{Braun:2011aw} is shown as a dashed blue line
-(no uncertainty estiamte was provided in teh original reference). 
+(no uncertainty estiamte was provided in the original reference). 
 }
@@
 
-The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{Burkhardt:1970ti,Jaffe:1996zw}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function:
+The zero-th moment corresponds to an extension of the Burkhardt-Cottingham sum
+rule \cite{Burkhardt:1970ti,Jaffe:1996zw}, that appears to be broken by the
+non-perturbative spin-flip contribution from the jet function:  
 \begin{align}
@@
 \end{align}
-This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
-It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe:1996zw}.
+This sum rule, in which the pure twist-3 part does not take part, is a
+consequence of the Lorentz invariance of the DIS cross section, that entails
+$\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. It explicitly displays a
+contribution from spin-flip processes, that are included in the original
+derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show
+up in treatments that only consider free field quark propagators for the
+struck quark \cite{Jaffe:1996zw}.
 
@@
 Even if the BC sun rule is broken by a 
-$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe:1996zw}), we obtain that $h_1(x)/x$ must be integrable.
-This entails a bound on the small $x$ behavior of the transversity,
+$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a
+finite but non-zero number \cite{Jaffe:1996zw}), we obtain that $h_1(x)/x$
+must be integrable. This entails a bound on the small $x$ behavior of the
+transversity, 
 \begin{align}
@@
 \end{align}
-This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is, as yet, very limited, and in general for proper extrapolations when calculating moments.
+This bound will be very useful, \eg, in transversity fits, where the data at
+small $x$ is, as yet, very limited, and in general for proper extrapolations
+when calculating moments.
 
@@
 \end{align}
-where $h_1^q[1] = \int_0^1 \dx $ is the contribution of a quark $q$ to the tensor charge.
-In this case, the transevrsity contribution is a background to the extraction of teh poure twist-3 piece.
-Fortunately, it is a quantity that can be extracted from the lattice \cite{Bhattacharya:2016zcn} or fitted \cite{Pavia15, others, reviews?}.
-Furthermore the new sum rule \eqref{eq:ABsumrule} and bound \eqref{eq:ABbound} promise to improve future transversity fits.
-What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator.
-We will, however, discuss later perspectives on how to measure it.
-Therefore the pure twist-3 part can, in principle, be properly isolated.
+where $h_1^q[1] = \int_0^1 dx $ is the contribution of a quark $q$ to the
+tensor charge. In this case, the transevrsity contribution is a background to
+the extraction of the poure twist-3 piece. Fortunately, it is a quantity that
+can be extracted from the lattice \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} or fitted
+\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}. Furthermore the new sum rule
+\eqref{eq:ABsumrule} and bound \eqref{eq:ABbound} promise to improve future
+transversity fits. What is less obvious is how to calculate $M_q-m_q$ from
+first principles, since this is related to the spectral function of the quark
+propagator. We will, however, discuss later perspectives on how to measure
+it. Therefore the pure twist-3 part can, in principle, be properly isolated.
 
-The third moment is interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe-lectures}, and interpreted as as the average color force experienced by the struck quark as it exits teh nucleon \cite{M.Burkardt}.
-As in the previous case, however, the transversity contribution needs to be subtracted:
+The third moment is interesting because the pure twist-3 part can be related
+to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and interpreted as
+as the average color force experienced by the struck quark as it exits the
+nucleon~\cite{Burkardt:2012sd}.  As in the previous case, however, the
+transversity contribution needs to be subtracted: 
 \begin{align}

### 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
worked on BC discussion

--- 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 \affiliation{
-$^a$Jefferson Lab, Newport News, VA 23606, USA, and
-Hampton University, Hampton, VA 23668, USA \\
+$^a$Hampton University, Hampton, VA 23668, USA,
+and Jefferson Lab, Newport News, VA 23606, USA \\
 $^b$Dipartimento di Fisica, Universit\`a degli Studi di Pavia, and INFN,
@@
 \begin{abstract}
-
+We revisit the standard analysis of inclusive DIS on protons taking into account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons.
+As a consequence, a spin-flip term associated with the invariant mass of this (mini)jet of hadrons is generated non perturbatively, and couples to the target's transversity distribution function.
+In inclusive cross sections, this provides an hitherto neglected and large contribution to the twist-3 part of the $g_2$ structure function, that can explain the discrepancy between recent calculations and fits of this quantity.
+It also provides an extension of the Burkardt-Cottingham sum rule, that puts stringent constraints on the small-$x$ behavior of the transversity function.
+Perspectives to measure the new spin flip term, and applications to spin-1 targets will be briefly discussed.
 \end{abstract}
@@
 It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
-From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
+From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects.
 Taking into account that $J_1 < J_2$, we may therefore expect
@@
 \end{align}
-where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}.
+where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{New_testament}.
 In terms of the TMD fragmentation functions we are interested in, this reads
@@
 \end{align}
-where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$ and transverse momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function defined in \cite{Bacchetta:2006tn}.
+where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$ and transverse momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function defined in \cite{New-testament}.
 
@@
 The first term can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS_TMDlevel}.
-To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{Bacchetta:2006tn}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
+To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{New-testament}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
 \begin{align}
@@
 \end{align}
-This formula is the single most important result of this paper, and provides a
-non perturbative generalization of the commonly used $\int\tilde E =0$ sum
-rule introduced in \cite{Jaffe:1996zw}. Indeed, calculating the jet correlator 
+This formula is the single most important result of this paper, and provides a non perturbative generalization of the commonly used $\int\tilde E =0$ sum rule introduced in \cite{Jaffe-Ji}.
+Indeed, calculating the jet correlator
 on the perturbative vacuum one would obtain, as already discussed, $\mj=\mq$
@@
 The first term is also known as the Wandzura-Wilczeck function $g_2^{WW} =
-g_1^*(x)$ , and contains all the ``pure twist-2'' chiral even contributions to
+-g_1^*(x)$ , and contains all the ``pure twist-2'' chiral even contributions to
 the $g_2$ structure coming from quark-quark correlators. The second and third
@@
 transversity parton distribution function, $h_1$. 
-The former is usually neglected for
-light quarks since it is proportional to $\mq=O$(1 MeV). In the latter term,
+The fourth term is usually neglected for
+light quarks since it is proportional to $\mq=O$(1 MeV). In the last term,
 new in our analysis, the transversity distribution is multiplied by a constant
@@
 
-It is important to estimate the size of teh variou scontributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
+It is important to estimate the size of the various contributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
 \begin{align}
@@
 \end{align} 
-These are comapred in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function
-obtained in the very recent JAM15 fit of polarized DIS asymmetries
-\cite{Sato:2016tuz}, that includes a large amount of precise data at large $x$
-from Jefferson Lab, and simultaneously fits the higher-twist components of in
-$g_1$ and $g_2$ to the data. For the ``pure twist-3'' contribution,
-$g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
-elements, we show a model calculation by Braun et al. \cite{Braun-et-al}; for
-other estimates, see \cite{Other-tw3-calcs}. To estimate the contributions
-from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral
-odd quark-quark matrix elements, we use the recent Pavia15 fit of the
-transversity distribution from Ref.~\cite{Radici:2015mwa}, which is comparable
-also to other 
-extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. Furthermore, we choose the
-values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV.
+These are comapred in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function obtained in the very recent JAM15 fit of polarized DIS asymmetries \cite{JAM15}, that includes a large amount of precise data at large $x$ from Jefferson Lab, and simultaneously fits the higher-twist components of in $g_1$ and $g_2$ to the data.
+For the ``pure twist-3'' contribution, $g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix elements, we show a model calculation by Braun et al.
+\cite{Braun-et-al}; for other estimates, see \cite{Other-tw3-calcs}.
+To estimate the contributions from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral odd quark-quark matrix elements, we use the recent Pavia15 fit of the transversity distribution from Ref.~\cite{Radici:2015mwa}, which is comparable also to other
+extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. Furthermore, we choose the values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV.
 
@@
 \item In Jam 13, Fig.
-6, it looks like in general the violation of the BC sum rule is a small-x effect --> constraints on h(x) fits?
+6, it looks like in general the violation of teh BC sum rule is a small-x effect --> constraints on h(x) fits?
 This cannot really be checked vs.
@@
 \caption{\label{f:g2contrib} 
-Different contributions to the non Wandzura-Wilczek part of the proton (left)
-and neutron (right) $g_2$ structure function compared to the JAM15 fit of the
-$g_2-g_2^{\text{WW}}$ (solid black) \cite{Sato:2016tuz}. The quark and jet
-contributions are shown with a dotted red and a dot-dashed green line
-respectively, with uncertainty bands coming form the Pavia15 fit of the
-transversity function \cite{Radici:2015mwa}. The unceratainty in the choice
-$m_q=5$ GeV and $M_q=100$ GeV is not shown. The pure twist-3 contribution
-calculated by Braun et al. \cite{Braun:2011aw} is shown as a dashed blue line
-(no uncertainty estiamte was provided in teh original reference). 
+Different contributions to the non Wandzura-Wilczek part of the proton (left) and neutron (right) $g_2$ structure function compared to the JAM15 fit of the  $g_2-g_2^{\text{WW}}$ (solid black) \cite{JAM15}.
+The quark and jet contributions are shown with a dotted red and a dot-dashed green line respectively, with uncertainty bands coming form the Pavia15 fit of the transversity function \cite{Pavia15}.
+The unceratainty in the choice $m_q=5$ GeV and $M_q=100$ GeV is not shown.
+The pure twist-3 contribution calculated by Braun et al.
+\cite{Braun-et-al} is shown as a dashed blue line (no uncertainty estiamte was provided in teh original reference).
 }
@@
 
-It is interesting to consider the moments of the non Wandzura-Wilczek contribution to $g-2$,
+It is interesting to consider the moments of the non Wandzura-Wilczek contribution to $g_2$,
 \begin{align}
-  d_N = N \int_0^1 x^N \big( g_2(x) - g_2^{WW}(x) \big) \ .
+  d_N \equiv (N+1) \int_0^1 x^N \bigg( g_2(x) - g_2^{WW}(x) \bigg) \ .
 \end{align}
-For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = N/(N+1) f[N]$ and  
+For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = N/(N+1) \times f[N]$ and  
 \begin{align}
-  d_N & \equiv (N+1) g_2[N] + N g_1[N] \\
+  d_N & = (N+1) g_2[N] + N g_1[N] \\
   & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N] + \hat g_T^q[N]
@@
 \end{align}
-\AAcom{The notation used in JAM15 with $x^{N-1}$ for the Nth moment is pretty awkward here. Should we use $x^N$ instead?}
 
-The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{Burkhardt:1970ti,Jaffe:1996zw}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function:
+The zero-th moment provides an interestign relationship between the longitudinal and tensor spin structure of the target,
 \begin{align}
   \label{eq:BC}
-  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1(x) \ .
+  \int dx\, g_2(x) = \sum_q e_q^2 \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1^q(x) \ ,
 \end{align}
-This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
-It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe:1996zw}.
-
-Assuming the Burkhardt-Cottingham sum rule to be strictly valid, we obtain a strong constraint on the transversity function,
+where we used the fact that $\hat g_T^q[0]=0$ identically due to the symmetry properties of the quark-gluon-quark correlators.
+The sum rule \eqref{eq:BC}, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
+It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{BC} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe-lectures}.
+Assuming the Burkhardt-Cottingham sum rule $\int_0^1 dx\, g_2(x) =0$, that is derived at the cross section level (under suitable assumptions on teh high-energy behavior of te hspin-flip amplitude) rather than from an analysis of collinear correlators, as done here, to be strictly valid, we obtain a strong constraint on the transversity function,
 \begin{align}
-   \int dx\, \frac{1}{x} h_1(x) = 0 \ .
+   \int dx\, \frac{1}{x} h_1^q(x) = 0 \ .
 \label{eq:ABsumrule}
 \end{align}
-Even if the BC sun rule is broken by a 
-$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe:1996zw}), we obtain that $h_1(x)/x$ must be integrable.
+Interestingly, one can show that this constraint, if valid at any given scale $Q_0$ is conserved through QCD evolution.
+Even if the BC sum rule is broken either by a $J = 0$ fixed pole with non-polynomial residue \cite{Jaffe-lectures} or explicitly as, \eg, in the quark target model \cite{Metz-Kundu)} -- i.e., if $g_2$ integrates to a finite but non-zero number -- we obtain that $h_1(x)/x$ must be integrable.
 This entails a bound on the small $x$ behavior of the transversity,
 \begin{align}
-  h_1(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
+  h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
 \label{eq:ABbound}
@@
 \end{align}
-where $h_1^q[1] = \int_0^1 \dx $ is the contribution of a quark $q$ to the tensor charge.
-In this case, the transevrsity contribution is a background to the extraction of teh poure twist-3 piece.
-Fortunately, it is a quantity that can be extracted from the lattice \cite{Bhattacharya:2016zcn} or fitted \cite{Pavia15, others, reviews?}.
-Furthermore the new sum rule \eqref{eq:ABsumrule} and bound \eqref{eq:ABbound} promise to improve future transversity fits.
-What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator.
-We will, however, discuss later perspectives on how to measure it.
-Therefore the pure twist-3 part can, in principle, be properly isolated.
-
-The third moment is interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe-lectures}, and interpreted as as the average color force experienced by the struck quark as it exits teh nucleon \cite{M.Burkardt}.
-As in the previous case, however, the transversity contribution needs to be subtracted:
+where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the tensor charge. 
+The third moment is also interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe-lectures}, and interpreted as as the average color force experienced by the struck quark as it exits the nucleon \cite{M.Burkardt}:
 \begin{align}
@@
 \end{align}
+In both of these cases, the transversity contribution is a background to the extraction of the pure twist-3 piece.
+Fortunately, it is a quantity that can be extracted from the lattice \cite{Bhattacharya:2016zcn} or fitted \cite{Pavia15, others, reviews?}.
+Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound \eqref{eq:ABbound} promise to improve future transversity fits.
+What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator.
+We will, however, briefly discuss perspectives on how to measure it.
+Therefore the pure twist-3 part can, in principle, be properly isolated.
+
+\begin{figure}[tbh]
+  \centering
+  \parbox[b]{8cm}{\centering
+  \includegraphics
+      [width=7cm,clip=true]
+      {epl_emn_h_X.eps}
+  }
+  \parbox[b]{8cm}{\vskip-0.5cm\centering
+  \includegraphics
+      [width=7cm,clip=true]
+      {epl_emn_h_h_X.eps}
+  }
+  \caption{\small
+	Single hadron {\it (left)} and double hadron {\it (right)}
+	production in $e^+ e^-$ collisions at LO with jet and
+	fragmentation correlators.
+  }
+  \label{fig:epl_emn_h}
+\end{figure}
+
+A promising avenue to experimentally access jet functions is, however, through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
+production from the same hemisphere, $e^+ e^- \to h h X$, see 
+Fig.~\ref{fig:epl_emn_h}.
+In single-hadron production, the fragmentation functions $D_h$
+play the role of PDFs in DIS, and couple to the jet functions
+in an analogous way.
+In double hadron production the enlarged number of Dirac structures
+of the dihadron fragmentation correlator $D_{2h}$ allows one to access
+the jet function in novel ways, and in particular to isolate the
+contribution from the helicity-flip $J_0$ term.
+Studying and classifying all the possibilities offered by single and
+double hadron production will open up a rich phenom, which will in turn
+be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.
 

### 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex

--- 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 
-It is important to estimate the size of the variou scontributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
+It is important to estimate the size of the various contributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
 \begin{align}
@@
 \end{align}
-\AAcom{The notation used in JAM15 with $x^{N-1}$ for the Nth moment is pretty awkward here. Should we use $x^N$ instead?}
 
-The zero-th moment corresponds to an extension of the Burkhardt-Cottingham sum
-rule \cite{Burkhardt:1970ti,Jaffe:1996zw}, that appears to be broken by the
-non-perturbative spin-flip contribution from the jet function:  
+The zero-th moment provides an interesting relationship between the longitudinal and tensor spin structure of the target,
 \begin{align}
   \label{eq:BC}
-  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1(x) \ .
+  \int dx\, g_2(x) = \sum_q e_q^2 \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1^q(x) \ ,
 \end{align}
-This sum rule, in which the pure twist-3 part does not take part, is a
-consequence of the Lorentz invariance of the DIS cross section, that entails
-$\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. It explicitly displays a
-contribution from spin-flip processes, that are included in the original
-derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show
-up in treatments that only consider free field quark propagators for the
-struck quark \cite{Jaffe:1996zw}.
-
-Assuming the Burkhardt-Cottingham sum rule to be strictly valid, we obtain a strong constraint on the transversity function,
+where we used the fact that $\hat g_T^q[0]=0$ identically due to the symmetry properties of the quark-gluon-quark correlators.
+The sum rule \eqref{eq:BC}, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
+It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe:1996zw}.
+Assuming the Burkhardt-Cottingham sum rule $\int_0^1 dx\, g_2(x) =0$, that is derived at the cross section level (under suitable assumptions on teh high-energy behavior of te hspin-flip amplitude) rather than from an analysis of collinear correlators, as done here, to be strictly valid, we obtain a strong constraint on the transversity function,
 \begin{align}
-   \int dx\, \frac{1}{x} h_1(x) = 0 \ .
+   \int dx\, \frac{1}{x} h_1^q(x) = 0 \ .
 \label{eq:ABsumrule}
 \end{align}
-Even if the BC sun rule is broken by a 
-$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a
-finite but non-zero number \cite{Jaffe:1996zw}), we obtain that $h_1(x)/x$
-must be integrable. This entails a bound on the small $x$ behavior of the
-transversity, 
+Interestingly, one can show that this constraint, if valid at any given scale $Q_0$ is conserved through QCD evolution.
+Even if the BC sum rule is broken either by a $J = 0$ fixed pole with non-polynomial residue \cite{Jaffe:1996zw} or explicitly as, \eg, in the quark target model \cite{Metz-Kundu} -- i.e., if $g_2$ integrates to a finite but non-zero number -- we obtain that $h_1(x)/x$ must be integrable.
+This entails a bound on the small $x$ behavior of the transversity,
 \begin{align}
-  h_1(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
+  h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
 \label{eq:ABbound}
@@
 \end{align}
-where $h_1^q[1] = \int_0^1 dx $ is the contribution of a quark $q$ to the
-tensor charge. In this case, the transevrsity contribution is a background to
-the extraction of the poure twist-3 piece. Fortunately, it is a quantity that
-can be extracted from the lattice \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} or fitted
-\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}. Furthermore the new sum rule
-\eqref{eq:ABsumrule} and bound \eqref{eq:ABbound} promise to improve future
-transversity fits. What is less obvious is how to calculate $M_q-m_q$ from
-first principles, since this is related to the spectral function of the quark
-propagator. We will, however, discuss later perspectives on how to measure
-it. Therefore the pure twist-3 part can, in principle, be properly isolated.
-
-The third moment is interesting because the pure twist-3 part can be related
-to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and interpreted as
-as the average color force experienced by the struck quark as it exits the
-nucleon~\cite{Burkardt:2012sd}.  As in the previous case, however, the
-transversity contribution needs to be subtracted: 
+where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the tensor charge. 
+The third moment is also interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see  \cite{Jaffe:1996zw}, and interpreted as as the average color force experienced by the struck quark as it exits the nucleon \cite{Burkardt:2012sd}:
 \begin{align}
@@
 \end{align}
+In both of these cases, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
+\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} or fitted
+\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
+Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound \eqref{eq:ABbound} promise to improve future transversity fits.
+What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator.
+We will, however, briefly discuss perspectives on how to measure it.
+Therefore the pure twist-3 part can, in principle, be properly isolated.
+
+\begin{figure}[tbh]
+  \centering
+  \parbox[b]{8cm}{\centering
+  \includegraphics
+      [width=7cm,clip=true]
+      {epl_emn_h_X.eps}
+  }
+  \parbox[b]{8cm}{\vskip-0.5cm\centering
+  \includegraphics
+      [width=7cm,clip=true]
+      {epl_emn_h_h_X.eps}
+  }
+  \caption{\small
+	Single hadron {\it (left)} and double hadron {\it (right)}
+	production in $e^+ e^-$ collisions at LO with jet and
+	fragmentation correlators.
+  }
+  \label{fig:epl_emn_h}
+\end{figure}
+
+A promising avenue to experimentally access jet functions is, however, through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
+production from the same hemisphere, $e^+ e^- \to h h X$, see 
+Fig.~\ref{fig:epl_emn_h}.
+In single-hadron production, the fragmentation functions $D_h$
+play the role of PDFs in DIS, and couple to the jet functions
+in an analogous way.
+In double hadron production the enlarged number of Dirac structures
+of the dihadron fragmentation correlator $D_{2h}$ allows one to access
+the jet function in novel ways, and in particular to isolate the
+contribution from the helicity-flip $J_0$ term.
+Studying and classifying all the possibilities offered by single and
+double hadron production will open up a rich phenom, which will in turn
+be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.
 

### 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
some refinements

@@
 cut-diagram, even if none of the hadrons is detected in the final
-state. For a proper description of this effect, we include ``jet
-correlators'' into the analysis. We pay particular attention to ensuring that our
-results are gauge invariant. We observe that the inclusion of jet correlators
-introduces a new
+state. For a proper description of this effect, we include proper ``jet
+correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant. We observe that the inclusion of jet correlators introduces a new
 contribution to the inclusive $g_2$ structure function. This term has the
@@
 proportional to the transversity distribution function multiplied by a
-nonperturbative ``jet mass'' parameter, probably much larger than the mass of light
-quarks. 
-We provide estimates of this
-contribution based on a recent extraction of transversity and show that it
-could be very large.
+nonperturbative ``jet mass'' parameter, likely much larger than the mass of light quarks.
+We provide estimates of this contribution based on a recent extraction of transversity and show that it could be very large.
 
@@
 elements, we show a model calculation by Braun et al.~\cite{Braun:2011aw}; for
-other estimates, see \cite{Other-tw3-calcs}. To estimate the contributions
+(modified) bag model calculations, see \cite{Jaffe:1990qh,Stratmann:1993aw}. To estimate the contributions
 from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral
@@
 expected, the quark-mass contribution is essentially negligible and cannot
-reconcile these two. Even though the uncertainties in the $h_1$ extraction and
-even more the estimate of $M_q$ are large, it is quite clear that the gap
+reconcile these two. Even though the uncertainties in the $h_1$ extraction, and
+even more in the estimate of $M_q$, are large, it is quite clear that the gap
 between the pure twist-3 $g_2^{tw3}$ function and the JAM15 fit can be
@@
 calculation by Braun et al., one would conclude that the jet contribution
-cannot be that large. However, the latteris dominated by the $d$ quark's
+cannot be that large. However, the latter is dominated by the $d$ quark's
 transversity, whose fit suffers from large systematic uncertainties and
@@
 It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe:1996zw}.
-Assuming the Burkhardt-Cottingham sum rule $\int_0^1 dx\, g_2(x) =0$, that is derived at the cross section level (under suitable assumptions on teh high-energy behavior of te hspin-flip amplitude) rather than from an analysis of collinear correlators, as done here, to be strictly valid, we obtain a strong constraint on the transversity function,
+Since $h_1$ is driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule $\int_0^1 dx\, g_2(x) =0$ is satisfied at least asymptotically.
+At finite scales, assuming the Burkhardt-Cottingham sum rule, that is derived at the cross section level (under suitable assumptions on the high-energy behavior of te hspin-flip amplitude) rather than from an analysis of collinear correlators, as done here, to be strictly valid, we obtain a strong constraint on the transversity function,
 \begin{align}
@@
 \end{align}
-In both of these cases, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
+In both cases, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} or fitted

### 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
Some corrections

@@
 here the full QCD vacuum rather than the perturbative one.  
-The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral representation of the cut quark propagator \cite{D'Hoker-lecture-notes,Romao-lecture-notes},
+The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral
+representation of the cut quark propagator (see, e.g., Sec.~6.3 of
+\cite{D'Hoker:2004aa} and Sec.~2.7.2 of \cite{Romao:2013aa}),
 \begin{align} 
@@
 quark propagator, that have been also called ``jet functions'' in
-\cite{Accardi:2008ne,SCET?}. These satisfy
+\cite{Accardi:2008ne}. These satisfy
 \begin{align}
@@
 It is important to notice that $\xi_2=1$ exactly due to CPT invariance
-\cite{Weinberg:1995mt}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is
+(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is
 dynamically determined. From the analytic properties of spectral functions we
@@
   \label{eq:mjet}
-  \mj = O(10-100 \text{ MeV}) \ .
+  \mj = O(10^2 \text{ MeV}) \ .
 \end{align}
@@
 % (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.}
-Calculating this on the perturbative vacuum and limiting oneself to LO
+Calculating this on the perturbative vacuum and to leading order
 corresponds to taking the trace of the cut bare-quark propagator to obtain 
@@
 \end{equation}  
-This diagram and its hermitian conugate are not only important to account for
-all contribution of order $O(1/Q)$, but also in restoring up to twist-3 the
-gauge invariance broken in diagram \ref{fig:handbags}(a) by the different mass
+This diagram and its Hermitian conjugate are not only important to account for
+all contribution of order $O(1/Q)$, but also to restore the
+gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
 of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.
@@
 \end{align}
-Here and we reintroduced the quark flavor $q$ for maximum clarity, and $e_q$ its electric charge.
+For clarity, here we reintroduced the quark flavor $q$, $e_q$ being its electric charge.
 The first term can be easily integrated with the help of the sum rule
@@
 consequence of the QCD equations of motion \cite{Bacchetta:2006tn}, then
-utilize the sum rule \eqref{eq:SIDIS_to_DIS}: 
+make use of the sum rule \eqref{eq:SIDIS_to_DIS}: 
 \begin{align}
@@
 
-Finally, with suitable projections of the hadronic tensor, the inclusive cross section up to order $\Lambda/Q$ can be written as
+Finally, the contraction of the hadronic tensor with the leptonic tensor leads
+to the following well known result for the inclusive DIS cross section up to order $\Lambda/Q$~\cite{Bacchetta:2006tn}
 \begin{align}
@@
 \end{align}
-where the structure functions on the right hand side are defined as
+where the structure functions on the right hand side correspond to
 \begin{align}
@@
 The second term in the last structure function is a new result from our
-analysis; it is not suppressed as an inverse power of $Q$, and therefore
-survives even in the Bjorken limit. On the non-perturbative
+analysis; it is not suppressed as an inverse power of $Q$ compared to the
+standard term. On the nonperturbative
 vacuum the jet mass is larger than the quark's, and this contributes a
-non-negligible term to the twist-3 part of the $g_2$ function, as we will
+nonnegligible term to the twist-3 part of the $g_2$ function, as we will
 discuss in the next section.
@@
 \end{align}
-where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$. The first 4
+where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$. The first four
 terms coincide with the result obtained in the conventional handbag
@@
 The first term is also known as the Wandzura-Wilczeck function $g_2^{WW} =
--g_1^*(x)$ , and contains all the ``pure twist-2'' chiral even contributions to
+-g_1^*(x)$ , and contains all the twist-2 chiral-even contributions to
 the $g_2$ structure coming from quark-quark correlators. The second and third
@@
 \begin{align}
-g_2^{tw3} & = \frac{1}{2}\,\sum_a e_a^2
+g_2^{\rm tw3} & = \frac{1}{2}\,\sum_a e_a^2
     \biggl(
@@
 \end{align} 
-These are comapred in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function
+These are compared in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function
 obtained in the very recent JAM15 fit of polarized DIS asymmetries
@@
 $g_1$ and $g_2$ to the data. For the ``pure twist-3'' contribution,
-$g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
+$g_2^{\rm tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
 elements, we show a model calculation by Braun et al.~\cite{Braun:2011aw}; for
 (modified) bag model calculations, see \cite{Jaffe:1990qh,Stratmann:1993aw}. To estimate the contributions
-from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral
+from quark ($g_2^q$) and jet mass ($g_2^{\rm jet}$) effects, that depend on chiral
 odd quark-quark matrix elements, we use the recent Pavia15 fit of the
@@
 even more in the estimate of $M_q$, are large, it is quite clear that the gap
-between the pure twist-3 $g_2^{tw3}$ function and the JAM15 fit can be
+between the pure twist-3 $g_2^{\rm tw3}$ function and the JAM15 fit can be
 explained by the new jet-mass contribution we discussed in this paper.
@@
 In the neutron case, the jet contribution is very negative at intermediate to
-large values of $x$. If one trusts the order of magnituse of the $g_2^{tw3}$
+large values of $x$. If one trusts the order of magnituse of the $g_2^{\rm tw3}$
 calculation by Braun et al., one would conclude that the jet contribution
@@
 \item JAM13 neutron has almost 0 twist 3, with small positive contribution at
-  small x. Can we use this to highlight the $g_2^{jet}$ contribution? Or maybe
-  as a cnstrain: if Braun is right then $g_2^{jet}(n) \approx
-  -g_2^{tw3}(n)$. (still, does not help much for the proton). 
+  small x. Can we use this to highlight the $g_2^{\rm jet}$ contribution? Or maybe
+  as a cnstrain: if Braun is right then $g_2^{\rm jet}(n) \approx
+  -g_2^{\rm tw3}(n)$. (still, does not help much for the proton). 
 \item In Jam 13, Fig. 6, it looks like in general the violation of the BC sum
@@
 Interestingly, one can show that this constraint, if valid at any given scale $Q_0$ is conserved through QCD evolution.
-Even if the BC sum rule is broken either by a $J = 0$ fixed pole with non-polynomial residue \cite{Jaffe:1996zw} or explicitly as, \eg, in the quark target model \cite{Metz-Kundu} -- i.e., if $g_2$ integrates to a finite but non-zero number -- we obtain that $h_1(x)/x$ must be integrable.
+Even if the BC sum rule is broken either by a $J = 0$ fixed pole with non-polynomial residue \cite{Jaffe:1996zw} or explicitly as, \eg, in the quark target model \cite{Kundu:2001pk} -- i.e., if $g_2$ integrates to a finite but nonzero number -- we obtain that $h_1(x)/x$ must be integrable.
 This entails a bound on the small $x$ behavior of the transversity,
@@
       [width=7cm,clip=true]
-      {epl_emn_h_X.eps}
+      {epl_emn_h_X}
   }
@@
       [width=7cm,clip=true]
-      {epl_emn_h_h_X.eps}
+      {epl_emn_h_h_X}
   }

### 2016-07-27 1607 - JMC for g2/Paper/JMC_dis.tex
Changes, especially in last part

@@
 terms coincide with the result obtained in the conventional handbag
-approximation \cite{Accardi:2009au}, while the fifth is new.
+approximation \cite{Accardi:2009au}, while the fifth is new. Note that even if
+the relation is written for the sum of the quark weighted by their charge
+squared, it can be considered valid also flavor by flavor. In fact, the steps
+leading to such a decomposition are formulated at the correlator level.
 
@@
 \begin{align}
-g_2^{\rm tw3} & = \frac{1}{2}\,\sum_a e_a^2
+g_2^{\rm tw3} & = \frac{1}{2}\,\sum_q e_q^2
     \biggl(
-    \widetilde g_T^{a \star}(x) 
+    \widetilde g_T^{q \star}(x) 
     + \int_x^1\frac{dy}{y} \widehat{g}_T^q(y) 
@@
 &
-g_2^{\text{quark}} &= \frac{1}{2}\,\sum_a e_a^2 
+g_2^{\text{quark}} &= \frac{1}{2}\,\sum_q e_q^2 
  \frac{\mq}{\Lambda} (h_1^q/x)^\star(x),
 &
-g_2^{\text{jet}} &= \frac{1}{2}\,\sum_a e_a^2 
+g_2^{\text{jet}} &= \frac{1}{2}\,\sum_q e_q^2 
 \frac{\mj-\mq}{\Lambda} \frac{h_1^q(x)}{x}. 
@@
 smaller in magnitude, and opposite in sign, compared to the JAM15 fit. As
-expected, the quark-mass contribution is essentially negligible and cannot
-reconcile these two. Even though the uncertainties in the $h_1$ extraction, and
-even more in the estimate of $M_q$, are large, it is quite clear that the gap
+expected, the quark-mass contribution is essentially negligible. 
+For what concerns the jet-mass contribution, the uncertainties due to the $h_1$
+extraction are very large, especially at low $x$. In addition, there is an
+overall normalization uncertainty due to the choice of $\mj$, not shown in the
+plot. In any case, the jet-mass contribution is strikingly large. If we assume
+that the pure twist-3 contributions are of the order of the model calculation
+by Braun et al., the breaking of the Wandura-Wilczek relation can be used to
+constrain the extractions of the transversity distribution, in particular at
+low $x$. 
+Moreover, it is quite clear that the gap
 between the pure twist-3 $g_2^{\rm tw3}$ function and the JAM15 fit can be
@@
 In the neutron case, the jet contribution is very negative at intermediate to
-large values of $x$. If one trusts the order of magnituse of the $g_2^{\rm tw3}$
+large values of $x$. 
+If one trusts the order of magnitude of the $g_2^{\rm tw3}$
 calculation by Braun et al., one would conclude that the jet contribution
-cannot be that large. However, the latter is dominated by the $d$ quark's
+should not be that large. However, the jet contribution is strongly influenced
+by the $d$ quark's
 transversity, whose fit suffers from large systematic uncertainties and
-saturates the negative Soffer bound.Recent deata in $p+p$ collisions indicate,
-however, that $h_1^d$ is less negative than in the Pavia15 fits, in agreement
-with the JAM15 fit of the non Wandzura-Wilczek contribution to
-$g_2$. Correspondingly the jet contribution to the proton at $x \approx 0.1$
+saturates the negative Soffer bound. Recent deata in $p+p$ collisions indicate,
+however, that $h_1^d$ might be less negative than in the Pavia15
+fits~\cite{Radici:2016lam}.
+Correspondingly the jet contribution to the proton at $x \approx 0.1$
 would become less positive, inproving as well the agreement with the JAM15
 fit.
-
-\begin{itemize}
-\item smaller-$x$: constrains the small-$x$ behavior of transversity.
-\end{itemize}
-Some ideas to check:
-\begin{itemize}
-\item JAM13 neutron has almost 0 twist 3, with small positive contribution at
-  small x. Can we use this to highlight the $g_2^{\rm jet}$ contribution? Or maybe
-  as a cnstrain: if Braun is right then $g_2^{\rm jet}(n) \approx
-  -g_2^{\rm tw3}(n)$. (still, does not help much for the proton). 
-\item In Jam 13, Fig. 6, it looks like in general the violation of the BC sum
-  rule is a small-x effect --> constraints on h(x) fits? This cannot really be
-  checked vs. JAM15, that assumes $g_2^(0)$ respects BC.  
-\end{itemize}
 
@@
 calculated by Braun et al. \cite{Braun:2011aw} is shown as a dashed blue line
-(no uncertainty estiamte was provided in the original reference). 
+(no uncertainty estimate was provided in the original reference). 
 }
@@
 
-The zero-th moment provides an interesting relationship between the longitudinal and tensor spin structure of the target,
+The zero-th moment provides an interesting relationship between transversity
+and the inclusive structure function $g_2$:
 \begin{align}
@@
 \end{align}
-where we used the fact that $\hat g_T^q[0]=0$ identically due to the symmetry properties of the quark-gluon-quark correlators.
-The sum rule \eqref{eq:BC}, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
-It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe:1996zw}.
-Since $h_1$ is driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule $\int_0^1 dx\, g_2(x) =0$ is satisfied at least asymptotically.
-At finite scales, assuming the Burkhardt-Cottingham sum rule, that is derived at the cross section level (under suitable assumptions on the high-energy behavior of te hspin-flip amplitude) rather than from an analysis of collinear correlators, as done here, to be strictly valid, we obtain a strong constraint on the transversity function,
+where we used the fact that $\hat g_T^q[0]=0$ identically due to the symmetry
+properties of the quark-gluon-quark correlators. 
+The sum rule \eqref{eq:BC}
+generalizes the Burkhardt-Cottingham (BC) sum rule~\cite{Burkhardt:1970ti},
+which states that  $\int_0^1 dx\, g_2(x) =0$. 
+However, we show that jet-mass corrections violate the BC sum rule. The
+possibility of a violation of the sum rule due to 
+contributions from spin-flip
+processes was already mentioned in the original
+derivation~\cite{Burkhardt:1970ti}, 
+but do not show up in treatments that only
+consider free field quark propagators for the struck quark
+\cite{Jaffe:1996zw}. Since $h_1$ is driven to 0 by QCD evolution as $Q^2 \to
+\infty$, the BC sum rule $\int_0^1 dx\, g_2(x) =0$ is satisfied at least
+asymptotically. Although we formulated \eqref{eq:BC} in terms of sum over quark flavors in order to display a clear
+connection to the structure function $g_2$, we stress that it is valid also
+flavor by flavor, i.e., for each single flavor the only measurable nonzero contribution to the zeroth moment of the
+structure function $g_2$ can come from the jet-mass
+corrections and transversity.\footnote{This conclusion is true even if the BC sum rule is broken by a $J = 0$ fixed pole with
+non-polynomial residue \cite{Jaffe:1996zw}, since this would appear as a
+$\delta(x)$ contribution and would not be measurable.}
+The fact that $g_2^{\text{quark}}$ disappears in the zeroth moment
+of $g_2$ is due to the definition of the $\ast$ functions. The fact that $g_2^{\rm tw3}$
+disappears is due to the symmetry properties of $\widehat{g}_T^q$, or
+equivalently  is a consequence of the
+Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) =
+\int_0^1 g_T^q(x)$.
+
+At finite scales, the only way to preserve the validity of the
+Burkhardt-Cottingham sum rule is if
+%that is derived at the cross section level (under suitable assumptions on the
+%high-energy behavior of te hspin-flip amplitude) rather than from an analysis
+%of collinear correlators, as done here, 
+%to be strictly valid, we obtain a
+%strong constraint on the transversity function, 
 \begin{align}
@@
 \end{align}
-Interestingly, one can show that this constraint, if valid at any given scale $Q_0$ is conserved through QCD evolution.
-Even if the BC sum rule is broken either by a $J = 0$ fixed pole with non-polynomial residue \cite{Jaffe:1996zw} or explicitly as, \eg, in the quark target model \cite{Kundu:2001pk} -- i.e., if $g_2$ integrates to a finite but nonzero number -- we obtain that $h_1(x)/x$ must be integrable.
-This entails a bound on the small $x$ behavior of the transversity,
+Interestingly, one can show that this constraint, if valid at any given scale
+$Q_0$ is conserved through QCD evolution. However, we think that this
+constrain cannot be satisfied in general, since it is broken in perturbative
+QCD~\cite{Kundu:2001pk} and models (see, e.g., \cite{}).
+
+E or explicitly as, \eg, in the quark
+target model \cite{Kundu:2001pk} -- i.e., if $g_2$ integrates to a finite but
+nonzero number -- 
+If we assume that the BC sum rule is broken by a {\em finite} amount, we
+obtain that $h_1(x)/x$ must be integrable, implying a 
+a bound on the small $x$ behavior of the transversity, 
 \begin{align}

### 2016-07-28 1607 - JMC for g2/Paper/JMC_dis.tex
Added bib and bst files

@@
 transversity cannot be accessed in inclusive DIS,
-but only in more complex processes such as semi-inclusive DIS or Drell-Yan~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1993kk}.
+but only in more complex processes such as semi-inclusive DIS or Drell-Yan~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1992kk}.
 
@@
 \bibliographystyle{myrevtex}
-\bibliography{mybiblio}
+\bibliography{jetbiblio}
 

### 2016-07-28 1607 - JMC for g2/Paper/JMC_dis.tex
Added references

@@
 constrain cannot be satisfied in general, since it is broken in perturbative
-QCD~\cite{Kundu:2001pk} and models (see, e.g., \cite{}).
+QCD~\cite{Kundu:2001pk} and models (see, e.g., \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}).
 
-E or explicitly as, \eg, in the quark
-target model \cite{Kundu:2001pk} -- i.e., if $g_2$ integrates to a finite but
-nonzero number -- 
 If we assume that the BC sum rule is broken by a {\em finite} amount, we
@@
 \end{align}
-This bound will be very useful, \eg, in transversity fits, where the data at
+This bound can be very useful, \eg, in transversity fits, where the data at
 small $x$ is, as yet, very limited, and in general for proper extrapolations
@@
 where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the tensor charge.
-The third moment is also interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and interpreted as as the average color force experienced by the struck quark as it exits the nucleon \cite{Burkardt:2012sd}:
+
+The second moment is also interesting because the pure twist-3 part can be
+related to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and
+interpreted as as the average color force experienced by the struck quark as
+it exits the nucleon \cite{Burkardt:2012sd}: 
 \begin{align}
@@
 \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
-Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound \eqref{eq:ABbound} promise to improve future transversity fits.
-What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator.
-We will, however, briefly discuss perspectives on how to measure it.
-Therefore the pure twist-3 part can, in principle, be properly isolated.
+Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound
+\eqref{eq:ABbound} promise to improve future transversity fits. What is less
+obvious is how to calculate $M_q-m_q$ from first principles, since this is
+related to the spectral function of the quark propagator. We will, however,
+briefly discuss perspectives on how to measure it. Therefore the pure twist-3
+part can, in principle, be properly isolated. For experimental
+measurements of $d_2$, see, e.g., Refs.~\cite{Anthony:2002hy,Slifer:2008xu,Solvignon:2013yun,Posik:2014usi,Flay:2016wie}.
 

### 2016-07-29 1607 - JMC for g2/Paper/JMC_dis.tex
small changes

--- 2016-07-27 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 + \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
-+ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ .
++ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ ,
 \label{e:jetexpansion}
 \end{equation} 
-Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes
-only at twist-4 order, and will not be considered further in this paper. We
-focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3. At this order, 
+where $\Lambda$ is an arbitrary scale, introduced for power counting purposes.
+In this parametrization, no terms proportional to $\gamma_5$ enters because of parity invariance.
+Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes only at twist-4 order, and will not be considered further in this paper.
+We focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3.
+At this order,
 \begin{equation}
@@
 \end{equation} 
-is nothing else than the full quark propagator; note however, that we consider
-here the full QCD vacuum rather than the perturbative one.  
+is nothing else than the cut quark propagator; note however, that we consider
+here the full QCD vacuum rather than the perturbative one (or, in other words, teh interacting rather than teh free quark fields).
 The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral

### 2016-08-01 1607 - JMC for g2/Paper/JMC_dis.tex
Some conclusions added

--- 2016-07-28 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 \begin{abstract}
-We revisit the standard analysis of inclusive DIS on protons taking into account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons.
-As a consequence, a spin-flip term associated with the invariant mass of this (mini)jet of hadrons is generated non perturbatively, and couples to the target's transversity distribution function.
-In inclusive cross sections, this provides an hitherto neglected and large contribution to the twist-3 part of the $g_2$ structure function, that can explain the discrepancy between recent calculations and fits of this quantity.
-It also provides an extension of the Burkardt-Cottingham sum rule, that puts stringent constraints on the small-$x$ behavior of the transversity function.
-Perspectives to measure the new spin flip term, and applications to spin-1 targets will be briefly discussed.
+We revisit the standard analysis of inclusive Deep Inelastic Scattering (DIS)
+off nucleons taking into
+account the fact that on-shell quarks cannot be present in the final state,
+but they rather decay into hadrons. As a consequence, a spin-flip term
+associated with the invariant mass of the produced hadrons is generated
+non perturbatively, and couples to the target's transversity distribution
+function. In inclusive cross sections, this provides an hitherto neglected and
+large contribution to the twist-3 part of the $g_2$ structure function, that
+can explain the discrepancy between recent calculations and fits of this
+quantity. It also provides an extension of the Burkardt-Cottingham sum rule,
+that puts constraints on the small-$x$ behavior of the transversity
+function and can help constraining the nucleon tensor charge.
+%Perspectives to measure the new spin-flip term, and applications to
+%spin-1 targets will be briefly discussed. 
 \end{abstract}
@@
 
-A promising avenue to experimentally access jet functions is, however, through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
+To experimentally measure jet functions and in particular the jet mass parameter, a promising avenue is throug inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
 production from the same hemisphere, $e^+ e^- \to h h X$, see 
@@
 In double hadron production the enlarged number of Dirac structures
-of the dihadron fragmentation correlator $D_{2h}$ allows one to access
+of the dihadron fragmentation correlator allows one to access
 the jet function in novel ways, and in particular to isolate the
-contribution from the helicity-flip $J_0$ term.
+contribution from the helicity-flip $J_0$ term in combination with the
+chiral-odd fragmentation function $H_1^{\sphericalangle}$.
 Studying and classifying all the possibilities offered by single and
-double hadron production will open up a rich phenom, which will in turn
+double hadron production will open up a rich phenomenology, which will in turn
 be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.
-
-{\bf [---------------- AA:  EDITED down here --------------------]}
-
-It is important to explore in which other process does $\mj$ contribute, as to provide an experimental check of the formalism:
-\begin{itemize}
-\item inclusive $\Lambda$ production in $e^+ + e^-$
-\item same-side dihadrons in $e^+ + e^-$ 
-\end{itemize}
-\todo{It would be cool to find a process where the $\mj$ contribution is the only one (similar to the BC breaking) ...}
 
@@
 \section{Conclusions}
+
+In this paper, we revisited the analysis of inclusive DIS, including the
+effects due to the production of a system of final state hadrons, which we
+conveniently referred to as ``jet.'' We described the jet in terms of a jet
+correlator, corresponding to a 
+nonperturbative cut propagator, different from the standard
+perturbative propagator. We
+carried out the
+analysis of the jet correlator up to twist-3 level. The introduction of this jet correlator
+leads to a difference in the expression of the structure function $g_2$ in
+inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass
+parameter and to the transversity distribution function. This new term
+contributes to the violation of the Wandzura-Wilczek relation, in addition to
+the standard pure twist-3 terms and quark mass corrections. Contrary to these
+standard terms, however, the new jet mass correction violates also the
+Burkhardt-Cottingham sum rule. This is yet another example of how surprising
+and rich the phenomenology of polarized inclusive DIS can be. Detailed measurements of the $g_2$ structure
+function can be used to constrain the jet mass parameter, the transversity
+distribution function and the nucleon tensor charge, helping their extraction from other observables in, e.g.,
+electron-positron annihilation and semi-inclusive DIS, respectively. The
+knowledge of jet
+mass parameter and transversity distribution will be eventually needed for a precise
+extraction of pure twist-3 terms from the structure function $g_2$.
 

### 2016-08-05 1607 - JMC for g2/Paper/JMC_dis.tex
Added ETL sum rule discussion. Revised paper from beginning until conclusion, excluded; updated e+e- diagrams with right notation

@@
 \newcommand{\Tr}{\operatorname*{Tr}\nolimits} % Trace operator
-\newcommand{\xbj}{x}                   % Bjorken variable
+\newcommand{\xbj}{{x_B}}                   % Bjorken variable
 \newcommand{\de}{d}                    % differential
@@
 can explain the discrepancy between recent calculations and fits of this
-quantity. It also provides an extension of the Burkardt-Cottingham sum rule,
-that puts constraints on the small-$x$ behavior of the transversity
-function and can help constraining the nucleon tensor charge.
+quantity. It also provides an extension of both the Burkardt-Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity
+function and can help constraining the nucleon tensor charge, and of the Efremov-Teryaev-Leader sum rule, suggesting a novel way to mwasure the tensor charge of the proton. 
 %Perspectives to measure the new spin-flip term, and applications to
@@
 
-The tensor charge is a fundamental property of the nucleon, at
-present poorly constrained. It has been estimated in lattice
-QCD (see, \eg,
+The tensor charge is a fundamental property of the nucleon, that is at
+present poorly constrained but of fundamental importance, not the least because its knowledge can be used also to put constraints on the search of physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
+The tensor charge has been estimated in lattice QCD (see, \eg,
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn}), but
-only limited information is available from direct measurements. The
-way to extract the tensor charge from experimental measurements requires first
-of all the extraction the so-called transversity parton distribution function,
+only limited information is available from direct measurements. Its experimental extraction requires first of all the measurement of the so-called transversity parton distribution function,
 denoted by $h_1^q(x)$ (see Ref.~\cite{Barone:2001sp} for a review on transversity and
 Refs.~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa} for the most recent
-extractions). 
-The integral of the transversity distribution
-corresponds to the contribution of flavor $q$ to the tensor charge.
-The knowledge of the tensor charge can be used also to put constraints on the search of physics beyond the Standard
-Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
-
-In this paper, we discuss the possibility of observing the effect of
-the transversity parton distribution function (PDF) in totally inclusive Deep Inelastic Scattering.
+extractions). Secondly, one needs to perform a flavor decomposition and evaluate its integral, that corresponds to the contribution of flavor $q$ to the tensor charge.
 
@@
 appear in a scattering process~\cite{Jaffe:1996zw}. Usually, this spin flip is provided by another
-nonperturbative distribution or fragmentation function, implying that
-transversity cannot be accessed in inclusive DIS,
-but only in more complex processes such as semi-inclusive DIS or Drell-Yan~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1992kk}.
-
-The only other way to attain spin-flip terms in QED and QCD is taking into
-account mass corrections. In fact, it is well known that transversity gives a
+nonperturbative distribution or fragmentation function, accessible in Drell-Yan or semi-inclusive DIS~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1992kk}.
+The only other known way to attain spin-flip terms in QED and QCD is taking into
+account mass corrections. In fact, it is well known that the transversity distribution gives a
 contribution to the structure function $g_2$ in inclusive DIS (see, \eg,
@@
 particular to the violation of the so-called Wandzura--Wilczek relation for
-$g_2$~\cite{Wandzura:1977qf}. However, this contribution is proportional to the current quark mass
-and can be expected to be very small.
+$g_2$~\cite{Wandzura:1977qf}. However, this contribution is proportional to the current quark mass and can be expected to be negligibly small. This implies that
+transversity cannot be accessed in inclusive DIS, but only in more complex processes such as semi-inclusive DIS or dilepton production in hadron-hadron collisions.
 
+In this paper, we discuss a novel way of accessing the transversity parton distribution function (PDF) and measuring the proton's tensor charge in totally inclusive Deep Inelastic Scattering. 
 We revisit the standard analysis of inclusive DIS taking into account the fact
@@
 cut-diagram, even if none of the hadrons is detected in the final
-state. For a proper description of this effect, we include proper ``jet
+state. For a proper description of this effect, we include ``jet
 correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant. We observe that the inclusion of jet correlators introduces a new
-contribution to the inclusive $g_2$ structure function. This term has the
-interesting features that: a) violates the Wandzura--Wilczek relation, b)
-potentially violates the Burkhardt--Cottingham sum rule, c) is
+contribution to the inclusive $g_2$ structure function. This term is
 proportional to the transversity distribution function multiplied by a
-nonperturbative ``jet mass'' parameter, likely much larger than the mass of light quarks.
-We provide estimates of this contribution based on a recent extraction of transversity and show that it could be very large.
+nonperturbative ``jet mass'' parameter, likely much larger than the mass of light quarks, and has the
+interesting features that: (a) it violates the Wandzura--Wilczek relation; (b)
+it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution; (c) it also extends the Efremov-Teryaev-Leader sum rule, and provides a novel way to measure the proton's tensor charge.
+We provide estimates of this new jet-mass induced contribution based on a recent extraction of transversity, and show that it can indeed be very large.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Jet correlator and twist-2 structure functions}
+%\section{Jet correlator and twist-2 structure functions}
+\section{The jet correlator}
 
@@
 \end{align} 
-In this definition, $l$ is the quark four-momentum, $\Psi$ the quark field
+In this definition, $l$ is the quark's four-momentum, $\Psi$ the quark field
 operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
@@
 is nothing else than the cut quark propagator; note however, that we consider
-here the full QCD vacuum rather than the perturbative one (or, in other words, teh interacting rather than teh free quark fields).
+here the full QCD vacuum rather than the perturbative one (or, in other words, the interacting rather than the free quark fields).
 The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral
@@
 Fig.\ref{fig:handbags}(a), and the $J_i$ are the spectral functions of the
-quark propagator, that have been also called ``jet functions'' in
+quark propagator, also called ``jet functions'' in
 \cite{Accardi:2008ne}. These satisfy
@@
   (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
-  \caption{Diagrams contributing to DIS scattering up to twist-3 expansion, including a jet correlator in the top part.
+  \caption{Diagrams contributing to DIS scattering up to twist-3, including a jet correlator in the top part.
 Note the gluon attaches to both the nucleon and jet correlators.
@@
 When inserting the jet correlator in the handbag diagram for inclusive DIS,
-the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$. This
+the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$, where $x_B$ is the Bjorken invariant. This
 induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the
@@
 \begin{align}
-  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(x_B(1+\mu^2/Q^2)) \ ,
+  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(\xi(1+\mu^2/Q^2)) \ ,
 \label{eq:F2}
@@
 $\xi=2x_B/(1+\sqrt{1+4x_B^2M^2/Q^2})$ with $M$ the nucleon's mass is the
-Nachtmann scaling variable. (We also omitted the dependence of the structure
+Nachtmann scaling variable. (We omitted the dependence of the structure
 function on $Q^2$ for clarity of notation). In this paper we limit our
 attention to effects of order $O(1/Q)$ and therefore can extend the
-integration to $\mu^2=\infty$. Therefore, the jet function $J_2$ decouples
-and, thanks to the sum rule \eqref{eq:jetfnsprops}, integrates to 1. One then
-recovers the conventional result, 
+integration to $\mu^2=\infty$. As a consequence, the jet function $J_2$ decouples and, thanks to the sum rule \eqref{eq:jetfnsprops}, integrates to 1. One then recovers the conventional result, 
 \begin{align}
@@
 \end{align} 
-where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
+Here, $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
 % The $\xi_1$ and $\xi_4$ have an interpretation as average invariant mass (and mass squared) of the current jet, and $l^-=q^- + O(1/Q)$ is imposed by 4-momentum conservation at the hard scattering vertex.
@@
   \label{eq:mjet}
-  \mj = O(10^2 \text{ MeV}) \ .
+  \mj = O(100 \text{ MeV}) \ .
 \end{align}
@@
 % (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.}
-Calculating this on the perturbative vacuum and to leading order
-corresponds to taking the trace of the cut bare-quark propagator to obtain 
+On the non-perturbative vacuum, this corresponds the contribution of a quark of flavor $q$ to the chiral condensate, and is calculable in principle in lattice QCD.
+Considering the perturbative vacuum and calculating the same to leading order in the strong coupling constant, corresponds, instead, to taking the trace of the cut bare-quark propagator to obtain 
 $\mj = \,_{\text{pert}} \langle 0
-|  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass, recovering the
-conventional result. However, we are here considering non perturbative effects
+|  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass. One recovers, therefore, the result of the calculation with the conventional handbag diagram. 
+However, we are here considering non perturbative effects
 on the quark fragmentation and $\mj \gtrsim \mq$.
+Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.
+
+%, an example of which we will discuss in the next section.  
 %very importantly, this
@@
 vacuum as depicted in Figs.\ref{fig:handbags}(b) and (c), respectively. 
-In the former the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up $O(1/Q)$
+In the former the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up to $O(1/Q)$
 these give the same contribution as in the conventional handbag calculation.
@@
 The novel element in our analysis is the jet's quark-gluon-quark correlator
-$\Xi_A^{\mu}(l,k)$ in diagrams \ref{fig:handbags}(c), 
+$\Xi_A^{\mu}(l,k)$ in diagram \ref{fig:handbags}(c), 
 \begin{equation} 
@@
 This diagram and its Hermitian conjugate are not only important to account for
-all contribution of order $O(1/Q)$, but also to restore the
-gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
+all contribution of order $O(1/Q)$, but also to restore gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
 of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.
@@
 calculate the inclusive cross section as an integral of the semi-inclusive
-one, utilize the QCD equation of motions and furthermore summed over all
+one, utilize the QCD equation of motions, sum over all
 hadron flavors, and take advantage of  
@@
   \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
-  \sum_h \int dz d^2p_{hT} E(z,p_{hT}) & = \xi_1 \ ,
+  \sum_h \int dz d^2p_{hT} E^h(z,p_{hT}) & = \xi_1 = \mj / \Lambda\ ,
 \end{align}
@@
 function of the hadron's collinear momentum fraction $z$ and transverse
-momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function
+momentum $p_{hT}$, and $E^h(z,p_{hT})$ is a chiral-odd twist-3 function
 defined in \cite{Bacchetta:2006tn}.
@@
     \sum_q e_q^2
-    \bigg[ 2 x_b g_T(x_B) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
+    \bigg[ 2 \xbj g_T(\xbj) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
   %\\ &
-  + 2 h_1(x_B) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots
+  + 2 h_1(\xbj) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots
 \end{align}
@@
 on the perturbative vacuum one would obtain, as already discussed, $\mj=\mq$
-and the new term would vanish.
+and the integral would vanish.
 
@@
 \end{align}
+\todo{Alessandro, please double check that $h_1$ appears naked in Eq.~\eqref{e:FLTint}, and that this implies dividing it by $x$ in Eq.~\eqref{e:g2}.
+It is fundamental for the conclusion about the ETL sum rule later on.\\}
 The second term in the last structure function is a new result from our
@@
 
-The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
+The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function.
+\AAcom{But in the past we mentioned that it could also appear in some fancier structure function -- the one that also obays a WW-type relation.
+Or maybe, we were saying that $\xi_1$ might appear there, and the sentence as written here is correct.} Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
 \begin{align}
 \label{e:g2}
-  g_2(x_B) = g_2^{WW} + \frac{1}{2}\,\sum_a e_a^2
+  g_2(\xbj) = g_2^{WW}(\xbj) + \frac{1}{2}\,\sum_a e_a^2
 \biggl(
-    \widetilde g_T^{a \star}(x) 
-    + \int_x^1\frac{dy}{y} \widehat{g}_T^q(y) 
-    + \frac{\mq}{\Lambda} \left(\frac{h_1^q}{x}\right)^\star(x) 
-    + \frac{\mj-\mq}{\Lambda} \frac{h_1^q(x)}{x} 
+    \widetilde g_T^{a \star}(\xbj) 
+    + \int_\xbj^1\frac{dy}{y} \widehat{g}_T^q(y) 
+    + \frac{\mq}{\Lambda} \left(\frac{h_1^q}{x}\right)^\star(\xbj) 
+    + \frac{\mj-\mq}{\Lambda} \frac{h_1^q(\xbj)}{\xbj} 
 \Biggr) \ ,
@@
 The first term is also known as the Wandzura-Wilczeck function $g_2^{WW} =
--g_1^*(x)$ , and contains all the twist-2 chiral-even contributions to
+-g_1^*$, and contains all the twist-2 chiral-even contributions to
 the $g_2$ structure coming from quark-quark correlators. The second and third
 terms contain all ``pure twist-3'' contributions, i.e., those coming from
-quark-gluon-quark correlators. The fourth and fifth terms depend on the
+quark-gluon-quark correlators. The fourth and fifth terms contain chiral-odd twist-2 contributions and depend on the
 transversity parton distribution function, $h_1$. 
 The fourth term is usually neglected for
-light quarks since it is proportional to $\mq=O$(1 MeV). In the last term,
-new in our analysis, the transversity distribution is multiplied by a constant
-of $O$(100 MeV), and cannot be a priori neglected.
+light quarks since it is proportional to $\mq=O$(1 MeV). The last term,
+new in our analysis, is again proportional to the transversity distribution but multiplied by a constant of $O$(100 MeV), and cannot be a priori neglected.
 
@@
     \biggl(
-    \widetilde g_T^{q \star}(x) 
-    + \int_x^1\frac{dy}{y} \widehat{g}_T^q(y) 
+    \widetilde g_T^{q \star}(\xbj) 
+    + \int_\xbj^1\frac{dy}{y} \widehat{g}_T^q(y) 
     \biggr) 
-&
+\nonumber \\ 
 g_2^{\text{quark}} &= \frac{1}{2}\,\sum_q e_q^2 
- \frac{\mq}{\Lambda} (h_1^q/x)^\star(x),
-&
+ \frac{\mq}{\Lambda} (h_1^q/x)^\star(\xbj) \ ,
+\\
 g_2^{\text{jet}} &= \frac{1}{2}\,\sum_q e_q^2 
-\frac{\mj-\mq}{\Lambda} \frac{h_1^q(x)}{x}. 
+\frac{\mj-\mq}{\Lambda} \frac{h_1^q(\xbj)}{\xbj} \ .
+\nonumber 
 \end{align} 
-These are compared in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function
-obtained in the very recent JAM15 fit of polarized DIS asymmetries
-\cite{Sato:2016tuz}, that includes a large amount of precise data at large $x$
-from Jefferson Lab, and simultaneously fits the higher-twist components of in
+These terms are compared in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function obtained in the very recent JAM15 fit of polarized DIS asymmetries
+\cite{Sato:2016tuz}, that includes a large amount of precise data at large $\xbj$ and small $Q^2$ from Jefferson Lab, and simultaneously fits the higher-twist components of
 $g_1$ and $g_2$ to the data. For the ``pure twist-3'' contribution,
 $g_2^{\rm tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
-elements, we show a model calculation by Braun et al.~\cite{Braun:2011aw}; for
+elements, we show a recent light-front model calculation by Braun et al.~\cite{Braun:2011aw}; for
 (modified) bag model calculations, see \cite{Jaffe:1990qh,Stratmann:1993aw}. To estimate the contributions
-from quark ($g_2^q$) and jet mass ($g_2^{\rm jet}$) effects, that depend on chiral
-odd quark-quark matrix elements, we use the recent Pavia15 fit of the
+from quark ($g_2^{\text{quark}}$) and jet mass ($g_2^{\text{jet}}$) effects, that depend on chiral-odd quark-quark matrix elements, we use the recent Pavia15 fit of the
 transversity distribution from Ref.~\cite{Radici:2015mwa}, which is comparable
@@
 As one can see, in the proton case the pure twist-3 contribution is quite
-smaller in magnitude, and opposite in sign, compared to the JAM15 fit. As
-expected, the quark-mass contribution is essentially negligible. 
+smaller in magnitude, and opposite in sign, compared to the JAM15 fit. The quark-mass contribution, as expected, is essentially negligible. 
 For what concerns the jet-mass contribution, the uncertainties due to the $h_1$
-extraction are very large, especially at low $x$. In addition, there is an
+extraction are very large, especially at low $\xbj$. In addition, there is an
 overall normalization uncertainty due to the choice of $\mj$, not shown in the
@@
 by Braun et al., the breaking of the Wandura-Wilczek relation can be used to
-constrain the extractions of the transversity distribution, in particular at
-low $x$. 
+constrain the extractions of the transversity distribution. This is inparticular true at low $\xbj$, where th wpure twist-3 term is expected to vanish. 
 Moreover, it is quite clear that the gap
 between the pure twist-3 $g_2^{\rm tw3}$ function and the JAM15 fit can be
-explained by the new jet-mass contribution we discussed in this paper.
+explained by the new jet-mass contribution we discuss in this paper.
 
 In the neutron case, the jet contribution is very negative at intermediate to
-large values of $x$. 
+large values of $\xbj$. 
 If one trusts the order of magnitude of the $g_2^{\rm tw3}$
 calculation by Braun et al., one would conclude that the jet contribution
-should not be that large. However, the jet contribution is strongly influenced
-by the $d$ quark's
-transversity, whose fit suffers from large systematic uncertainties and
-saturates the negative Soffer bound. Recent deata in $p+p$ collisions indicate,
-however, that $h_1^d$ might be less negative than in the Pavia15
+should not be that large.
+However, this contribution depends strongly on the $d$ quark's transversity, whose fit suffers from large systematic uncertainties and saturates the negative Soffer bound.
+Recent deata in $p+p$ collisions indicate, in fact, that $h_1^d$ might be less negative than in the Pavia15
 fits~\cite{Radici:2016lam}.
-Correspondingly the jet contribution to the proton at $x \approx 0.1$
+Correspondingly the jet contribution to the proton at $\xbj \approx 0.1$
 would become less positive, inproving as well the agreement with the JAM15
@@
 
-\begin{figure}[tbh]
+\begin{figure}[htb]
 \begin{center}
@@
 transversity function \cite{Radici:2015mwa}. The unceratainty in the choice
-$m_q=5$ GeV and $M_q=100$ GeV is not shown. The pure twist-3 contribution
+$m_q=5$ GeV and $\mj=100$ GeV is not shown. The pure twist-3 contribution
 calculated by Braun et al. \cite{Braun:2011aw} is shown as a dashed blue line
@@
 \end{figure}
+
+\section{Moments of the $g_2$ strcuture function}
 
@@
   & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N] + \hat g_T^q[N]
-    + \frac{(N+1) M_q-m_q}{\Lambda} h_1^q[N] \bigg) \ .
+    + \frac{(N+1) \mj-\mq}{\Lambda} h_1^q[N] \bigg) \ .
 \end{align}
@@
   \label{eq:BC}
-  \int dx\, g_2(x) = \sum_q e_q^2 \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1^q(x) \ ,
+  \int dx\, g_2(x) = \sum_q e_q^2 \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1^q(x) \ .
 \end{align}
-where we used the fact that $\hat g_T^q[0]=0$ identically due to the symmetry
-properties of the quark-gluon-quark correlators. 
+Here we used the fact $f^*[0]=0$ for any function $f$, which eliminates the contribution from the quark-mass and the twist-3 $\widetilde g_T$ terms; instead, $\widehat g_T^q[0]$ vanishes identically due to the symmetry
+properties of the quark-gluon-quark correlators, or equivalently as a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
+The only surviving term on the right-hand side is the new jet contribution.
 The sum rule \eqref{eq:BC}
@@
 which states that  $\int_0^1 dx\, g_2(x) =0$. 
-However, we show that jet-mass corrections violate the BC sum rule. The
-possibility of a violation of the sum rule due to 
-contributions from spin-flip
-processes was already mentioned in the original
-derivation~\cite{Burkhardt:1970ti}, 
-but do not show up in treatments that only
+Here, we have shown that jet-mass corrections can directly violate the BC sum rule.
+In fact, the possibility of a violation of the BC sum rule due to 
+contributions from spin-flip processes was already mentioned in the original
+derivation, but these do not show up in treatments that only
 consider free field quark propagators for the struck quark
-\cite{Jaffe:1996zw}. Since $h_1$ is driven to 0 by QCD evolution as $Q^2 \to
-\infty$, the BC sum rule $\int_0^1 dx\, g_2(x) =0$ is satisfied at least
-asymptotically. Although we formulated \eqref{eq:BC} in terms of sum over quark flavors in order to display a clear
-connection to the structure function $g_2$, we stress that it is valid also
+\cite{Jaffe:1996zw}.  Although we formulated \eqref{eq:BC} in terms of a sum over quark flavors in order to display a clear
+connection to the structure function $g_2$, we stress that this is valid also
 flavor by flavor, i.e., for each single flavor the only measurable nonzero contribution to the zeroth moment of the
-structure function $g_2$ can come from the jet-mass
-corrections and transversity.\footnote{This conclusion is true even if the BC sum rule is broken by a $J = 0$ fixed pole with
+structure function $g_2$ can come from the coupling between the jet mass and the transversity function\footnote{This conclusion is true even if the BC sum rule is broken by a $J = 0$ fixed pole with
 non-polynomial residue \cite{Jaffe:1996zw}, since this would appear as a
-$\delta(x)$ contribution and would not be measurable.}
-The fact that $g_2^{\text{quark}}$ disappears in the zeroth moment
-of $g_2$ is due to the definition of the $\ast$ functions. The fact that $g_2^{\rm tw3}$
-disappears is due to the symmetry properties of $\widehat{g}_T^q$, or
-equivalently  is a consequence of the
-Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) =
-\int_0^1 g_T^q(x)$.
+$\delta(\xbj)$ contribution and would not be measurable.}.
 
-At finite scales, the only way to preserve the validity of the
+One should notice that since $h_1$ is slowly driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule is still satisfied at least
+asymptotically.
+At finite scales, however, the only way to preserve the validity of the
 Burkhardt-Cottingham sum rule is if
@@
 $Q_0$ is conserved through QCD evolution. However, we think that this
-constrain cannot be satisfied in general, since it is broken in perturbative
-QCD~\cite{Kundu:2001pk} and models (see, e.g., \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}).
-
-If we assume that the BC sum rule is broken by a {\em finite} amount, we
+constrain cannot be satisfied in general, since it is explicitly broken in perturbative
+QCD~\cite{Kundu:2001pk} as well as in model calculations (see, e.g., \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}).
+If, nonetheless,  we assume that the BC sum rule is broken by a {\em finite} amount, we
 obtain that $h_1(x)/x$ must be integrable, implying a 
@@
 small $x$ is, as yet, very limited, and in general for proper extrapolations
-when calculating moments.
+when measuring moments.
 
-The first moment is the first in which a contribution from the pure twist-3 part of $g_2$ appears:
+The first moment is the first one to display a contribution from the pure twist-3 part of $g_2$:
 \begin{align}
   d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1]
-    + \frac{2M_q-m_q}{\Lambda} h_1^q[1] \bigg)
+    + \frac{2\mj-\mq}{\Lambda} h_1^q[0] \bigg)
+\label{e:d1}
 \end{align}
-where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the tensor charge.
-
+where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the target's tensor charge. 
 The second moment is also interesting because the pure twist-3 part can be
@@
   d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2]
-    + \frac{3M_q-m_q}{\Lambda} h_1^q[2] \bigg)
+    + \frac{3\mj-\mq}{\Lambda} h_1^q[1] \bigg) \ .
 \end{align}
-In both cases, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
+For experimental
+measurements of $d_2$, see, e.g., Refs.~\cite{Anthony:2002hy,Slifer:2008xu,Solvignon:2013yun,Posik:2014usi,Flay:2016wie}.
+For both of these moments, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} or fitted
@@
 Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound
-\eqref{eq:ABbound} promise to improve future transversity fits. What is less
-obvious is how to calculate $M_q-m_q$ from first principles, since this is
-related to the spectral function of the quark propagator. We will, however,
-briefly discuss perspectives on how to measure it. Therefore the pure twist-3
-part can, in principle, be properly isolated. For experimental
-measurements of $d_2$, see, e.g., Refs.~\cite{Anthony:2002hy,Slifer:2008xu,Solvignon:2013yun,Posik:2014usi,Flay:2016wie}.
+\eqref{eq:ABbound} promise to improve future transversity fits.
+Funally, th $\mj$ mass parameter can as well be evaliated on the lattice, or also measured, \eg, in electron-positron collisions, as we will briefly discuss later.
+Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
 
-\begin{figure}[tbh]
+Finally, we note that the jet contribution also leads to an explicit breaking of the Efremov-Teriayev-Leader (ETL) sum rule \cite{Efremov:1996hd}, in which the pure twist-3 contribution to the first moment of $g_2-g_2^{WW}$ also disappears.
+To see this, let's define the valence contribution to a given structure function as $f^V=\frac12\sum_q e_q^2 (f^q-f{\bar q})$.
+Then, as shown in \cite{Efremov:1996hd}, $\tilde g_T^V[1]+\widehat g_T^V[1] = 0$, and from Eq.~\eqref{e:d1} we obtain
+\begin{align}
+  d_1^V = \frac12 \sum_q e_q^2 \frac{2\mj- \mq}{\Lambda} 
+    \big(h_1^{q}[0]-h_1^{\bar q}[0]\big) \ .
+\end{align}
+Assuming $M_u \approx M_d \gg m_u , m_d$ and isospin symmetry of the proton and neutron, we can also see that 
+\begin{align}
+  d_1^V = \frac{M_{\text{light}}}{\Lambda} \delta_T(p) \ ,   
+\end{align}
+This gives an alternative way to experimentally access the proton tensor charge, $\delta_T(p) = \sum_q e_q^2 \big(h_1^{q}[0]-h_1^{\bar q}[0]\big)$, by measusing moments of the flavor separated $g_2$ structure function.
+\AAcom{I tried to build an observable for $d_1^V$ such as $p-n$ or $p-\bar p$, but I am messing up a bit. We may try and discuss this at the Gordon.}
+%, if the mass parameter $M_{\text{light}} \equiv M_u=M_d$ can be measured with sufficient accuracy, for example in positron-electron annihilation as we shall briefly discuss next.
+
+\section{Measuring the jet PCFs}
+
+To experimentally measure jet functions, and in particular the jet mass parameter $M_q$, a promising avenue is through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
+production from the same hemisphere, $e^+ e^- \to h h X$, see 
+Fig.~\ref{fig:epl_emn_h}.
+In single-hadron production, the fragmentation functions $D^h$
+play the role of PDFs in DIS, and couple to the jet functions
+in an analogous way. To access the spin-flip $J_1$ function one needs to detected a polarized hadron, such as a $\delta$ baryon. 
+In double hadron production, the enlarged number of Dirac structures
+of the dihadron fragmentation correlator allows one to access
+the jet function in novel ways, and in particular to isolate the
+contribution from the helicity-flip $J_1$ term in combination with the
+chiral-odd fragmentation function $H_1^{\sphericalangle}$.
+While measurements in the asymptotic large $Q^2$ regime will provide access to the integral of the $J_1$ jet function, i.e., to the jet-mass parameter $\mj$, perhaps even more interesting is the possibility to experimentally measure at finite values of $Q^2$ the momentum dependence of the jet functions $J_1$ and $J_2$, that enter structure functions in a way analogous to Eq.~\eqref{eq:F2}.
+In other words, it becomes possible to experimentally access the quark's spectral function.
+
+Studying and classifying all the possibilities offered by single and
+double hadron production in electron-positron annihilation events will open up a rich phenomenology, which will in turn be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.
+
+\begin{figure}[htb]
   \centering
@@
 
-To experimentally measure jet functions and in particular the jet mass parameter, a promising avenue is throug inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
-production from the same hemisphere, $e^+ e^- \to h h X$, see 
-Fig.~\ref{fig:epl_emn_h}.
-In single-hadron production, the fragmentation functions $D_h$
-play the role of PDFs in DIS, and couple to the jet functions
-in an analogous way. 
-In double hadron production the enlarged number of Dirac structures
-of the dihadron fragmentation correlator allows one to access
-the jet function in novel ways, and in particular to isolate the
-contribution from the helicity-flip $J_0$ term in combination with the
-chiral-odd fragmentation function $H_1^{\sphericalangle}$.
-Studying and classifying all the possibilities offered by single and
-double hadron production will open up a rich phenomenology, which will in turn
-be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this paper, we revisited the analysis of inclusive DIS, including the
-effects due to the production of a system of final state hadrons, which we
-conveniently referred to as ``jet.'' We described the jet in terms of a jet
-correlator, corresponding to a 
-nonperturbative cut propagator, different from the standard
-perturbative propagator. We
-carried out the
-analysis of the jet correlator up to twist-3 level. The introduction of this jet correlator
+In this paper, we revisited the inclusive DIS analysis, including the
+effects due to the production of a system of final state hadrons in the current direction, which we
+conveniently referred to as a ``jet.'' We described this in terms of a jet
+correlator that corresponds, up to twist-4 contributions, to the nonperturbative quark cut propagator, or, equivalently, to the quark's spectral function. 
+%different from the standard perturbative propagator. 
+We then carried out the analysis of 
+%the jet correlator and 
+the DIS cross section up to twist-3 level. 
+The introduction of this jet correlator
 leads to a difference in the expression of the structure function $g_2$ in
@@
 the standard pure twist-3 terms and quark mass corrections. Contrary to these
-standard terms, however, the new jet mass correction violates also the
+standard terms, however, the new jet mass correction does not necessarily integrate to zero and so violates also the
 Burkhardt-Cottingham sum rule. This is yet another example of how surprising
-and rich the phenomenology of polarized inclusive DIS can be. Detailed measurements of the $g_2$ structure
+and rich the phenomenology of polarized inclusive DIS can be. 
+Detailed measurements of the $g_2$ structure
 function can be used to constrain the jet mass parameter, the transversity
 distribution function and the nucleon tensor charge, helping their extraction from other observables in, e.g.,
-electron-positron annihilation and semi-inclusive DIS, respectively. The
+electron-positron annihilation and semi-inclusive DIS, respectively. 
+The
 knowledge of jet
@@
 \begin{acknowledgments}
-This work was supported by DOE contract No. DE-AC05-06OR23177,
+This work was supported by the United States Department of Energy (DOE) contract No. DE-AC05-06OR23177,
 under which Jefferson Science Associates, LLC operates Jefferson Lab, by the DOE contract DE-SC008791 and 
@@
 
+\ \\ \AAcom{NOTE: the umlauts do not show up in the bibliography!! See, e.g., reference [5]. Need to fix this.}
+
 \bibliographystyle{myrevtex}

### 2017-05-17 1607 - JMC for g2/Paper/JMC_dis.tex
Revised paper after discussions with Andrea

@@
 
+\newcommand{\id}{{\bm 1}
+                 %\mathbb{I}
+}
+
+%\renewcommand{\Xi}{\Pi}
+%\renewcommand{\xi}{\pi}
+
 \allowdisplaybreaks[2]
@@
 
-\date{\bf \today, \currenttime}
+\date{\bf Thursday, May 4th, 2017}
+%\date{\bf \today, \currenttime}
 
@@
 We revisit the standard analysis of inclusive Deep Inelastic Scattering (DIS)
-off nucleons taking into
-account the fact that on-shell quarks cannot be present in the final state,
-but they rather decay into hadrons. As a consequence, a spin-flip term
+off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons -  a process that can be described in terms of suitable "jet" correlators.
+As a consequence, a spin-flip term
 associated with the invariant mass of the produced hadrons is generated
@@
 can explain the discrepancy between recent calculations and fits of this
-quantity. It also provides an extension of both the Burkardt-Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity
-function and can help constraining the nucleon tensor charge, and of the Efremov-Teryaev-Leader sum rule, suggesting a novel way to mwasure the tensor charge of the proton. 
+quantity.
+It also provides an extension of the Burkardt-Cottingham sum rule, putting constraints on the small-x behavior of the transversity function, as well as an extension of the Efremov-Teryaev-Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
 %Perspectives to measure the new spin-flip term, and applications to
@@
 The tensor charge is a fundamental property of the nucleon, that is at
-present poorly constrained but of fundamental importance, not the least because its knowledge can be used also to put constraints on the search of physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
+present poorly constrained but of fundamental importance, not the least because its knowledge can be also used to put constraints on the search of physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
 The tensor charge has been estimated in lattice QCD (see, \eg,
@@
 that on-shell quarks cannot be present in the final state, but they rather
-decay into hadrons (ideally, forming jets of hadrons). This is sufficient to modify the structure of the DIS
+decay into hadrons, typically forming mini-jets of hadrons. This is sufficient to modify the structure of the DIS
 cut-diagram, even if none of the hadrons is detected in the final
 state. For a proper description of this effect, we include ``jet
-correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant. We observe that the inclusion of jet correlators introduces a new
+correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant. We observe that jet correlators introduce a new
 contribution to the inclusive $g_2$ structure function. This term is
 proportional to the transversity distribution function multiplied by a
-nonperturbative ``jet mass'' parameter, likely much larger than the mass of light quarks, and has the
-interesting features that: (a) it violates the Wandzura--Wilczek relation; (b)
-it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution; (c) it also extends the Efremov-Teryaev-Leader sum rule, and provides a novel way to measure the proton's tensor charge.
-We provide estimates of this new jet-mass induced contribution based on a recent extraction of transversity, and show that it can indeed be very large.
+nonperturbative ``jet mass'' parameter, much larger than the mass of light quarks, and has the interesting features that:
+(a) it violates the Wandzura--Wilczek relation;
+(b) it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution;
+(c) it also extends the Efremov-Teryaev-Leader sum rule, and provides a novel way to measure the proton's tensor charge.
+We provide estimates of this new jet-mass-induced contribution based on a recent extraction of transversity, and show that it can indeed be very large.
 
@@
 Motivated by large-$x$ mass corrections to inclusive DIS structure functions,
-Accardi and Qiu have introduced in the LO handbag diagram 
+Accardi and Qiu \cite{Accardi:2008ne} have introduced in the LO handbag diagram 
 a ``jet correlator'' (also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph})
-that accounts for invariant mass production in the current jet, and ensures
+that accounts for invariant mass production in the current region, and ensures
 that leading twist calculations in collinear factorization are consistent with
@@
 correlator's gauge invariance by introducing two Wilson line operators ${\cal
-  U}^{n_+}$ along a light-cone plus direction determined by the vector
-$n_+$. This path choice for the Wilson line is required by QCD factorization
-theorems, and the vector is determined by the particular hard process to which
-the jet correlator contributes. For example, in the case of inclusive DIS
+  U}^{n_+}$ running to infinity first along along a light-cone plus direction determined by the vector $n_+$, then along the direction transverse to that vector, see \cite{Bacchetta:2006tn} for details/ This path choice for the Wilson line is required by QCD factorization theorems, and the vector is determined by the particular hard process to which the jet correlator contributes.
+For example, in the case of inclusive DIS
 discussed in this paper, this is determined by the four momentum transfer $q$
@@
 \begin{equation}
-\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+\Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
 + \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
@@
 where $\Lambda$ is an arbitrary scale, introduced for power counting purposes.
-In this parametrization, no terms proportional to $\gamma_5$ enters because of parity invariance.
+In this parametrization, no terms proportional to $\gamma_5$ enter because of parity invariance.
 Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes only at twist-4 order, and will not be considered further in this paper.
@@
 \begin{equation}
-  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+  \Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
     + O(\Lambda^2/Q^2)
@@
   \Xi(l) =  
-  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
-  \delta(l^2 -\mu_j^2) \ ,
+  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu\,\id + J_2 (\mu^2)\,\lslash \big] \,
+  \delta(l^2 -\mu^2) \ ,
 \label{e:jetspectral}
 \end{align}
-where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it
+where $\mu^2$ can be interpreted as the invariant mass of the current jet, {\it
   i.e.}, of the particles going through the cut in the top blob of
-Fig.\ref{fig:handbags}(a), and the $J_i$ are the spectral functions of the
+Fig.\ref{fig:handbags}(a). The $J_i$ are the spectral functions of the
 quark propagator, also called ``jet functions'' in
-\cite{Accardi:2008ne}. These satisfy
+\cite{Accardi:2008ne}, that can be interpreted as the current jet mass distributions. These satisfy
 \begin{align}
@@
   (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
-  \caption{Diagrams contributing to DIS scattering up to twist-3, including a jet correlator in the top part.
+  \caption{Diagrams contributing to inclusive DIS scattering up to twist-3, including a jet correlator in the top part.
 Note the gluon attaches to both the nucleon and jet correlators.
@@
 
-When inserting the jet correlator in the handbag diagram for inclusive DIS,
-the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$, where $x_B$ is the Bjorken invariant. This
-induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the
-$F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}: 
-\begin{align}
-  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(\xi(1+\mu^2/Q^2)) \ ,
-\label{eq:F2}
-\end{align}
-where $F_2^{(0)}$ is the structure function calculated with the handbag
-diagram sporting a bare quark propagator instead of the jet correlator, and
-$\xi=2x_B/(1+\sqrt{1+4x_B^2M^2/Q^2})$ with $M$ the nucleon's mass is the
-Nachtmann scaling variable. (We omitted the dependence of the structure
-function on $Q^2$ for clarity of notation). In this paper we limit our
-attention to effects of order $O(1/Q)$ and therefore can extend the
-integration to $\mu^2=\infty$. As a consequence, the jet function $J_2$ decouples and, thanks to the sum rule \eqref{eq:jetfnsprops}, integrates to 1. One then recovers the conventional result, 
-\begin{align}
-  F_2(x_B) = \Big[ \int_0^\infty d\mu^2\, J_2(\mu^2) \Big] F_2^{(0)}(x_B) 
-     + O(\Lambda^2/Q^2) = F_2^{(0)}(x_B)  + O(\Lambda^2/Q^2) \ .
-\end{align}
-%The same holds true also for the helicity structure function $g_1$.
-%
-More in general, the jet correlator decouples from the parton correlator $\Phi$ in any inclusive cross section calculation up to $O(1/Q)$, and the inclusive structure functions only depend on the integrated jet correlator
+When inserting the jet correlator in the handbag diagram for inclusive DIS, the integration over $dl^+$, or equivalently $dl^2/(2l^-)$, is kinematically coupled to the other integrations, and induces corrections of order $O(1/Q^2)$ whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}.
+In this paper, where we limit our
+attention to effects of order $O(1/Q)$, we can neglect $k^-$ compared to $q^-$.
+As a consequence, we can extend the integration over $dl^2$ to infinity, the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator
 \begin{equation} 
-  \Xi(l^-) \equiv \int \frac{dl^2}{2l^-} d^2 l_T \, \Xi(l) 
-    =  \frac{\Lambda}{2 l^-}\,\xi_1 {\bm 1}
+  \Xi(l^-,{\bm l_T}) \equiv \int \frac{dl^2}{2l^-} \, \Xi(l) 
+    =  \frac{\Lambda}{2 l^-}\,\xi_1 \id
     +  \xi_2 \frac{\nslash_-}{2} 
-    + \text{higher\ twists}
-    % +\frac{\Lambda^2}{4 (l^-)^2}\,\xi_3 \nslash_+
-    % + i \frac{\Lambda}{2 l^-} \xi_4 
-    % \frac{ \bigl[\nslash_-, \nslash_+ \bigr]}{2}.
+    + \text{higher\ twists} \ .
 \end{equation} 
-where 
+where the terms up to twist-3 are independent of ${\bm l_T}$, and the neglected higher twist terms only contribute to $O(1/Q^2)$ to the cross section.
+Note that thanks to Eq.~\eqref{eq:jetfnsprops} we also obtain
 \begin{align}
@@
 \xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ .
-% \\
-% \xi_3 &= 0,
-% &
-% \xi_4 &= \int d\mu^2 \frac{\mu^2}{\Lambda^2} J_1(\mu^2) = \frac{\mjs}{\Lambda^2}.
 \end{align} 
 Here, $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
-% The $\xi_1$ and $\xi_4$ have an interpretation as average invariant mass (and mass squared) of the current jet, and $l^-=q^- + O(1/Q)$ is imposed by 4-momentum conservation at the hard scattering vertex.
-The $\xi^4$ term contributes at order $O(1/Q^2)$ and is no further considered in this paper.
 It is important to notice that $\xi_2=1$ exactly due to CPT invariance
-(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is
-dynamically determined. From the analytic properties of spectral functions we
-may expect \cite{Accardi:2008ne} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2
+(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
+From the analytic properties of spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2
 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the
-mass of the pion, due to color confinement effects. Taking into account that
-$J_1 < J_2$, we may therefore expect  
+mass of the pion, due to color confinement effects \cite{Accardi:2008ne}. Taking into account that $J_1 < J_2$, we may therefore estimate 
 \begin{align}
@@
 Although $\mj$ is in general a nonperturbative quantity, it is interesting to
-notice that  
-\begin{align}
-  \label{eq:xi2_chiral_cond}
-  \mj = \frac{\Lambda}{4} \int \Tr \big[ \Xi(l) \bm 1] 
-   = \langle 0 | \bar \psi_i(0) \psi_i(0) | 0 \rangle
-\end{align}
-% \todo{[AA] 2 issues here: (1) possible factors of 4. 
-% (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.}
-On the non-perturbative vacuum, this corresponds the contribution of a quark of flavor $q$ to the chiral condensate, and is calculable in principle in lattice QCD.
-Considering the perturbative vacuum and calculating the same to leading order in the strong coupling constant, corresponds, instead, to taking the trace of the cut bare-quark propagator to obtain 
-$\mj = \,_{\text{pert}} \langle 0
-|  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass. One recovers, therefore, the result of the calculation with the conventional handbag diagram. 
+notice that on the perturbative vacuum, 
+\begin{align*}
+  \Xi^\text{pert}(l) = (\lslash + m_q \id) \, \delta(l^2-m_q^2) + O(\alpha_s) \ ,
+\end{align*}
+where $\mq$ is the current quark mass; one recovers, therefore, the result of the calculation with the conventional handbag diagram.
+% \begin{align}
+%   \label{eq:xi2_chiral_cond}
+%   \mj = \frac{\Lambda}{4} \int \Tr \big[ \Xi(l) \bm 1] 
+%    = \langle 0 | \bar \psi_i(0) \psi_i(0) | 0 \rangle
+% \end{align}
+% % \todo{[AA] 2 issues here: (1) possible factors of 4. 
+% % (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.}
+% On the non-perturbative vacuum, this corresponds the contribution of a quark of flavor $q$ to the chiral condensate, and is calculable in principle in lattice QCD.
+% Considering the perturbative vacuum and calculating the same to leading order in the strong coupling constant, corresponds, instead, to taking the trace of the cut bare-quark propagator to obtain 
+% $\mj = \,_{\text{pert}} \langle 0
+% |  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass. One recovers, therefore, the result of the calculation with the conventional handbag diagram. 
 However, we are here considering non perturbative effects
-on the quark fragmentation and $\mj \gtrsim \mq$.
+on the quark fragmentation and $\mj > \mq$. 
 Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.
-
-%, an example of which we will discuss in the next section.  
-%very importantly, this
-%quantity can be computed in lattice QCD. 
-%\todo{[AA] Are qe sure that $\mj > \mq$??}
-%\todo{[AA] Need to discuss connection to quark condensate and tensor charge.}
 
@@
 vacuum as depicted in Figs.\ref{fig:handbags}(b) and (c), respectively.
-In the former the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up to $O(1/Q)$
-these give the same contribution as in the conventional handbag calculation.
 
-The novel element in our analysis is the jet's quark-gluon-quark correlator
-$\Xi_A^{\mu}(l,k)$ in diagram \ref{fig:handbags}(c), 
+In diagram (b), the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up to $O(1/Q)$ these give the same contribution as in the conventional handbag calculation.
+The novel element in our analysis, instead, is the jet's quark-gluon-quark correlator $\Xi_A^{\mu}(l,k)$ in diagram (c), defined as
 \begin{equation} 
@@
 calculate the inclusive cross section as an integral of the semi-inclusive
-one, utilize the QCD equation of motions, sum over all
-hadron flavors, and take advantage of  
+one summed over all produced hadron flavors, then utilize the QCD equation of motions, sum over all hadron flavors, and take advantage of  
 \begin{align}
   \label{eq:SIDIS_to_DIS}
-  \sum_h \int \frac{d^3p_h}{(2\pi)2E_h} \Delta^h(l,p_h) = \Xi(l) \ , 
+  \sum_h \int d^2p_{hT}\frac{dp_h^-}{2p_h^-} \Delta^h(l,p_h) = \Xi(l) \ , 
 \end{align}
@@
 hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}. In terms of
-the TMD fragmentation functions we are interested in, this reads 
+the TMD fragmentation functions we are interested in, the sum rule \eqref{eq:SIDIS_to_DIS} reads 
 \begin{align}
-  \label{eq:SIDIS_to_DIS_TMDlevel}
+  \label{eq:SIDIS_to_DIS_TMDlevel1}
   \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
+  \label{eq:SIDIS_to_DIS_TMDlevel2}
   \sum_h \int dz d^2p_{hT} E^h(z,p_{hT}) & = \xi_1 = \mj / \Lambda\ ,
 \end{align}
-where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a
-function of the hadron's collinear momentum fraction $z$ and transverse
+where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function, that depends on the hadron's collinear momentum fraction $z$ and transverse
 momentum $p_{hT}$, and $E^h(z,p_{hT})$ is a chiral-odd twist-3 function
@@
 
-% As we shall see, an analogous formula for quark-gluon-quark correlators is not needed.
-%The $\xi_1$ term is chiral-odd and therefore can appear in the inclusive cross section only coupled to the transversity function $h_1$. Therefore, for our analysis 
-The relevant part of the semi-inclusive hadronic tensor for our analysis is 
+The role of the $\xi_1=M_q/\Lambda$ term in inclusive DIS can be discussed by analyzing the following terms of the semi-inclusive hadronic tensor:
 \begin{align}
@@
     \sum_q e_q^2
-    \bigg[ 2 \xbj g_T(\xbj) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
+    \bigg[ 2 \xbj g_T^q(\xbj) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
   %\\ &
-  + 2 h_1(\xbj) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots
+  + 2 h_1^q(\xbj) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots \ ,
 \end{align}
+where $g_T^q$ and $\tilde E^q$ are twist-3 TMDs originating, respectively, from the quark-quark and the quark-gluon-quark fragmentation correlators. 
 For clarity, here we reintroduced the quark flavor $q$, $e_q$ being its electric charge.
-The first term can be easily integrated with the help of the sum rule
-\eqref{eq:SIDIS_to_DIS_TMDlevel}. To integrate the latter, we first need make
+The first term can be easily integrated with the help of the sum rules
+\eqref{eq:SIDIS_to_DIS_TMDlevel2} and \label{eq:SIDIS_to_DIS_TMDlevel2}. To integrate the second term, however, we first need make
 use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a
@@
 Finally, the contraction of the hadronic tensor with the leptonic tensor leads
-to the following well known result for the inclusive DIS cross section up to order $\Lambda/Q$~\cite{Bacchetta:2006tn}
+to the following result for the inclusive DIS cross section up to order $\Lambda/Q$~\cite{Bacchetta:2006tn}:
 \begin{align}
-\frac{d\sigma}{d\xbj \, dy\, d\psi}
+\frac{d\sigma}{d\xbj \, dy\, d\phi_S}
 %&
@@
 \biggl\{
-&F_{UU ,T} + \varepsilon F_{UU ,L}
+&F_{T} + \varepsilon F_{L}
 + S_\parallel \lambda_e\,
@@
 \end{align}
-where the structure functions on the right hand side correspond to
+where $\phi_S$ is the angle between the transverse component of the proton spin vector and the lepton plane, $\epsilon$ is the ratio of the longitudinal and transverse photon fluxes, and $\lambda_e$ is the electron's helicity.
+The structure functions on the right hand side correspond to
 \begin{align}
@@
 \biggl(\xbj  g_T^q(\xbj)
-   + \frac{\mj -\mq}{\Lambda} \, h_{1}^q(\xbj) \biggr).
+   + \frac{\mj -\mq}{\Lambda} \, h_{1}^q(\xbj) \biggr) \ ,
 \label{e:FLTint}
 \end{align}
-\todo{Alessandro, please double check that $h_1$ appears naked in Eq.~\eqref{e:FLTint}, and that this implies dividing it by $x$ in Eq.~\eqref{e:g2}.
-It is fundamental for the conclusion about the ETL sum rule later on.\\}
+where $f_1^q$, $g_1^q$ and $h_1^q$ are the unpolarized, polarized, and transversity PDFs,respectively.
 The second term in the last structure function is a new result from our
-analysis; it is not suppressed as an inverse power of $Q$ compared to the
-standard term. On the nonperturbative
-vacuum the jet mass is larger than the quark's, and this contributes a
-nonnegligible term to the twist-3 part of the $g_2$ function, as we will
-discuss in the next section.
+analysis, that is not suppressed as an inverse power of $Q$ compared to the
+standard $g_T$ term.
+Perutrbatively, $M_q=m_q$ and the new term vanishes.
+However, on the nonperturbative vacuum the jet mass $M_q$ is larger than the quark's, originating a nonnegligible term to the twist-3 part of the target's $g_2$ structure function, as we will discuss in the next section.
 
@@
 
-The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function.
-\AAcom{But in the past we mentioned that it could also appear in some fancier structure function -- the one that also obays a WW-type relation.
-Or maybe, we were saying that $\xi_1$ might appear there, and the sentence as written here is correct.} Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
+The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function of the proton. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
 \begin{align}
@@
 approximation \cite{Accardi:2009au}, while the fifth is new. Note that even if
-the relation is written for the sum of the quark weighted by their charge
-squared, it can be considered valid also flavor by flavor. In fact, the steps
+the relation is written for the sum over quark flavors weighted by their charge
+squared, it is also valid flavor by flavor; in fact, the steps
 leading to such a decomposition are formulated at the correlator level.
 
-The first term is also known as the Wandzura-Wilczeck function $g_2^{WW} =
+The first term is also known as the Wandzura-Wilczeck function, $g_2^{WW} =
 -g_1^*$, and contains all the twist-2 chiral-even contributions to
@@
 values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV. 
+\AAcom{Did we really use 100 MeV in teh plots? I seem to remember 50 MeV.}
 
 As one can see, in the proton case the pure twist-3 contribution is quite
-smaller in magnitude, and opposite in sign, compared to the JAM15 fit. The quark-mass contribution, as expected, is essentially negligible. 
+smaller in magnitude, and opposite in sign, compared to the twist-3 term extracted in the JAM15 fit. The quark-mass contribution, as expected, is essentially negligible. 
 For what concerns the jet-mass contribution, the uncertainties due to the $h_1$
@@
 by Braun et al., the breaking of the Wandura-Wilczek relation can be used to
-constrain the extractions of the transversity distribution. This is inparticular true at low $\xbj$, where th wpure twist-3 term is expected to vanish. 
+constrain the extractions of the transversity distribution. This is inparticular true at low $\xbj$, where the pure twist-3 term is expected to vanish. 
 Moreover, it is quite clear that the gap
@@
 \end{align}
-For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = N/(N+1) \times f[N]$ and  
+For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = f[N]\,N/(N+1)$ and  
 \begin{align}
   d_N & = (N+1) g_2[N] + N g_1[N] \\
-  & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N] + \hat g_T^q[N]
-    + \frac{(N+1) \mj-\mq}{\Lambda} h_1^q[N] \bigg) \ .
+  & = \frac12 \sum_q e_q^2 \bigg[ N \tilde g_T^q[N] + \hat g_T^q[N]
+    + N \,\frac{m_q}{\Lambda} \bigg(\frac{h_1}{x}\bigg)^{\!\!*}\![N]
+    + \frac{(N+1) \mj-\mq}{\Lambda} h_1^q[N-1] \bigg] \ .
 \end{align}
 
-The zero-th moment provides an interesting relationship between transversity
-and the inclusive structure function $g_2$:
+The zero-th moment, $d_0$, provides an interesting relationship between transversity and the inclusive structure function $g_2$:
 \begin{align}
@@
 Here we used the fact $f^*[0]=0$ for any function $f$, which eliminates the contribution from the quark-mass and the twist-3 $\widetilde g_T$ terms; instead, $\widehat g_T^q[0]$ vanishes identically due to the symmetry
-properties of the quark-gluon-quark correlators, or equivalently as a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
-The only surviving term on the right-hand side is the new jet contribution.
-The sum rule \eqref{eq:BC}
+properties of the quark-gluon-quark correlators \cite{Accardi:2009au}, or equivalently as a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
+
+Note that the only surviving term on the right-hand side is the new jet contribution. Thus, our new sum rule \eqref{eq:BC}
 generalizes the Burkhardt-Cottingham (BC) sum rule~\cite{Burkhardt:1970ti},
-which states that  $\int_0^1 dx\, g_2(x) =0$. 
-Here, we have shown that jet-mass corrections can directly violate the BC sum rule.
+which states that  $\int_0^1 dx\, g_2(x) =0$, while we have shown that jet-mass corrections, and in particular from invariant mass generation in spin-flip processes,  can directly violate this.
 In fact, the possibility of a violation of the BC sum rule due to 
@@
 derivation, but these do not show up in treatments that only
-consider free field quark propagators for the struck quark
+consider free-field quark propagators for the struck quark
 \cite{Jaffe:1996zw}.  Although we formulated \eqref{eq:BC} in terms of a sum over quark flavors in order to display a clear
@@
 flavor by flavor, i.e., for each single flavor the only measurable nonzero contribution to the zeroth moment of the
-structure function $g_2$ can come from the coupling between the jet mass and the transversity function\footnote{This conclusion is true even if the BC sum rule is broken by a $J = 0$ fixed pole with
+structure function $g_2$ can come from the coupling between its jet mass and transversity function\footnote{This conclusion is true even if the BC sum rule is broken by a $J = 0$ fixed pole with
 non-polynomial residue \cite{Jaffe:1996zw}, since this would appear as a
@@
 $Q_0$ is conserved through QCD evolution. However, we think that this
-constrain cannot be satisfied in general, since it is explicitly broken in perturbative
-QCD~\cite{Kundu:2001pk} as well as in model calculations (see, e.g., \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}).
-If, nonetheless,  we assume that the BC sum rule is broken by a {\em finite} amount, we
-obtain that $h_1(x)/x$ must be integrable, implying a 
+constrain is unlikely to be satisfied in general, since it is explicitly broken in perturbative
+QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
+Then, if we assume that the BC sum rule is broken by a {\em finite} amount, we obtain that $h_1(x)/x$ must be integrable, implying a
 a bound on the small $x$ behavior of the transversity, 
@@
 small $x$ is, as yet, very limited, and in general for proper extrapolations
-when measuring moments.
+to $x_B=0$ when experimentally measuring moments.
 
-The first moment is the first one to display a contribution from the pure twist-3 part of $g_2$:
+The first moment,$d_1$, is the first one to display a contribution from the pure twist-3 part of $g_2$:
 \begin{align}
@@
 \end{align}
-where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the target's tensor charge. 
-The second moment is also interesting because the pure twist-3 part can be
-related to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and
-interpreted as as the average color force experienced by the struck quark as
-it exits the nucleon \cite{Burkardt:2012sd}: 
+where $h_1^q[0] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the target's tensor charge.
+Here, we neglected the quark mass contribution, although its first moment is not identically equal to zero.
+The second moment, $d_2$, is also interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and
+interpreted as the average color force experienced by the struck quark as
+it exits the nucleon \cite{Burkardt:2012sd}; for experimental
+measurements of $d_2$, see, e.g., Refs.~\cite{Anthony:2002hy,Slifer:2008xu,Solvignon:2013yun,Posik:2014usi,Flay:2016wie}. Neglecting the quark mass term contribution, one obtains
 \begin{align}
@@
 \end{align}
-For experimental
-measurements of $d_2$, see, e.g., Refs.~\cite{Anthony:2002hy,Slifer:2008xu,Solvignon:2013yun,Posik:2014usi,Flay:2016wie}.
-For both of these moments, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
-\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} or fitted
-\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
+For both the $d_1$ and $d_2$ moments, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
+\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} 
+\AAcom{Check the $q+\bar q$ vs. $q-\bar q$ issue for lattice moments discussed in Oxford}
+or fitted \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
 Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound
-\eqref{eq:ABbound} promise to improve future transversity fits.
-Funally, th $\mj$ mass parameter can as well be evaliated on the lattice, or also measured, \eg, in electron-positron collisions, as we will briefly discuss later.
-Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
+\eqref{eq:ABbound} promise to improve future transversity fits. Finally, the $\mj$ jet mass parameter can
+%as well be evaliated on the lattice, or 
+also be measured, \eg, in electron-positron collisions, as we will briefly discuss later. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
 
-Finally, we note that the jet contribution also leads to an explicit breaking of the Efremov-Teriayev-Leader (ETL) sum rule \cite{Efremov:1996hd}, in which the pure twist-3 contribution to the first moment of $g_2-g_2^{WW}$ also disappears.
-To see this, let's define the valence contribution to a given structure function as $f^V=\frac12\sum_q e_q^2 (f^q-f{\bar q})$.
+To conclude this section, we note that the jet contribution also leads to an explicit breaking of the Efremov-Teriayev-Leader (ETL) sum rule \cite{Efremov:1996hd}, in which the pure twist-3 contribution to the first moment of $g_2-g_2^{WW}$ also disappears.
+To see this, let's define the valence contribution to a given structure function as $f^V=\frac12\sum_q e_q^2 (f^q-f^{\bar q})$.
 Then, as shown in \cite{Efremov:1996hd}, $\tilde g_T^V[1]+\widehat g_T^V[1] = 0$, and from Eq.~\eqref{e:d1} we obtain
@@
 \end{align}
-Assuming $M_u \approx M_d \gg m_u , m_d$ and isospin symmetry of the proton and neutron, we can also see that 
+Assuming $M_\text{light}\equiv M_u \approx M_d \gg m_u , m_d$ and isospin symmetry of the proton and neutron, we can also see that 
 \begin{align}
@@
 \end{align}
-This gives an alternative way to experimentally access the proton tensor charge, $\delta_T(p) = \sum_q e_q^2 \big(h_1^{q}[0]-h_1^{\bar q}[0]\big)$, by measusing moments of the flavor separated $g_2$ structure function.
-\AAcom{I tried to build an observable for $d_1^V$ such as $p-n$ or $p-\bar p$, but I am messing up a bit. We may try and discuss this at the Gordon.}
-%, if the mass parameter $M_{\text{light}} \equiv M_u=M_d$ can be measured with sufficient accuracy, for example in positron-electron annihilation as we shall briefly discuss next.
+This gives an alternative way to access the proton tensor charge, $\delta_T(p) = \sum_q e_q^2 \big(h_1^{q}[0]-h_1^{\bar q}[0]\big)$, by measusing moments of the flavor separated $g_2$ structure function.
+\AAcom{I tried to build an observable for $d_1^V$ such as $p-n$ or $p-\bar p$, but I am messing up a bit.}
 
-\section{Measuring the jet PCFs}
+\section{Measuring the integrated jet PCFs}
 
@@
 Fig.~\ref{fig:epl_emn_h}.
+\AAcom{Andrea suggested to remove teh figures, to avoid competitors stealing our idea and doing the actual analysis of te hobservables sensitive to $M_q$.
+I see his point, but am a bit torn about this.}
 In single-hadron production, the fragmentation functions $D^h$
 play the role of PDFs in DIS, and couple to the jet functions
-in an analogous way. To access the spin-flip $J_1$ function one needs to detected a polarized hadron, such as a $\delta$ baryon. 
+in an analogous way. To access the spin-flip $J_1$ function one needs to detected a polarized hadron, such as a $\Delta$ baryon. 
 In double hadron production, the enlarged number of Dirac structures
-of the dihadron fragmentation correlator allows one to access
+of the dihadron fragmentation correlators \cite{Bacchetta:2002ux,Bacchetta:2003vn} allows one to access
 the jet function in novel ways, and in particular to isolate the
@@
 chiral-odd fragmentation function $H_1^{\sphericalangle}$.
-While measurements in the asymptotic large $Q^2$ regime will provide access to the integral of the $J_1$ jet function, i.e., to the jet-mass parameter $\mj$, perhaps even more interesting is the possibility to experimentally measure at finite values of $Q^2$ the momentum dependence of the jet functions $J_1$ and $J_2$, that enter structure functions in a way analogous to Eq.~\eqref{eq:F2}.
-In other words, it becomes possible to experimentally access the quark's spectral function.
 
 Studying and classifying all the possibilities offered by single and
-double hadron production in electron-positron annihilation events will open up a rich phenomenology, which will in turn be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.
+double hadron production in electron-positron annihilation events will open up a rich phenomenology, which will in turn be needed to extract pure twist-3 matrix elements from the $g_2$ DIS structure function.
+While measurements in the asymptotically large $Q^2$ regime will provide access to the integral of the $J_1$ jet function, i.e., to the jet-mass parameter $\mj$, perhaps even more interesting is the possibility to experimentally measure at finite values of $Q^2$ the momentum dependence of the jet functions $J_1$ and $J_2$, that enter structure functions in a way analogous to that discussed in Ref.~\cite{Accardi:2008ne}.
+In other words, it will become possible to experimentally access the quark's spectral function.
 
@@
 extraction of pure twist-3 terms from the structure function $g_2$.
+\AAcom{We shoiuld try and make the conclusions a little crisper.}
 
@@
 \begin{acknowledgments}
-This work was supported by the United States Department of Energy (DOE) contract No. DE-AC05-06OR23177,
-under which Jefferson Science Associates, LLC operates Jefferson Lab, by the DOE contract DE-SC008791 and 
+We are grateful to A.~Signori for a careful reading of a draft o fthis article, and to A.~Mukherjee, M.~Starttman, and W.~Vogelsang for interestign discussions.
+This work was supported by the United States Department of Energy (DOE) contract No.
+DE-AC05-06OR23177,
+under which Jefferson Science Associates, LLC operates Jefferson Lab, by the DOE contract DE-SC008791, and 
 by the European Research Council (ERC) under the European Union's 

### 2017-05-31 1607 - JMC for g2/Paper/JMC_dis.tex
Draft revision after AA talk at QCD Evolution 2017

@@
 
-\preprint{JLAB-THY-16-????}
+\preprint{JLAB-THY-17-????}
 
-\title{Accessing the nucleon tensor structure in inclusive deep inelastic scattering}
+\title{Accessing the nucleon transverse structure in inclusive deep inelastic scattering}
 
@@
 \begin{abstract}
-We revisit the standard analysis of inclusive Deep Inelastic Scattering (DIS)
+We revisit the standard analysis of inclusive Deep Inelastic Scattering
 off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons -  a process that can be described in terms of suitable "jet" correlators.
@@
 associated with the invariant mass of the produced hadrons is generated
-non perturbatively, and couples to the target's transversity distribution
+non perturbatively and couples to the target's transversity distribution
 function. In inclusive cross sections, this provides an hitherto neglected and
@@
 quantity.
-It also provides an extension of the Burkardt-Cottingham sum rule, putting constraints on the small-x behavior of the transversity function, as well as an extension of the Efremov-Teryaev-Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
+It also provides an extension of the Burkhardt--Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
 %Perspectives to measure the new spin-flip term, and applications to
@@
 The tensor charge is a fundamental property of the nucleon, that is at
-present poorly constrained but of fundamental importance, not the least because its knowledge can be also used to put constraints on the search of physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
+present poorly constrained but of fundamental importance, not the least because its knowledge can also be used to put constraints on searches for physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
 The tensor charge has been estimated in lattice QCD (see, \eg,
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn}), but
-only limited information is available from direct measurements. Its experimental extraction requires first of all the measurement of the so-called transversity parton distribution function,
-denoted by $h_1^q(x)$ (see Ref.~\cite{Barone:2001sp} for a review on transversity and
+only limited information is available from direct measurements.
+Its experimental extraction requires first of all flavor-separated measurements of the so-called transversity parton distribution function,
+denoted by $h_1^q(x)$ (see Ref.~\cite{Barone:2001sp} for a review and
 Refs.~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa} for the most recent
-extractions). Secondly, one needs to perform a flavor decomposition and evaluate its integral, that corresponds to the contribution of flavor $q$ to the tensor charge.
+extractions). Secondly, one needs to perform flavor-by-flavor integrals of these, that correspond to the contribution of a parton flavor $q$ to the tensor charge.
 
@@
 appear in a scattering process~\cite{Jaffe:1996zw}. Usually, this spin flip is provided by another
-nonperturbative distribution or fragmentation function, accessible in Drell-Yan or semi-inclusive DIS~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1992kk}.
-The only other known way to attain spin-flip terms in QED and QCD is taking into
-account mass corrections. In fact, it is well known that the transversity distribution gives a
-contribution to the structure function $g_2$ in inclusive DIS (see, \eg,
-\cite{Accardi:2009au} and references therein), and in
-particular to the violation of the so-called Wandzura--Wilczek relation for
-$g_2$~\cite{Wandzura:1977qf}. However, this contribution is proportional to the current quark mass and can be expected to be negligibly small. This implies that
-transversity cannot be accessed in inclusive DIS, but only in more complex processes such as semi-inclusive DIS or dilepton production in hadron-hadron collisions.
+nonperturbative distribution or fragmentation function, accessible in Drell-Yan or semi-inclusive Deep Inelastic Scattering (DIS)~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1992kk}.
+The only other known way to attain spin-flip terms in Quantum Electro-Dynamics and QCD is taking into account mass corrections.
+In fact, it is well known that the transversity distribution gives a contribution to the structure function $g_2$ in inclusive DIS (see, \eg, \cite{Accardi:2009au} and references therein), and in particular to the violation of the so-called Wandzura--Wilczek relation for $g_2$~\cite{Wandzura:1977qf}.
+However, this contribution is proportional to the current quark mass and can be expected to be negligibly small.
+%This implies that the transversity distribution cannot be accessed in inclusive DIS, but only in more complex processes such as semi-inclusive DIS or dilepton production in hadron-hadron collisions.
 
 In this paper, we discuss a novel way of accessing the transversity parton distribution function (PDF) and measuring the proton's tensor charge in totally inclusive Deep Inelastic Scattering. 
-We revisit the standard analysis of inclusive DIS taking into account the fact
-that on-shell quarks cannot be present in the final state, but they rather
-decay into hadrons, typically forming mini-jets of hadrons. This is sufficient to modify the structure of the DIS
-cut-diagram, even if none of the hadrons is detected in the final
+We revisit the standard analysis of the DIS handbag diagram, taking into account the fact that on-shell quarks cannot, in fact, be present in the final state, but they rather decay and form mini-jets of hadrons.
+This is sufficient to modify the structure of the DIS
+cut diagram, even if none of the hadrons is detected in the final
 state. For a proper description of this effect, we include ``jet
-correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant. We observe that jet correlators introduce a new
-contribution to the inclusive $g_2$ structure function. This term is
-proportional to the transversity distribution function multiplied by a
-nonperturbative ``jet mass'' parameter, much larger than the mass of light quarks, and has the interesting features that:
+correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant.
+
+The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a non perturbative mass of order 100 MeV, much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes.
+Here, we formalize this idea in the context of collinear factorization, and observe that jet correlators introduce a new
+contribution already in one-photon exchange processes, and more precisely to the inclusive $g_2$ structure function.
+The new term is proportional to the transversity distribution function multiplied by a new nonperturbative ``jet mass'', which will be precisely defined below, and has the interesting features that:
 (a) it violates the Wandzura--Wilczek relation;
 (b) it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution;
-(c) it also extends the Efremov-Teryaev-Leader sum rule, and provides a novel way to measure the proton's tensor charge.
-We provide estimates of this new jet-mass-induced contribution based on a recent extraction of transversity, and show that it can indeed be very large.
+(c) it also extends the Efremov--Teryaev--Leader sum rule, providing a novel way to measure the proton's tensor charge.
+We Estimates this new jet-mass-induced contribution based on a recent extraction of the transversity distribution, and show it can indeed be very large.
 
@@
 %\section{Jet correlator and twist-2 structure functions}
-\section{The jet correlator}
+\section{The quark-quark jet correlator}
 
-Motivated by large-$x$ mass corrections to inclusive DIS structure functions,
+Motivated by mass corrections to inclusive DIS structure functions at large values of the Bjorken invariant $x_B$,
 Accardi and Qiu \cite{Accardi:2008ne} have introduced in the LO handbag diagram 
-a ``jet correlator'' (also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph})
-that accounts for invariant mass production in the current region, and ensures
-that leading twist calculations in collinear factorization are consistent with
-the requirement imposed by baryon number conservation that $x_B<1$
-\cite{Accardi:2008ne}. The jet correlator is depicted in
+a ``jet correlator'', also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph}, that accounts for invariant mass production in the current region and ensures that leading twist calculations in collinear factorization are consistent with the $x_B<1$ requirement imposed by baryon number conservation.
+\cite{Accardi:2008ne}.
+The jet correlator is depicted in
 Figure~\ref{fig:handbags}(a) and is defined as 
@@
 operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
-the nonperturbative vacuum state. Furthermore, we explicitly guarantee the
-correlator's gauge invariance by introducing two Wilson line operators ${\cal
-  U}^{n_+}$ running to infinity first along along a light-cone plus direction determined by the vector $n_+$, then along the direction transverse to that vector, see \cite{Bacchetta:2006tn} for details/ This path choice for the Wilson line is required by QCD factorization theorems, and the vector is determined by the particular hard process to which the jet correlator contributes.
+the nonperturbative vacuum state. Furthermore, the correlator's gauge invariance is explicitly guaranteed the two Wilson line operators ${\cal
+  U}^{n_+}$, that run to infinity first along along a light-cone plus direction determined by the vector $n_+$, then along the direction transverse to that vector, see \cite{Bacchetta:2006tn} for details.
+This path choice for the Wilson line is required by QCD factorization theorems, and the vector $n_+$ is determined by the particular hard process to which the jet correlator contributes.
 For example, in the case of inclusive DIS
@@
 The correlator $\Xi$ can be parametrized in terms of jet parton correlation
-functions (PCFs), using the vectors $l$ and $n_+$: 
+functions $A_i$ and $B_i$ through a Lorentz covariant Dirac decomposition that utilizes the vectors $l$ and $n_+$, 
 \begin{equation}
@@
 In this parametrization, no terms proportional to $\gamma_5$ enter because of parity invariance.
-Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes only at twist-4 order, and will not be considered further in this paper.
+Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes only at twist-4 order and will not be considered further in this paper.
 We focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3.
@@
 quark propagator, also called ``jet functions'' in
-\cite{Accardi:2008ne}, that can be interpreted as the current jet mass distributions. These satisfy
+\cite{Accardi:2008ne}, and can be interpreted as current-jet mass distributions.
+As a consequence of positivity constraints and CPT invariance, These satisfy \cite{D'Hoker:2004aa,Romao:2013aa,Weinberg:1995mt}
 \begin{align}
@@
 attention to effects of order $O(1/Q)$, we can neglect $k^-$ compared to $q^-$.
-As a consequence, we can extend the integration over $dl^2$ to infinity, the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator
+As a consequence, we can extend the integration over $dl^2$ to infinity, with the consequence that the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator
 \begin{equation} 
@@
     +  \xi_2 \frac{\nslash_-}{2} 
-    + \text{higher\ twists} \ .
+    + O(l_T/l^-) + \text{higher\ twists} \ .
 \end{equation} 
-where the terms up to twist-3 are independent of ${\bm l_T}$, and the neglected higher twist terms only contribute to $O(1/Q^2)$ to the cross section.
-Note that thanks to Eq.~\eqref{eq:jetfnsprops} we also obtain
+The neglected ${\bm l_T}$-dependent and higher twist terms only contribute to $O(1/Q^2)$ to the inclusive cross section. Note that thanks to Eq.~\eqref{eq:jetfnsprops} we obtain
 \begin{align}
@@
 &
-\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ .
+\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ ,
 \end{align} 
-Here, $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
-It is important to notice that $\xi_2=1$ exactly due to CPT invariance
-(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
-From the analytic properties of spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2
-(\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the
-mass of the pion, due to color confinement effects \cite{Accardi:2008ne}. Taking into account that $J_1 < J_2$, we may therefore estimate 
+where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
+It is important to notice that while $\xi_2=1$ exactly due to CPT invariance
+(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
+From the analytic properties of the spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$ with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects.
+Taking into account that $J_1 < J_2$, we may therefore estimate
 \begin{align}
   \label{eq:mjet}
-  \mj = O(100 \text{ MeV}) \ .
+  \mj = O(100 \text{\ MeV}) \ .
 \end{align}
@@
 \begin{align*}
-  \Xi^\text{pert}(l) = (\lslash + m_q \id) \, \delta(l^2-m_q^2) + O(\alpha_s) \ ,
+  \Xi^\text{pert}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + O(\alpha_s) \ ,
 \end{align*}
-where $\mq$ is the current quark mass; one recovers, therefore, the result of the calculation with the conventional handbag diagram.
+where $\mq$ is the current quark mass; therefore $\mj^\text{pert}=m_q$, and one recovers the result of the calculation with the conventional handbag diagram.
 % \begin{align}
@@
 However, we are here considering non perturbative effects
-on the quark fragmentation and $\mj > \mq$. 
+in the quark propagation, and $\mj \gg \mq$. 
 Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.
@@
 
-Extending the analysis of \cite{Accardi:2008ne} to the calculation of twist-3
+Extending this analysis to the calculation of twist-3
 structure functions requires not only to consider the $\xi_1$ term in the jet
@@
 
-In diagram (b), the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up to $O(1/Q)$ these give the same contribution as in the conventional handbag calculation.
+In diagram (b), the $\xi_1$ term contributes to $O(1/Q^2)$, so that up to $O(1/Q)$ considered in this paper this give the same contribution as in the conventional handbag calculation.
 The novel element in our analysis, instead, is the jet's quark-gluon-quark correlator $\Xi_A^{\mu}(l,k)$ in diagram (c), defined as
@@
 \begin{split} 
-  \left(\Xi_A^{\mu} \right)_{ij} &=
-   \frac{1}{2}\, \sum_X \int \frac{\de \eta^+\, \de^2 \bm{\eta}_T}{(2\pi)^{3}}\;
+  \left(\tilde \Xi_A^{\mu} \right)_{ij} &=
+   \int \frac{\de^4 \eta}{(2\pi)^{4}}\;
    e^{\ii k \cdot \eta}\,
@@
    g A^{\mu}(\eta)\,
-   \,\psi_i(\eta)|X\rangle
-   \langle X|
-             \bar{\psi}_j(0)\,
+   \,\psi_i(\eta)
+   \,\bar{\psi}_j(0)\,
    {\cal U}^{n_+}_{(0,+\infty)}
-   |0\rangle \bigg|_{\eta^-=0} .
+   |0\rangle \ .
 \label{e:xi_A}
@@
 
-Rather than directly using the definition \eqref{e:xi_A}, it is convenient to
-calculate the inclusive cross section as an integral of the semi-inclusive
-one summed over all produced hadron flavors, then utilize the QCD equation of motions, sum over all hadron flavors, and take advantage of  
+Rather than directly using the definition \eqref{e:xi_A}, it is convenient and instructive to calculate the inclusive cross section as an integral of the semi-inclusive one summed over all produced hadron flavors, then utilize the QCD equations of motion, sum over all hadron flavors, and take advantage of
 \begin{align}
   \label{eq:SIDIS_to_DIS}
-  \sum_h \int d^2p_{hT}\frac{dp_h^-}{2p_h^-} \Delta^h(l,p_h) = \Xi(l) \ , 
+  \sum_h \int d^2p_{hT}\frac{dp_h^-}{2p_h^-} \,p_h^- \, \Delta^h(l,p_h) = l^-\,\Xi(l) \ , 
 \end{align}
 where $\Delta^h$ is the quark fragmentation correlator for production of a
-hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}. In terms of
+hadron of flavor $h$ and momentum $p_h$, discussed in detail  \cite{Bacchetta:2006tn}. In terms of
 the TMD fragmentation functions we are interested in, the sum rule \eqref{eq:SIDIS_to_DIS} reads 
@@
     & = i \frac{2\Lambda}{Q} \hat t^{[\mu}_{\phantom \perp} 
-    \epsilon_\perp^{\nu]\rho}S_{\perp\rho} 
-    \sum_q e_q^2
+    \epsilon_\perp^{\nu]\rho}S_{\perp\rho} \\
+    & \times \sum_q e_q^2
     \bigg[ 2 \xbj g_T^q(\xbj) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
   %\\ &
-  + 2 h_1^q(\xbj) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots \ ,
+  + 2 h_1^q(\xbj) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots \ , \nonumber
 \end{align}
-where $g_T^q$ and $\tilde E^q$ are twist-3 TMDs originating, respectively, from the quark-quark and the quark-gluon-quark fragmentation correlators. 
-For clarity, here we reintroduced the quark flavor $q$, $e_q$ being its electric charge.
+where $g_T^q(z,p_{hT})$ and $\tilde E^q(z,p_{hT})$ are twist-3 TMDs originating, respectively, from the quark-quark and the quark-gluon-quark fragmentation correlators. 
+For clarity, here we reintroduced the quark flavors $q$, $e_q$ being their respective electric charge.
 The first term can be easily integrated with the help of the sum rules
-\eqref{eq:SIDIS_to_DIS_TMDlevel2} and \label{eq:SIDIS_to_DIS_TMDlevel2}. To integrate the second term, however, we first need make
+\eqref{eq:SIDIS_to_DIS_TMDlevel1} and \eqref{eq:SIDIS_to_DIS_TMDlevel2}. To integrate the second term, however, we first need make
 use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a
 consequence of the QCD equations of motion \cite{Bacchetta:2006tn}, then
-make use of the sum rule \eqref{eq:SIDIS_to_DIS}: 
+make again use of the sum rules \eqref{eq:SIDIS_to_DIS_TMDlevel1}-\eqref{eq:SIDIS_to_DIS_TMDlevel2} to obtain
 \begin{align}
   \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) 
-    = \sum_h \int dz d^2p_{hT} \Big[ E^{q,h}(z,p_{hT}) - \frac{\mq}{\Lambda} z D_1^{q,h}(z,p_{hT}) \Big]
-    = \xi_1 - \frac{\mq}{\Lambda} \xi_2 = \frac{\mj - \mq}{\Lambda} \ .
+    = \xi_1 - \frac{\mq}{\Lambda} \xi_2 = \frac{\mj - \mq}{\Lambda }\ .
 \end{align}
-This formula is the single most important result of this paper, and provides a
+This formula provides a
 non perturbative generalization of the commonly used $\int\tilde E =0$ sum
@@
 where $\phi_S$ is the angle between the transverse component of the proton spin vector and the lepton plane, $\epsilon$ is the ratio of the longitudinal and transverse photon fluxes, and $\lambda_e$ is the electron's helicity.
-The structure functions on the right hand side correspond to
+The structure functions on the right hand side read
 \begin{align}
@@
 The second term in the last structure function is a new result from our
-analysis, that is not suppressed as an inverse power of $Q$ compared to the
+analysis, and, although proportional to the jet mass, it is not suppressed as an inverse power of $Q$ compared to the
 standard $g_T$ term.
-Perutrbatively, $M_q=m_q$ and the new term vanishes.
-However, on the nonperturbative vacuum the jet mass $M_q$ is larger than the quark's, originating a nonnegligible term to the twist-3 part of the target's $g_2$ structure function, as we will discuss in the next section.
+Perturbatively, $M_q^\text{pert}=m_q$ and the new term vanishes.
+However, on the nonperturbative vacuum the jet mass $M_q$ is much larger than the quark's current mass $m_q$, originating a nonnegligible term to the twist-3 part of the target's $g_2$ structure function, as we will discuss in the next section.
 
@@
 
-The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function of the proton. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
+The new term in Eq.\eqref{e:FLTint} only appears in the $g_2=\frac12 \sum_q e_q^2(g_T^q-g_1^q)$ structure function. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
 \begin{align}
@@
 \end{align}
-where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$. The first four
-terms coincide with the result obtained in the conventional handbag
+where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$, and $\tilde g_T$ and $\hat g_T$ are pure twist-3 functions defined in that reference.
+The first four terms coincide with the result obtained in the conventional handbag
 approximation \cite{Accardi:2009au}, while the fifth is new. Note that even if
@@
 squared, it is also valid flavor by flavor; in fact, the steps
-leading to such a decomposition are formulated at the correlator level.
+leading to such a decomposition are formulated at the quark correlator level.
 
-The first term is also known as the Wandzura-Wilczeck function, $g_2^{WW} =
--g_1^*$, and contains all the twist-2 chiral-even contributions to
-the $g_2$ structure coming from quark-quark correlators. The second and third
+The first term is also known as the Wandzura-Wilczek function, $g_2^{WW} =
+-g_1^*$, with $g_1=\frac12 \sum_q e_q^2 g_1^q$, and contains all the twist-2 chiral-even contributions to the $g_2$ structure coming from quark-quark correlators. The second and third
 terms contain all ``pure twist-3'' contributions, i.e., those coming from
 quark-gluon-quark correlators. The fourth and fifth terms contain chiral-odd twist-2 contributions and depend on the
-transversity parton distribution function, $h_1$. 
+transversity distribution function, $h_1$. 
 The fourth term is usually neglected for
 light quarks since it is proportional to $\mq=O$(1 MeV). The last term,
-new in our analysis, is again proportional to the transversity distribution but multiplied by a constant of $O$(100 MeV), and cannot be a priori neglected.
+new in our analysis, is again proportional to the transversity distribution but multiplied by the jet mass $\mj=O$(100 MeV), so that it cannot be a priori neglected.
 
@@
 g_2^{\text{quark}} &= \frac{1}{2}\,\sum_q e_q^2 
- \frac{\mq}{\Lambda} (h_1^q/x)^\star(\xbj) \ ,
+ \frac{\mq}{\Lambda} \bigg( \frac{h_1^q}{x} \bigg)^\star\!\!(\xbj) \ ,
 \\
@@
 \cite{Sato:2016tuz}, that includes a large amount of precise data at large $\xbj$ and small $Q^2$ from Jefferson Lab, and simultaneously fits the higher-twist components of
-$g_1$ and $g_2$ to the data. For the ``pure twist-3'' contribution,
+$g_1$ and $g_2$ to the data\footnote{Keep in mind, however, that the JAM15 fit imposes the $\int dx g_2(x) =0$ Burkhardt--Cottingham sum rule, which, however, is broken by inclusion of jet correlators, as discussed in Section~\ref{sec:moments}.}.
+For the ``pure twist-3'' contribution,
 $g_2^{\rm tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
-elements, we show a recent light-front model calculation by Braun et al.~\cite{Braun:2011aw}; for
-(modified) bag model calculations, see \cite{Jaffe:1990qh,Stratmann:1993aw}. To estimate the contributions
+elements, we show a recent light-front model calculation by Braun et al.~\cite{Braun:2011aw} (for bag model calculations, see \cite{Jaffe:1990qh,Stratmann:1993aw}). To estimate the contributions
 from quark ($g_2^{\text{quark}}$) and jet mass ($g_2^{\text{jet}}$) effects, that depend on chiral-odd quark-quark matrix elements, we use the recent Pavia15 fit of the
@@
 values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV. 
-\AAcom{Did we really use 100 MeV in teh plots? I seem to remember 50 MeV.}
+%\AAcom{Did we really use 100 MeV in teh plots? I seem to remember 50 MeV.}
 
 As one can see, in the proton case the pure twist-3 contribution is quite
-smaller in magnitude, and opposite in sign, compared to the twist-3 term extracted in the JAM15 fit. The quark-mass contribution, as expected, is essentially negligible. 
+smaller in magnitude than, and nearly opposite in sign compared to, the twist-3 term extracted in the JAM15 fit. The quark-mass contribution, as expected, is essentially negligible. 
 For what concerns the jet-mass contribution, the uncertainties due to the $h_1$
@@
 overall normalization uncertainty due to the choice of $\mj$, not shown in the
-plot. In any case, the jet-mass contribution is strikingly large. If we assume
-that the pure twist-3 contributions are of the order of the model calculation
-by Braun et al., the breaking of the Wandura-Wilczek relation can be used to
-constrain the extractions of the transversity distribution. This is inparticular true at low $\xbj$, where the pure twist-3 term is expected to vanish. 
+plot.
+In any case, the jet-mass contribution is strikingly large, and of the same order of magnitude as the chiral-even twist 3 term.
+If we assume the latter to be of the order of the model calculation
+by Braun et al., the breaking of the Wandzura-Wilczek relation can be used to
+constrain the extractions of the transversity distribution. This is in particular true at low $\xbj$, where the pure twist-3 term is expected to vanish. 
 Moreover, it is quite clear that the gap
@@
 should not be that large.
-However, this contribution depends strongly on the $d$ quark's transversity, whose fit suffers from large systematic uncertainties and saturates the negative Soffer bound.
-Recent deata in $p+p$ collisions indicate, in fact, that $h_1^d$ might be less negative than in the Pavia15
-fits~\cite{Radici:2016lam}.
+However, for a neutron target, $g_2^{jet}$ depends strongly on the $d$ quark's transversity, whose fit suffers from large systematic uncertainties and saturates the negative Soffer bound.
+Recent data in $p+p$ collisions indicate, in fact, that $h_1^{q=d}$ might be less negative than in the Pavia15 fits~\cite{Radici:2016lam}.
 Correspondingly the jet contribution to the proton at $\xbj \approx 0.1$
-would become less positive, inproving as well the agreement with the JAM15
+would become less positive, improving as well the agreement with the JAM15
 fit.
@@
 Different contributions to the non Wandzura-Wilczek part of the proton (left)
-and neutron (right) $g_2$ structure function compared to the JAM15 fit of the
-$g_2-g_2^{\text{WW}}$ (solid black) \cite{Sato:2016tuz}. The quark and jet
+and neutron (right) $g_2$ structure functions compared to the JAM15 fit of the
+$g_2-g_2^{\text{WW}}$ function (solid black) \cite{Sato:2016tuz}. The quark and jet
 contributions are shown with a dotted red and a dot-dashed green line
 respectively, with uncertainty bands coming form the Pavia15 fit of the
-transversity function \cite{Radici:2015mwa}. The unceratainty in the choice
+transversity function \cite{Radici:2015mwa}. The uncertainty in the choice
 $m_q=5$ GeV and $\mj=100$ GeV is not shown. The pure twist-3 contribution
@@
 
-\section{Moments of the $g_2$ strcuture function}
+\section{Moments of the $g_2$ structure function}
+\label{sec:moments}
 
@@
 \end{align}
-For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = f[N]\,N/(N+1)$ and  
+For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = - f[N]\,N/(N+1)$ and  
 \begin{align}
   d_N & = (N+1) g_2[N] + N g_1[N] \\
-  & = \frac12 \sum_q e_q^2 \bigg[ N \tilde g_T^q[N] + \hat g_T^q[N]
-    + N \,\frac{m_q}{\Lambda} \bigg(\frac{h_1}{x}\bigg)^{\!\!*}\![N]
-    + \frac{(N+1) \mj-\mq}{\Lambda} h_1^q[N-1] \bigg] \ .
+  & = \frac12 \sum_q e_q^2 \bigg[ \hat g_T^q[N] - N \tilde g_T^q[N] 
+    + \frac{(N+1) \mj-(2N+1)\mq}{\Lambda} h_1^q[N-1] \bigg] \ .
 \end{align}
 
-The zero-th moment, $d_0$, provides an interesting relationship between transversity and the inclusive structure function $g_2$:
+The zero-th moment, $d_0=\int g_2$, provides an interesting relationship between transversity and the inclusive structure function $g_2$:
 \begin{align}
@@
 \end{align}
-Here we used the fact $f^*[0]=0$ for any function $f$, which eliminates the contribution from the quark-mass and the twist-3 $\widetilde g_T$ terms; instead, $\widehat g_T^q[0]$ vanishes identically due to the symmetry
-properties of the quark-gluon-quark correlators \cite{Accardi:2009au}, or equivalently as a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$.
-
+Here we used the fact that $\widehat g_T^q[0]$ vanishes identically due to the symmetry properties of the quark-gluon-quark correlators \cite{Accardi:2009au}.
+%, or equivalently as a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. 
+%
 Note that the only surviving term on the right-hand side is the new jet contribution. Thus, our new sum rule \eqref{eq:BC}
-generalizes the Burkhardt-Cottingham (BC) sum rule~\cite{Burkhardt:1970ti},
+generalizes the Burkhardt--Cottingham (BC) sum rule~\cite{Burkhardt:1970ti},
 which states that  $\int_0^1 dx\, g_2(x) =0$, while we have shown that jet-mass corrections, and in particular from invariant mass generation in spin-flip processes,  can directly violate this.
@@
 flavor by flavor, i.e., for each single flavor the only measurable nonzero contribution to the zeroth moment of the
-structure function $g_2$ can come from the coupling between its jet mass and transversity function\footnote{This conclusion is true even if the BC sum rule is broken by a $J = 0$ fixed pole with
+structure function $g_2^q$ comes from the coupling between its jet mass and transversity function\footnote{This conclusion is true even if the BC sum rule is broken by a $J = 0$ fixed pole with
 non-polynomial residue \cite{Jaffe:1996zw}, since this would appear as a
@@
 At finite scales, however, the only way to preserve the validity of the
-Burkhardt-Cottingham sum rule is if
+BC sum rule is if
 %that is derived at the cross section level (under suitable assumptions on the
@@
 Interestingly, one can show that this constraint, if valid at any given scale
-$Q_0$ is conserved through QCD evolution. However, we think that this
-constrain is unlikely to be satisfied in general, since it is explicitly broken in perturbative
-QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
-Then, if we assume that the BC sum rule is broken by a {\em finite} amount, we obtain that $h_1(x)/x$ must be integrable, implying a
+$Q_0$ is conserved through QCD evolution.
+However, we think that it is unlikely to be satisfied in general, since Eq.\eqref{eq:ABsumrule} is explicitly broken in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
+Then, if we assume that the BC sum rule is broken by a {\em finite} amount (which is very reasonable from the recent small-$x$ estimate $g_2\propto x^{\sqrt{ \alpha_s N_c / \pi}}$, with $N_c=3$ the number of colors, and $alpha_s$ the strong coupling constant \cite{Kovchegov:2016zex})
+we obtain that $h_1(x)/x$ must be integrable. This implies a 
 a bound on the small $x$ behavior of the transversity, 
@@
 
-The first moment,$d_1$, is the first one to display a contribution from the pure twist-3 part of $g_2$:
+The first moment, $d_1$, is the first one to display a contribution from the pure twist-3 part of $g_2$:
 \begin{align}
-  d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1]
-    + \frac{2\mj-\mq}{\Lambda} h_1^q[0] \bigg)
+  d_1 & = \frac12 \sum_q e_q^2 \bigg(  \hat g_T^q[1] - 2 \tilde g_T^q[1]
+    + \frac{2\mj-3\mq}{\Lambda} h_1^q[0] \bigg)
 \label{e:d1}
 \end{align}
-where $h_1^q[0] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the target's tensor charge.
-Here, we neglected the quark mass contribution, although its first moment is not identically equal to zero.
-The second moment, $d_2$, is also interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and
+where $h_1^q[0] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the target's tensor charge. The second moment,
+\begin{align}
+  d_2 & = \frac12 \sum_q e_q^2 \bigg(\hat g_T^q[2] - 3 \tilde g_T^q[2] 
+    + \frac{3\mj-4\mq}{\Lambda} h_1^q[1] \bigg) \ ,
+\end{align}
+is also interesting because the pure twist-3 part can be related to quark-gluon-quark local matrix elements, see \cite{Jaffe:1996zw}, and
 interpreted as the average color force experienced by the struck quark as
 it exits the nucleon \cite{Burkardt:2012sd}; for experimental
-measurements of $d_2$, see, e.g., Refs.~\cite{Anthony:2002hy,Slifer:2008xu,Solvignon:2013yun,Posik:2014usi,Flay:2016wie}. Neglecting the quark mass term contribution, one obtains
-\begin{align}
-  d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2]
-    + \frac{3\mj-\mq}{\Lambda} h_1^q[1] \bigg) \ .
-\end{align}
+measurements of $d_2$, see, e.g., Refs.~\cite{Anthony:2002hy,Slifer:2008xu,Solvignon:2013yun,Posik:2014usi,Flay:2016wie}.
+
 For both the $d_1$ and $d_2$ moments, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} 
-\AAcom{Check the $q+\bar q$ vs. $q-\bar q$ issue for lattice moments discussed in Oxford}
+%\AAcom{Check the $q+\bar q$ vs. $q-\bar q$ issue for lattice moments discussed in Oxford}
 or fitted \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
-Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound
-\eqref{eq:ABbound} promise to improve future transversity fits. Finally, the $\mj$ jet mass parameter can
-%as well be evaliated on the lattice, or 
-also be measured, \eg, in electron-positron collisions, as we will briefly discuss later. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
+Furthermore, the new sum rule \eqref{eq:BCsumrule} and the bound
+\eqref{eq:ABbound} promise to improve future transversity fits. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
 
-To conclude this section, we note that the jet contribution also leads to an explicit breaking of the Efremov-Teriayev-Leader (ETL) sum rule \cite{Efremov:1996hd}, in which the pure twist-3 contribution to the first moment of $g_2-g_2^{WW}$ also disappears.
-To see this, let's define the valence contribution to a given structure function as $f^V=\frac12\sum_q e_q^2 (f^q-f^{\bar q})$.
-Then, as shown in \cite{Efremov:1996hd}, $\tilde g_T^V[1]+\widehat g_T^V[1] = 0$, and from Eq.~\eqref{e:d1} we obtain
-\begin{align}
-  d_1^V = \frac12 \sum_q e_q^2 \frac{2\mj- \mq}{\Lambda} 
-    \big(h_1^{q}[0]-h_1^{\bar q}[0]\big) \ .
-\end{align}
-Assuming $M_\text{light}\equiv M_u \approx M_d \gg m_u , m_d$ and isospin symmetry of the proton and neutron, we can also see that 
-\begin{align}
-  d_1^V = \frac{M_{\text{light}}}{\Lambda} \delta_T(p) \ ,   
-\end{align}
-This gives an alternative way to access the proton tensor charge, $\delta_T(p) = \sum_q e_q^2 \big(h_1^{q}[0]-h_1^{\bar q}[0]\big)$, by measusing moments of the flavor separated $g_2$ structure function.
-\AAcom{I tried to build an observable for $d_1^V$ such as $p-n$ or $p-\bar p$, but I am messing up a bit.}
-
-\section{Measuring the integrated jet PCFs}
-
-To experimentally measure jet functions, and in particular the jet mass parameter $M_q$, a promising avenue is through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
+We should also note that the $\mj$ jet mass parameter can
+also be experimentally measured, \eg, in electron-positron collisions.
+A promising avenue is through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
 production from the same hemisphere, $e^+ e^- \to h h X$, see 
 Fig.~\ref{fig:epl_emn_h}.
-\AAcom{Andrea suggested to remove teh figures, to avoid competitors stealing our idea and doing the actual analysis of te hobservables sensitive to $M_q$.
+%\AAcom{Andrea suggested to remove teh figures, to avoid competitors stealing our idea and doing the actual analysis of te hobservables sensitive to $M_q$.
 I see his point, but am a bit torn about this.}
-In single-hadron production, the fragmentation functions $D^h$
-play the role of PDFs in DIS, and couple to the jet functions
-in an analogous way. To access the spin-flip $J_1$ function one needs to detected a polarized hadron, such as a $\Delta$ baryon. 
+In single-hadron production, the fragmentation functions 
+play the role of PDFs in DIS and couple to the jet functions
+in an analogous way. To access the spin-flip $J_1$ function one needs to detect a polarized hadron, such as a $\Delta$ baryon. 
 In double hadron production, the enlarged number of Dirac structures
-of the dihadron fragmentation correlators \cite{Bacchetta:2002ux,Bacchetta:2003vn} allows one to access
+of the dihadron fragmentation correlators related to the relative momentum of the two hadrons \cite{Bacchetta:2002ux,Bacchetta:2003vn} allows one to access
 the jet function in novel ways, and in particular to isolate the
@@
 
-Studying and classifying all the possibilities offered by single and
-double hadron production in electron-positron annihilation events will open up a rich phenomenology, which will in turn be needed to extract pure twist-3 matrix elements from the $g_2$ DIS structure function.
-While measurements in the asymptotically large $Q^2$ regime will provide access to the integral of the $J_1$ jet function, i.e., to the jet-mass parameter $\mj$, perhaps even more interesting is the possibility to experimentally measure at finite values of $Q^2$ the momentum dependence of the jet functions $J_1$ and $J_2$, that enter structure functions in a way analogous to that discussed in Ref.~\cite{Accardi:2008ne}.
-In other words, it will become possible to experimentally access the quark's spectral function.
-
-\begin{figure}[htb]
+\begin{figure}[tbh]
   \centering
-  \parbox[b]{8cm}{\centering
+  \parbox[c]{8cm}{\vskip.1cm\centering
   \includegraphics
@@
   }
-  \parbox[b]{8cm}{\vskip-0.5cm\centering
+  \parbox[c]{8cm}{\vskip-0.2cm\centering
   \includegraphics
@@
 
+To conclude this section, we note that the jet contribution also leads to an explicit breaking of the Efremov--Teryaev--Leader (ETL) sum rule \cite{Efremov:1996hd}, in which the pure twist-3 contribution to the first moment of $g_2-g_2^{WW}$ also disappears.
+To see this, let's define the valence contribution to a given structure function as $f^V=\frac12\sum_q e_q^2 (f^q-f^{\bar q})$.
+Then, as shown in \cite{Efremov:1996hd}, $\widehat g_T^V[1] - 2\tilde g_T^V[1] = 0$, and from Eq.~\eqref{e:d1} we obtain
+\begin{align}
+  d_1^V = \frac12 \sum_q e_q^2 \frac{2\mj- \mq}{\Lambda} 
+    \big(h_1^{q}[0]-h_1^{\bar q}[0]\big) \ .
+\end{align}
+Assuming $M_\text{light}\equiv M_u \approx M_d \gg m_u , m_d$ and isospin symmetry of the proton and neutron, we can also see that 
+\begin{align}
+  d_1^V = \frac{M_{\text{light}}}{\Lambda} \delta_T(p) \ ,   
+\end{align}
+This gives an alternative way to access the proton tensor charge, $\delta_T(p) = \sum_q e_q^2 \big(h_1^{q}[0]-h_1^{\bar q}[0]\big)$, by measuring or fitting moments of the flavor separated $g_2$ structure function.
+%\AAcom{I tried to build an observable for $d_1^V$ such as $p-n$ or $p-\bar p$, but I am messing up a bit.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 conveniently referred to as a ``jet.'' We described this in terms of a jet
-correlator that corresponds, up to twist-4 contributions, to the nonperturbative quark cut propagator, or, equivalently, to the quark's spectral function. 
+correlator that corresponds, up to twist-4 contributions, to the nonperturbative quark cut propagator, or, equivalently, to the quark's spectral function, and of a quark-gluon-quark jet correlator needed to insure gauge invariance of the calculation.
 %different from the standard perturbative propagator. 
@@
 %the jet correlator and 
-the DIS cross section up to twist-3 level. 
-The introduction of this jet correlator
+the DIS cross section up to contribution of order $1/Q$. 
+The introduction of the jet correlators 
 leads to a difference in the expression of the structure function $g_2$ in
-inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass
-parameter and to the transversity distribution function. This new term
+inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter $\mj=O$(100 MeV)
+and to the transversity distribution function. This new term
 contributes to the violation of the Wandzura-Wilczek relation, in addition to
@@
 standard terms, however, the new jet mass correction does not necessarily integrate to zero and so violates also the
-Burkhardt-Cottingham sum rule. This is yet another example of how surprising
+BC and ETL sum rules. This is yet another example of how surprising
 and rich the phenomenology of polarized inclusive DIS can be.
+
 Detailed measurements of the $g_2$ structure
-function can be used to constrain the jet mass parameter, the transversity
-distribution function and the nucleon tensor charge, helping their extraction from other observables in, e.g.,
-electron-positron annihilation and semi-inclusive DIS, respectively. 
-The
-knowledge of jet
-mass parameter and transversity distribution will be eventually needed for a precise
-extraction of pure twist-3 terms from the structure function $g_2$.
-\AAcom{We shoiuld try and make the conclusions a little crisper.}
+function can be used to constrain the jet mass parameter $M_q$, the transversity
+distribution function and the nucleon tensor charge, helping their extraction from other observables, e.g., in electron-positron annihilation and semi-inclusive DIS.
+Knowledge of the jet mass parameter and of the transversity distribution will eventually be needed for a precise extraction of pure twist-3 terms from the $g_2$ structure function, or from transverse target single spin asymmetries \cite{Schlegel:2012ve}.
+
+Finally, studying and classifying all the contributions of jet correlators to single and ouble hadron production in electron-positron annihilation events will open up a rich phenomenology.
+Measurements in the asymptotically large $Q^2$ regime will provide access to the integral of the $J_1$ jet function, i.e., to the jet-mass parameter $\mj$, and therefore (in conjunction with precise measurements or lattice QCD calculations of the first $h_1$ moment) also of the target's tensor charge through the modified ETL sum rule.
+Equally interesting is the possibility to experimentally measure, at finite values of $Q^2$, the momentum dependence of the jet functions $J_1$ and $J_2$, that enter structure functions integrated only up to $\mu^2=Q^2(1/x_B-1)$~\cite{Accardi:2008ne}.
+In other words, it may become possible to experimentally access also the quark's spectral function itself.
 
@@
 \begin{acknowledgments}
-We are grateful to A.~Signori for a careful reading of a draft o fthis article, and to A.~Mukherjee, M.~Starttman, and W.~Vogelsang for interestign discussions.
-This work was supported by the United States Department of Energy (DOE) contract No.
+We are grateful to A.~Signori for a careful reading of a draft of this article, and to A.~Mukherjee, M.~Strattman, and W.~Vogelsang for interesting and informative discussions.
+This work has been supported by the United States Department of Energy (DOE) contract No.
 DE-AC05-06OR23177,
@@
 
-\ \\ \AAcom{NOTE: the umlauts do not show up in the bibliography!! See, e.g., reference [5]. Need to fix this.}
+%\ \\ \AAcom{NOTE: the umlauts do not show up in the bibliography!! See, e.g., reference [5]. Need to fix!}
 

### 2017-06-01 1607 - JMC for g2/Paper/JMC_dis.tex
minor changes
Checked a few misprints here and there. Changed a few sentences, with
no deep change of meaning. Still have to check Eqs. 25-26.

@@
 We revisit the standard analysis of inclusive Deep Inelastic Scattering
-off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons -  a process that can be described in terms of suitable "jet" correlators.
+off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons --  a process that can be described in terms of suitable ``jet'' correlators.
 As a consequence, a spin-flip term
@@
 
-The tensor charge is a fundamental property of the nucleon, that is at
+The tensor charge is a fundamental property of the nucleon that is at
 present poorly constrained but of fundamental importance, not the least because its knowledge can also be used to put constraints on searches for physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
@@
 In this paper, we discuss a novel way of accessing the transversity parton distribution function (PDF) and measuring the proton's tensor charge in totally inclusive Deep Inelastic Scattering. 
-We revisit the standard analysis of the DIS handbag diagram, taking into account the fact that on-shell quarks cannot, in fact, be present in the final state, but they rather decay and form mini-jets of hadrons.
+We revisit the standard analysis of the DIS handbag diagram, taking into account the fact that on-shell quarks cannot, in fact, be present in the final state, but they rather decay and form jets of hadrons.
 This is sufficient to modify the structure of the DIS
@@
 (c) it also extends the Efremov--Teryaev--Leader sum rule, providing a novel way to measure the proton's tensor charge.
-We Estimates this new jet-mass-induced contribution based on a recent extraction of the transversity distribution, and show it can indeed be very large.
+We estimate this new jet-mass-induced contribution based on a recent extraction of the transversity distribution, and show it can indeed be very large.
 
@@
   \Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
-    + O(\Lambda^2/Q^2)
+    + {\cal O}(\Lambda^2/Q^2)
 \label{e:jetexpansion-tw3}
@@
 here the full QCD vacuum rather than the perturbative one (or, in other words, the interacting rather than the free quark fields).
-The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral
+The $A_1$ and $A_2$ terms can be interpreted in terms of the spectral
 representation of the cut quark propagator (see, e.g., Sec.~6.3 of
@@
 \end{align}
-From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
+From a comparison of Eqs.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
 \begin{align}
@@
 
-When inserting the jet correlator in the handbag diagram for inclusive DIS, the integration over $dl^+$, or equivalently $dl^2/(2l^-)$, is kinematically coupled to the other integrations, and induces corrections of order $O(1/Q^2)$ whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}.
+When inserting the jet correlator in the handbag diagram for inclusive DIS, the integration over $dl^+$, or equivalently $dl^2/(2l^-)$, is kinematically coupled to the other integrations, and induces corrections of order ${\cal O}(1/Q^2)$ whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}.
 In this paper, where we limit our
-attention to effects of order $O(1/Q)$, we can neglect $k^-$ compared to $q^-$.
+attention to effects of order ${\cal O}(1/Q)$, we can neglect $k^-$ compared to $q^-$.
 As a consequence, we can extend the integration over $dl^2$ to infinity, with the consequence that the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator
@@
     +  \xi_2 \frac{\nslash_-}{2} 
-    + O(l_T/l^-) + \text{higher\ twists} \ .
+    + {\cal O}(l_T/l^-) + \text{higher\ twists} \ .
 \end{equation} 
-The neglected ${\bm l_T}$-dependent and higher twist terms only contribute to $O(1/Q^2)$ to the inclusive cross section. Note that thanks to Eq.~\eqref{eq:jetfnsprops} we obtain
+The neglected ${\bm l_T}$-dependent and higher twist terms only contribute to ${\cal O}(1/Q^2)$ to the inclusive cross section. Note that thanks to Eq.~\eqref{eq:jetfnsprops} we obtain
 \begin{align}
@@
   \label{eq:mjet}
-  \mj = O(100 \text{\ MeV}) \ .
+  \mj = {\cal O}(100 \text{\ MeV}) \ .
 \end{align}
@@
 \begin{align*}
-  \Xi^\text{pert}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + O(\alpha_s) \ ,
+  \Xi^\text{pert}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + {\cal O}(\alpha_s) \ ,
 \end{align*}
@@
 
-In diagram (b), the $\xi_1$ term contributes to $O(1/Q^2)$, so that up to $O(1/Q)$ considered in this paper this give the same contribution as in the conventional handbag calculation.
+In diagram (b), the $\xi_1$ term contributes to ${\cal O}(1/Q^2)$, so that up to ${\cal O}(1/Q)$ considered in this paper this give the same contribution as in the conventional handbag calculation.
 The novel element in our analysis, instead, is the jet's quark-gluon-quark correlator $\Xi_A^{\mu}(l,k)$ in diagram (c), defined as
@@
 This diagram and its Hermitian conjugate are not only important to account for
-all contribution of order $O(1/Q)$, but also to restore gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
+all contribution of order ${\cal O}(1/Q)$, but also to restore gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
 of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.
@@
 where $\Delta^h$ is the quark fragmentation correlator for production of a
-hadron of flavor $h$ and momentum $p_h$, discussed in detail  \cite{Bacchetta:2006tn}. In terms of
+hadron of flavor $h$ and momentum $p_h$, discussed in detail in Ref.~\cite{Bacchetta:2006tn}. In terms of
 the TMD fragmentation functions we are interested in, the sum rule \eqref{eq:SIDIS_to_DIS} reads 
@@
 F_{LL} &=\xbj\,\sum_q e_q^2\,g_1^q(\xbj),
+\label{e:FLLint}
 \\
@@
 The second term in the last structure function is a new result from our
-analysis, and, although proportional to the jet mass, it is not suppressed as an inverse power of $Q$ compared to the
+analysis, it is proportional to the jet mass, and it is not suppressed as an
+inverse power of $Q$ compared to the 
 standard $g_T$ term.
@@
 
-The new term in Eq.\eqref{e:FLTint} only appears in the $g_2=\frac12 \sum_q e_q^2(g_T^q-g_1^q)$ structure function. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
+The structure functions in Eqs.~\eqref{e:FLLint} -- \eqref{e:FLTint} can be
+related to the usual
+structure functions $g_1$ and $g_2$ defined. In
+particular, the expression of the structure function $g_2$ is
+\begin{equation} 
+g_2=\frac12 \sum_q e_q^2(g_T^q-g_1^q)
+\end{equation}
+structure function. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
 \begin{align}
@@
 The first four terms coincide with the result obtained in the conventional handbag
-approximation \cite{Accardi:2009au}, while the fifth is new. Note that even if
+approximation \cite{Accardi:2009au}, while the last is new. Note that even if
 the relation is written for the sum over quark flavors weighted by their charge
@@
 The fourth term is usually neglected for
-light quarks since it is proportional to $\mq=O$(1 MeV). The last term,
-new in our analysis, is again proportional to the transversity distribution but multiplied by the jet mass $\mj=O$(100 MeV), so that it cannot be a priori neglected.
+light quarks since it is proportional to $\mq={\cal O}$(1 MeV). The last term,
+new in our analysis, is again proportional to the transversity distribution
+but multiplied by the jet mass $\mj={\cal O}$(100 MeV), so that it cannot be a priori neglected.
 
@@
 \cite{Sato:2016tuz}, that includes a large amount of precise data at large $\xbj$ and small $Q^2$ from Jefferson Lab, and simultaneously fits the higher-twist components of
-$g_1$ and $g_2$ to the data\footnote{Keep in mind, however, that the JAM15 fit imposes the $\int dx g_2(x) =0$ Burkhardt--Cottingham sum rule, which, however, is broken by inclusion of jet correlators, as discussed in Section~\ref{sec:moments}.}.
-For the ``pure twist-3'' contribution,
+$g_1$ and $g_2$ to the data.\footnote{Notice, however, that the JAM15 fit imposes the $\int dx g_2(x) =0$ Burkhardt--Cottingham sum rule, which, however, is broken by inclusion of jet correlators, as discussed in Section~\ref{sec:moments}.} For the ``pure twist-3'' contribution,
 $g_2^{\rm tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
@@
 transversity function \cite{Radici:2015mwa}. The uncertainty in the choice
-$m_q=5$ GeV and $\mj=100$ GeV is not shown. The pure twist-3 contribution
+$m_q=5$ MeV and $\mj=100$ MeV is not shown. The pure twist-3 contribution
 calculated by Braun et al. \cite{Braun:2011aw} is shown as a dashed blue line
@@
 However, we think that it is unlikely to be satisfied in general, since Eq.\eqref{eq:ABsumrule} is explicitly broken in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
-Then, if we assume that the BC sum rule is broken by a {\em finite} amount (which is very reasonable from the recent small-$x$ estimate $g_2\propto x^{\sqrt{ \alpha_s N_c / \pi}}$, with $N_c=3$ the number of colors, and $alpha_s$ the strong coupling constant \cite{Kovchegov:2016zex})
+Then, if we assume that the BC sum rule is broken by a {\em finite} amount (which is very reasonable from the recent small-$x$ estimate $g_2\propto x^{\sqrt{ \alpha_s N_c / \pi}}$, with $N_c=3$ the number of colors, and $\alpha_s$ the strong coupling constant \cite{Kovchegov:2016zex})
 we obtain that $h_1(x)/x$ must be integrable. This implies a 
@@
 or fitted \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
-Furthermore, the new sum rule \eqref{eq:BCsumrule} and the bound
-\eqref{eq:ABbound} promise to improve future transversity fits. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
+Furthermore, 
+%the new sum rule \eqref{eq:ABsumrule} and 
+the bound
+\eqref{eq:ABbound} promises to improve future transversity fits. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
 
@@
 leads to a difference in the expression of the structure function $g_2$ in
-inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter $\mj=O$(100 MeV)
+inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter $\mj={\cal O}$(100 MeV)
 and to the transversity distribution function. This new term
@@
 standard terms, however, the new jet mass correction does not necessarily integrate to zero and so violates also the
-BC and ETL sum rules. This is yet another example of how surprising
+Burkhardt--Cottingham and Efremov--Teryaev--Leader sum rules. This is yet another example of how surprising
 and rich the phenomenology of polarized inclusive DIS can be.
@@
 
-Finally, studying and classifying all the contributions of jet correlators to single and ouble hadron production in electron-positron annihilation events will open up a rich phenomenology.
+Finally, studying and classifying all the contributions of jet correlators to single and double hadron production in electron-positron annihilation events will open up a rich phenomenology.
 Measurements in the asymptotically large $Q^2$ regime will provide access to the integral of the $J_1$ jet function, i.e., to the jet-mass parameter $\mj$, and therefore (in conjunction with precise measurements or lattice QCD calculations of the first $h_1$ moment) also of the target's tensor charge through the modified ETL sum rule.
@@
 \begin{acknowledgments}
-We are grateful to A.~Signori for a careful reading of a draft of this article, and to A.~Mukherjee, M.~Strattman, and W.~Vogelsang for interesting and informative discussions.
+We are grateful to A.~Signori for a careful reading of a draft of this article, and to A.~Mukherjee, M.~Stratmann, and W.~Vogelsang for interesting and informative discussions.
 This work has been supported by the United States Department of Energy (DOE) contract No.

### 2017-06-06 1607 - JMC for g2/Paper/JMC_dis.tex
added preprint no.'
g2+g1 definition attempt - see e-mail from June 6

@@
 
-\preprint{JLAB-THY-17-????}
+\preprint{JLAB-THY-17-2483}
 
@@
 In this paper, we discuss a novel way of accessing the transversity parton distribution function (PDF) and measuring the proton's tensor charge in totally inclusive Deep Inelastic Scattering. 
-We revisit the standard analysis of the DIS handbag diagram, taking into account the fact that on-shell quarks cannot, in fact, be present in the final state, but they rather decay and form jets of hadrons.
-This is sufficient to modify the structure of the DIS
-cut diagram, even if none of the hadrons is detected in the final
-state. For a proper description of this effect, we include ``jet
-correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant.
+We revisit the standard analysis of the DIS handbag diagram, taking into account the fact that on-shell quarks cannot, in fact, be present in the final state, but they rather decay and form (mini)jets of hadrons.
+This is sufficient to modify the structure of the DIS cut diagram, even if none of those hadrons is detected in the final state.
+For a proper description of this effect, we include ``jet correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant.
 
@@
 \cite{Accardi:2008ne}, and can be interpreted as current-jet mass distributions.
-As a consequence of positivity constraints and CPT invariance, These satisfy \cite{D'Hoker:2004aa,Romao:2013aa,Weinberg:1995mt}
+As a consequence of positivity constraints and CPT invariance, these satisfy \cite{D'Hoker:2004aa,Romao:2013aa,Weinberg:1995mt}
 \begin{align}
@@
   \centering
-  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0}
+  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0.eps}
   \hfill
-  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
+  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2.eps}
   \hfill
-  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
+  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1.eps}
   \caption{Diagrams contributing to inclusive DIS scattering up to twist-3, including a jet correlator in the top part.
@@
 \begin{align}
-F_{UU ,T} &= \xbj\,\sum_q e_q^2\,f_1^q(\xbj),
+F_{T} &= \xbj\,\sum_q e_q^2\,f_1^q(\xbj),
 \\
-F_{UU ,L} &= 0,
+F_{L} &= 0,
 \\
@@
 related to the usual
-structure functions $g_1$ and $g_2$ defined. In
-particular, the expression of the structure function $g_2$ is
-\begin{equation} 
-g_2=\frac12 \sum_q e_q^2(g_T^q-g_1^q)
-\end{equation}
-structure function. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
+structure functions $g_1$ and $g_2$ defined from the following Lorentz decomposition of the hadronic tensor
+\begin{align}
+\begin{split}
+W^{\mu\nu}(P,q) 
+  & = \frac{1}{P\cdot q} \varepsilon^{\mu\nu\rho\sigma} q_\rho 
+  \Big[ S_\sigma g_1(x_B,Q^2) 
+    + \Big( S_\sigma - \frac{S\cdot q}{P\cdot q}\, p_\sigma
+	\Big) g_2(x_B,Q^2)
+  \Big] \ ,
+\label{eq:Wmunu}
+\end{split}
+\end{align}
+Then, in particular,
+\begin{align}
+  g_1 &= \frac{1}{x_B} F_{LL} \\
+  g_2+g_1 &= \frac{Q}{2\Lambda x_B^2} F_{LT}^{\cos \phi_S} \ .
+\end{align}
+% \begin{align}
+% g_1&=\frac12 \sum_q e_q^2g_1^q \ , \\
+% g_2&=\frac12 \sum_q e_q^2(g_T^q-g_1^q) \ .
+% \end{align}
+Utilizing Equations of Motion and Lorentz Invariance relations as discussed in Ref.~\cite{Accardi:2009au}, we arrive at
 \begin{align}
@@
 \end{align}
-where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$, and $\tilde g_T$ and $\hat g_T$ are pure twist-3 functions defined in that reference.
+where we used $f^*(x) = f(x) - \int_x^1\frac{dy}{y} f(y)$, and $\tilde g_T$ and $\hat g_T$ are pure twist-3 functions that only depend on projections of quark-gluon-quark correlator, and are explicitly defined in that reference.
 The first four terms coincide with the result obtained in the conventional handbag
@@
 \begin{center}
-\includegraphics[width=8cm]{g2contrib}
-\includegraphics[width=8cm]{g2contribN}
+\includegraphics[width=8cm]{g2contrib.pdf}
+\includegraphics[width=8cm]{g2contribN.pdf}
 \caption{\label{f:g2contrib} 
@@
 \begin{align}
-  d_N \equiv (N+1) \int_0^1 x^N \bigg( g_2(x) - g_2^{WW}(x) \bigg) \ .
+  d_N \equiv (N+1) \int_0^1 dx\,x^N \bigg( g_2(x) - g_2^{WW}(x) \bigg) \ .
 \end{align}
-For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = - f[N]\,N/(N+1)$ and  
+For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = f[N]\,N/(N+1)$ and  
 \begin{align}
   d_N & = (N+1) g_2[N] + N g_1[N] \\
-  & = \frac12 \sum_q e_q^2 \bigg[ \hat g_T^q[N] - N \tilde g_T^q[N] 
-    + \frac{(N+1) \mj-(2N+1)\mq}{\Lambda} h_1^q[N-1] \bigg] \ .
+  & = \frac12 \sum_q e_q^2 \bigg[ N \tilde g_T^q[N] + \hat g_T^q[N]  
+    + \frac{(N+1) \mj- \mq}{\Lambda} h_1^q[N-1] \bigg] \ .
 \end{align}
@@
 %
-Note that the only surviving term on the right-hand side is the new jet contribution. Thus, our new sum rule \eqref{eq:BC}
+Note that all pure twist-3 terms have explicitly disappeared, and the only surviving term on the right-hand side is the new jet contribution. Thus, our new sum rule \eqref{eq:BC}
 generalizes the Burkhardt--Cottingham (BC) sum rule~\cite{Burkhardt:1970ti},
@@
 %strong constraint on the transversity function, 
-\begin{align}
+$
+%\begin{align}
    \int dx\, \frac{1}{x} h_1^q(x) = 0 \ .
 \label{eq:ABsumrule}
-\end{align}
+%\end{align}
+$
 Interestingly, one can show that this constraint, if valid at any given scale
 $Q_0$ is conserved through QCD evolution.
-However, we think that it is unlikely to be satisfied in general, since Eq.\eqref{eq:ABsumrule} is explicitly broken in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
-Then, if we assume that the BC sum rule is broken by a {\em finite} amount (which is very reasonable from the recent small-$x$ estimate $g_2\propto x^{\sqrt{ \alpha_s N_c / \pi}}$, with $N_c=3$ the number of colors, and $\alpha_s$ the strong coupling constant \cite{Kovchegov:2016zex})
-we obtain that $h_1(x)/x$ must be integrable. This implies a 
-a bound on the small $x$ behavior of the transversity, 
+However, we think that it is unlikely to be satisfied in general, since it is explicitly broken in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
+Then, if we assume that the BC sum rule is broken by a {\em finite} amount we obtain that $h_1(x)/x$ must be integrable, which implies the following bound on the small $x$ behavior of the transversity:
 \begin{align}
@@
 to $x_B=0$ when experimentally measuring moments.
+We also note that the small-$x$ behavior of the longitudinal spin structure function $g_1$ has been recently investigated in Ref.~\cite{Kovchegov:2016zex}; it would be interesting to extend those techniques to the transverse spin structure functions $g_T=g_1+g_2$ and $h_1$.
 
@@
 \begin{align}
-  d_1 & = \frac12 \sum_q e_q^2 \bigg(  \hat g_T^q[1] - 2 \tilde g_T^q[1]
-    + \frac{2\mj-3\mq}{\Lambda} h_1^q[0] \bigg)
+  d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1] 
+    + \frac{2\mj-\mq}{\Lambda} h_1^q[0] \bigg)
 \label{e:d1}
@@
 \begin{align}
-  d_2 & = \frac12 \sum_q e_q^2 \bigg(\hat g_T^q[2] - 3 \tilde g_T^q[2] 
-    + \frac{3\mj-4\mq}{\Lambda} h_1^q[1] \bigg) \ ,
+  d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2] 
+    + \frac{3\mj-\mq}{\Lambda} h_1^q[1] \bigg) \ ,
 \end{align}
@@
       [width=7cm,clip=true]
-      {epl_emn_h_X}
+      {epl_emn_h_X.eps}
   }
@@
       [width=7cm,clip=true]
-      {epl_emn_h_h_X}
+      {epl_emn_h_h_X.eps}
   }
@@
   }
-  \label{fig:epl_emn_h}
+  \label{fig:epl_emn_h.eps}
 \end{figure}
@@
 To see this, let's define the valence contribution to a given structure function as $f^V=\frac12\sum_q e_q^2 (f^q-f^{\bar q})$.
-Then, as shown in \cite{Efremov:1996hd}, $\widehat g_T^V[1] - 2\tilde g_T^V[1] = 0$, and from Eq.~\eqref{e:d1} we obtain
+Then, as shown in \cite{Efremov:1996hd}, $\widehat 2\tilde g_T^V[1] + g_T^V[1]  = 0$, and from Eq.~\eqref{e:d1} we obtain
 \begin{align}

### 2017-07-10 1607 - JMC for g2/Paper/JMC_dis.tex
FIxed references, and cleanup

@@
 \documentclass[preprintnumbers,floatfix,nofootinbib]{revtex4}
+
+\pdfoutput=1 % if your are submitting a pdflatex to arXIv 
+             % (i.e. if you have images in pdf, eps, png or jpg format)
 
@@
 
-\date{\bf Thursday, May 4th, 2017}
+%\date{\bf Thursday, June 6th, 2017}
 %\date{\bf \today, \currenttime}
@@
 It also provides an extension of the Burkhardt--Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
-%Perspectives to measure the new spin-flip term, and applications to
-%spin-1 targets will be briefly discussed. 
 \end{abstract}
@@
 However, this contribution is proportional to the current quark mass and can be expected to be negligibly small.
-%This implies that the transversity distribution cannot be accessed in inclusive DIS, but only in more complex processes such as semi-inclusive DIS or dilepton production in hadron-hadron collisions.
 
@@
   \centering
-  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0.eps}
+  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0}
   \hfill
-  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2.eps}
+  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
   \hfill
-  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1.eps}
+  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
   \caption{Diagrams contributing to inclusive DIS scattering up to twist-3, including a jet correlator in the top part.
@@
 where $\mq$ is the current quark mass; therefore $\mj^\text{pert}=m_q$, and one recovers the result of the calculation with the conventional handbag diagram.
-% \begin{align}
-%   \label{eq:xi2_chiral_cond}
-%   \mj = \frac{\Lambda}{4} \int \Tr \big[ \Xi(l) \bm 1] 
-%    = \langle 0 | \bar \psi_i(0) \psi_i(0) | 0 \rangle
-% \end{align}
-% % \todo{[AA] 2 issues here: (1) possible factors of 4. 
-% % (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.}
-% On the non-perturbative vacuum, this corresponds the contribution of a quark of flavor $q$ to the chiral condensate, and is calculable in principle in lattice QCD.
-% Considering the perturbative vacuum and calculating the same to leading order in the strong coupling constant, corresponds, instead, to taking the trace of the cut bare-quark propagator to obtain 
-% $\mj = \,_{\text{pert}} \langle 0
-% |  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass. One recovers, therefore, the result of the calculation with the conventional handbag diagram. 
 However, we are here considering non perturbative effects
@@
 
-The role of the $\xi_1=M_q/\Lambda$ term in inclusive DIS can be discussed by analyzing the following terms of the semi-inclusive hadronic tensor:
+The role of the $\xi_1=M_q/\Lambda$ term in inclusive DIS can be discussed by analyzing the following terms of the semi-inclusive hadronic tensor \cite{Mulders:1995dh}:
 \begin{align}
   \label{eq:Wsidis_ini}
-  2 \Lambda  W^{\mu\nu}
-    & = i \frac{2\Lambda}{Q} \hat t^{[\mu}_{\phantom \perp} 
+  2 M  W^{\mu\nu}
+    & = i \frac{2M}{Q} \hat t^{[\mu}_{\phantom \perp} 
     \epsilon_\perp^{\nu]\rho}S_{\perp\rho} \\
     & \times \sum_q e_q^2
-    \bigg[ 2 \xbj g_T^q(\xbj) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
-  %\\ &
-  + 2 h_1^q(\xbj) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots \ , \nonumber
+    \bigg[ 2 \xbj g_T^q(\xbj) \sum_h \int d^2p_{hT} dz \, z\, D_1^{q,h}(z,p_{hT}) 
+  + \frac{2\Lambda}{M} h_1^q(\xbj) \sum_h \int d^2p_{hT}  dz \, \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots \ , \nonumber
 \end{align}
 where $g_T^q(z,p_{hT})$ and $\tilde E^q(z,p_{hT})$ are twist-3 TMDs originating, respectively, from the quark-quark and the quark-gluon-quark fragmentation correlators.
-For clarity, here we reintroduced the quark flavors $q$, $e_q$ being their respective electric charge.
+Note that in Eq.~\eqref{eq:Wsidis_ini} $M$ is the proton's mass, and we identified the power counting scale $M_h$ of Ref.~\cite{Mulders:1995dh} with our $\Lambda$.
+For clarity, we also reintroduced the quark flavors $q$, $e_q$ being their respective electric charge.
 The first term can be easily integrated with the help of the sum rules
@@
 \end{align}
-This formula provides a
+This formula provides us with a
 non perturbative generalization of the commonly used $\int\tilde E =0$ sum
@@
 Finally, the contraction of the hadronic tensor with the leptonic tensor leads
-to the following result for the inclusive DIS cross section up to order $\Lambda/Q$~\cite{Bacchetta:2006tn}:
+to the following result for the inclusive DIS cross section up to order $M/Q$~\cite{Bacchetta:2006tn}:
 \begin{align}
 \frac{d\sigma}{d\xbj \, dy\, d\phi_S}
-%&
 =
@@
 F_{LL}
-%\nonumber 
-%\\  &
 + |\bm{S}_\perp| \lambda_e\, \sqrt{2\,\varepsilon (1-\varepsilon)}\, 
@@
 \\
-F_{LT}^{\cos \phi_S}&=-\xbj\,\sum_q e_q^2\, \frac{2\Lambda}{Q}\,
+F_{LT}^{\cos \phi_S}&=-\xbj\,\sum_q e_q^2\, \frac{2M}{Q}\,
 \biggl(\xbj  g_T^q(\xbj)
-   + \frac{\mj -\mq}{\Lambda} \, h_{1}^q(\xbj) \biggr) \ ,
+   + \frac{\mj -\mq}{M} \, h_{1}^q(\xbj) \biggr) \ ,
 \label{e:FLTint}
@@
 The structure functions in Eqs.~\eqref{e:FLLint} -- \eqref{e:FLTint} can be
-related to the usual
-structure functions $g_1$ and $g_2$ defined from the following Lorentz decomposition of the hadronic tensor
+related to the usual structure functions $g_1$ and $g_2$ defined from the following Lorentz decomposition of the antysymmetric part of the inclusive hadronic tensor
 \begin{align}
 \begin{split}
-W^{\mu\nu}(P,q) 
+W_A^{\mu\nu}(P,q) 
   & = \frac{1}{P\cdot q} \varepsilon^{\mu\nu\rho\sigma} q_\rho 
@@
 	\Big) g_2(x_B,Q^2)
-  \Big] \ ,
+  \Big] \ .
 \label{eq:Wmunu}
@@
 \end{align}
-Then, in particular,
+Then, neglecting contrinutions of order $1/Q^2$, one obtains \cite{Bacchetta:2006tn},
 \begin{align}
-  g_1 &= \frac{1}{x_B} F_{LL} \\
-  g_2+g_1 &= \frac{Q}{2\Lambda x_B^2} F_{LT}^{\cos \phi_S} \ .
+  g_1 &= \frac{1}{2x_B} F_{LL} \\
+  g_2+g_1 &= - \frac{Q}{4 x_B^2 M} F_{LT}^{\cos \phi_S} \ .
 \end{align}
-% \begin{align}
-% g_1&=\frac12 \sum_q e_q^2g_1^q \ , \\
-% g_2&=\frac12 \sum_q e_q^2(g_T^q-g_1^q) \ .
-% \end{align}
-Utilizing Equations of Motion and Lorentz Invariance relations as discussed in Ref.~\cite{Accardi:2009au}, we arrive at
+Utilizing equations of motion and Lorentz invariance relations as discussed in Ref.~\cite{Accardi:2009au} to decompose $g_T$ into ``pure twist-3'' and twist-2 pieces, we arrive at
 \begin{align}
@@
     + \int_\xbj^1\frac{dy}{y} \widehat{g}_T^q(y) 
-    + \frac{\mq}{\Lambda} \left(\frac{h_1^q}{x}\right)^\star(\xbj) 
-    + \frac{\mj-\mq}{\Lambda} \frac{h_1^q(\xbj)}{\xbj} 
+    + \frac{\mq}{M} \left(\frac{h_1^q}{x}\right)^\star(\xbj) 
+    + \frac{\mj-\mq}{M} \frac{h_1^q(\xbj)}{\xbj} 
 \Biggr) \ ,
@@
 g_2^{\text{quark}} &= \frac{1}{2}\,\sum_q e_q^2 
- \frac{\mq}{\Lambda} \bigg( \frac{h_1^q}{x} \bigg)^\star\!\!(\xbj) \ ,
+ \frac{\mq}{M} \bigg( \frac{h_1^q}{x} \bigg)^\star\!\!(\xbj) \ ,
 \\
 g_2^{\text{jet}} &= \frac{1}{2}\,\sum_q e_q^2 
-\frac{\mj-\mq}{\Lambda} \frac{h_1^q(\xbj)}{\xbj} \ .
+\frac{\mj-\mq}{M} \frac{h_1^q(\xbj)}{\xbj} \ .
 \nonumber 
@@
 values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV.
-%\AAcom{Did we really use 100 MeV in teh plots? I seem to remember 50 MeV.}
 
@@
 \begin{center}
-\includegraphics[width=8cm]{g2contrib.pdf}
-\includegraphics[width=8cm]{g2contribN.pdf}
+\includegraphics[width=8cm]{g2contrib}
+\includegraphics[width=8cm]{g2contribN}
 \caption{\label{f:g2contrib} 
@@
   & = \frac12 \sum_q e_q^2 \bigg[ N \tilde g_T^q[N] + \hat g_T^q[N]  
-    + \frac{(N+1) \mj- \mq}{\Lambda} h_1^q[N-1] \bigg] \ .
+    + \frac{(N+1) \mj- \mq}{M} h_1^q[N-1] \bigg] \ .
 \end{align}
@@
   \label{eq:BC}
-  \int dx\, g_2(x) = \sum_q e_q^2 \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1^q(x) \ .
+  \int dx\, g_2(x) = \sum_q e_q^2 \frac{\mj-\mq}{M} \int dx\, \frac{1}{x} h_1^q(x) \ .
 \end{align}
-Here we used the fact that $\widehat g_T^q[0]$ vanishes identically due to the symmetry properties of the quark-gluon-quark correlators \cite{Accardi:2009au}.
-%, or equivalently as a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. 
-%
-Note that all pure twist-3 terms have explicitly disappeared, and the only surviving term on the right-hand side is the new jet contribution. Thus, our new sum rule \eqref{eq:BC}
+Assuming $M_\text{light}\equiv M_u -m_u \approx M_d -m_d$ and dominance of light quarks in the sum over flavors, we can also write
+\begin{align}
+  \label{eq:BC-sfn}
+  \int dx\, g_2(x) = \frac{M_\text{light}}{M} \int dx\, \frac{h_1(x)}{x} \ ,
+\end{align}
+with $h_1$ the transversity structure function.
+
+In Eq.~\eqref{eq:BC}, we used the fact that $\widehat g_T^q[0]$ vanishes identically due to the symmetry properties of the quark-gluon-quark correlators \cite{Accardi:2009au}.
+Therefore all pure twist-3 terms have explicitly disappeared, and the only surviving term on the right-hand side is the new jet contribution.
+Thus, our new sum rule \eqref{eq:BC}
 generalizes the Burkhardt--Cottingham (BC) sum rule~\cite{Burkhardt:1970ti},
@@
 BC sum rule is if
-%that is derived at the cross section level (under suitable assumptions on the
-%high-energy behavior of te hspin-flip amplitude) rather than from an analysis
-%of collinear correlators, as done here, 
-%to be strictly valid, we obtain a
-%strong constraint on the transversity function, 
 $
@@
   d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1] 
-    + \frac{2\mj-\mq}{\Lambda} h_1^q[0] \bigg)
+    + \frac{2\mj-\mq}{M} h_1^q[0] \bigg)
 \label{e:d1}
@@
   d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2] 
-    + \frac{3\mj-\mq}{\Lambda} h_1^q[1] \bigg) \ ,
+    + \frac{3\mj-\mq}{M} h_1^q[1] \bigg) \ ,
 \end{align}
@@
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} 
-%\AAcom{Check the $q+\bar q$ vs. $q-\bar q$ issue for lattice moments discussed in Oxford}
 or fitted \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
-Furthermore, 
-%the new sum rule \eqref{eq:ABsumrule} and 
-the bound
+Furthermore, the bound
 \eqref{eq:ABbound} promises to improve future transversity fits. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
@@
 A promising avenue is through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
-production from the same hemisphere, $e^+ e^- \to h h X$, see 
-Fig.~\ref{fig:epl_emn_h}.
-%\AAcom{Andrea suggested to remove teh figures, to avoid competitors stealing our idea and doing the actual analysis of te hobservables sensitive to $M_q$.
-I see his point, but am a bit torn about this.}
+production from the same hemisphere, $e^+ e^- \to h h X$, see~Fig.\ref{fig:epl_emn_h}.
 In single-hadron production, the fragmentation functions 
@@
   }
-  \label{fig:epl_emn_h.eps}
+  \label{fig:epl_emn_h}
 \end{figure}
@@
 \begin{align}
-  d_1^V = \frac12 \sum_q e_q^2 \frac{2\mj- \mq}{\Lambda} 
+  d_1^V = \frac12 \sum_q e_q^2 \frac{2\mj- \mq}{M} 
     \big(h_1^{q}[0]-h_1^{\bar q}[0]\big) \ .
 \end{align}
-Assuming $M_\text{light}\equiv M_u \approx M_d \gg m_u , m_d$ and isospin symmetry of the proton and neutron, we can also see that 
+Assuming again dominance of light flavors, we can also see that 
 \begin{align}
-  d_1^V = \frac{M_{\text{light}}}{\Lambda} \delta_T(p) \ ,   
+  d_1^V = \frac{M_{\text{light}}}{M} \delta_T(p) \ ,   
 \end{align}
 This gives an alternative way to access the proton tensor charge, $\delta_T(p) = \sum_q e_q^2 \big(h_1^{q}[0]-h_1^{\bar q}[0]\big)$, by measuring or fitting moments of the flavor separated $g_2$ structure function.
-%\AAcom{I tried to build an observable for $d_1^V$ such as $p-n$ or $p-\bar p$, but I am messing up a bit.}
 
@@
 correlator that corresponds, up to twist-4 contributions, to the nonperturbative quark cut propagator, or, equivalently, to the quark's spectral function, and of a quark-gluon-quark jet correlator needed to insure gauge invariance of the calculation.
-%different from the standard perturbative propagator. 
 We then carried out the analysis of
-%the jet correlator and 
 the DIS cross section up to contribution of order $1/Q$. 
@@
 
-%\ \\ \AAcom{NOTE: the umlauts do not show up in the bibliography!! See, e.g., reference [5]. Need to fix!}
-
 \bibliographystyle{myrevtex}

### 2017-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
Draft mods in v1, after referee report

@@
 \def\AAcom#1{{\bf  \textcolor{Red}{[AA: {#1}]}}}
-\def\AAmod#1{{\textcolor{Green}{#1}}}
+\def\AAmod#1{{\textcolor{Red}{#1}}}
 
@@
 \affiliation{
-$^a$Hampton University, Hampton, VA 23668, USA,
-and Jefferson Lab, Newport News, VA 23606, USA \\
+$^a$Hampton University, Hampton, VA 23668, USA, and Jefferson Lab, Newport News, VA 23606, USA \\
 $^b$Dipartimento di Fisica, Universit\`a degli Studi di Pavia, and INFN,
@@
 associated with the invariant mass of the produced hadrons is generated
-non perturbatively and couples to the target's transversity distribution
+nonperturbatively and couples to the target's transversity distribution
 function. In inclusive cross sections, this provides an hitherto neglected and
@@
 can explain the discrepancy between recent calculations and fits of this
-quantity.
-It also provides an extension of the Burkhardt--Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
+quantity.  It also provides an extension of the Burkhardt--Cottingham sum rule, \AAmod{
+  %putting constraints
+  providing new information}
+on the small-$x$ behavior of the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
 \end{abstract}
@@
 
-The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a non perturbative mass of order 100 MeV, much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes.
+The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a nonperturbative mass
+\AAmod{
+  % of order 100 MeV
+  estimated in the 10-100 MeV range},
+much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes.
 Here, we formalize this idea in the context of collinear factorization, and observe that jet correlators introduce a new
@@
 (a) it violates the Wandzura--Wilczek relation;
-(b) it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution;
+(b) it extends the Burkhardt--Cottingham sum rule, providing
+\AAmod{
+  %a useful bound
+  useful information}  
+on the small-$x$ behavior of the transversity distribution;
 (c) it also extends the Efremov--Teryaev--Leader sum rule, providing a novel way to measure the proton's tensor charge.
@@
 where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
-It is important to notice that while $\xi_2=1$ exactly due to CPT invariance
-(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
+
+\AAmod{
+% It is important to notice that while $\xi_2=1$ exactly due to CPT invariance
+% (see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass
+% $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
 From the analytic properties of the spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$ with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects.
 Taking into account that $J_1 < J_2$, we may therefore estimate
+% \begin{align}
+%   \label{eq:mjet}
+%   \mj = {\cal O}(100 \text{\ MeV}) \ .
+% \end{align}
+It is important to notice that, while $\xi_2=1$ exactly due to CPT invariance
+(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass
+$\mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
+From the analytic properties of the spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$ with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects, indicating $M_q=O(\Lambda_{QCD})$.
+However, in a dynamical confinement scenario, the spectral function $J_2$ needs not be positive definite \cite{Roberts:2016vyn} and we therefore estimate
 \begin{align}
-  \label{eq:mjet}
-  \mj = {\cal O}(100 \text{\ MeV}) \ .
+  M_q\sim 10-100 \text{\ MeV}.
 \end{align}
+An experimental measurement of $M_q$ is anyway possible, as we discuss in Sections~\ref{sec:moments}, and could shed light on the confinement mechanism.
+We have also explicitly verified that $M_q>m_q$ in a model where quark fragmentation is simulated by a Yukawa pseudoscalar quark-meson interaction.
+}
+
 Although $\mj$ is in general a nonperturbative quantity, it is interesting to
@@
 where $\mq$ is the current quark mass; therefore $\mj^\text{pert}=m_q$, and one recovers the result of the calculation with the conventional handbag diagram.
-However, we are here considering non perturbative effects
+However, we are here considering nonperturbative effects
 in the quark propagation, and $\mj \gg \mq$. 
@@
 This formula provides us with a
-non perturbative generalization of the commonly used $\int\tilde E =0$ sum
+nonperturbative generalization of the commonly used $\int\tilde E =0$ sum
 rule introduced in \cite{Jaffe:1996zw}. Indeed, calculating the jet correlator 
@@
 \section{The $g_2$ structure function}
+\label{sec:g2}
 
@@
 overall normalization uncertainty due to the choice of $\mj$, not shown in the
-plot.
-In any case, the jet-mass contribution is strikingly large, and of the same order of magnitude as the chiral-even twist 3 term.
+plot. In any case, the jet-mass contribution is strikingly large, and of the same order of magnitude as the chiral-even twist 3 term.
+
 If we assume the latter to be of the order of the model calculation
@@
 
-\begin{figure}[htb]
+\begin{figure}[tb]
 \begin{center}
@@
 \includegraphics[width=8cm]{g2contribN}
+\vskip-0.2cm
 \caption{\label{f:g2contrib} 
@@
 
-One should notice that since $h_1$ is slowly driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule is still satisfied at least
-asymptotically.
+One should notice that since $h_1$ is slowly driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule
+\AAmod{
+  %is still
+  may still be }
+satisfied at least asymptotically.
 At finite scales, however, the only way to preserve the validity of the
@@
 Interestingly, one can show that this constraint, if valid at any given scale
-$Q_0$ is conserved through QCD evolution.
-However, we think that it is unlikely to be satisfied in general, since it is explicitly broken in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
-Then, if we assume that the BC sum rule is broken by a {\em finite} amount we obtain that $h_1(x)/x$ must be integrable, which implies the following bound on the small $x$ behavior of the transversity:
-\begin{align}
-  h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
-\label{eq:ABbound}
-\end{align}
-This bound can be very useful, \eg, in transversity fits, where the data at
-small $x$ is, as yet, very limited, and in general for proper extrapolations
-to $x_B=0$ when experimentally measuring moments.
-We also note that the small-$x$ behavior of the longitudinal spin structure function $g_1$ has been recently investigated in Ref.~\cite{Kovchegov:2016zex}; it would be interesting to extend those techniques to the transverse spin structure functions $g_T=g_1+g_2$ and $h_1$.
+$Q_0$ is conserved through QCD evolution. However, we think that it is unlikely to be satisfied in general, since
+\AAmod{
+  %it is explicitly broken
+  the right hand side is different from zero}
+in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
+\AAmod{
+% Then, if we assume that the BC sum rule is broken by a {\em finite} amount we obtain that $h_1(x)/x$ must be integrable, which implies the following bound on the small $x$ behavior of the transversity:
+% \begin{align}
+%   h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
+% \label{eq:ABbound}
+% \end{align}
+% This bound can be very useful, \eg, in transversity fits, where the data at
+% small $x$ is, as yet, very limited, and in general for proper extrapolations
+% to $x_B=0$ when experimentally measuring moments.
+A finite breaking of the BC sum rule would imply that $h_1(x)/x$ must be integrable, which is possible only if, at small $x$, the transversity goes as $h_1^q(x) \propto x^\epsilon$ with $\epsilon>0$.
+While $\epsilon=1$ in perturbative QCD \cite{Hayashigaki:1997dn,Vogelsang:1997ak}, the leading Regge contribution at small $x$ indicates that $\epsilon = 0$  \cite{Kirschner:1996jj}, and opens the door to a more serious breaking of the sum rule.}
+Finally, we note that the small-$x$ behavior of the longitudinal spin structure function $g_1$ has been recently investigated in Ref.~\cite{Kovchegov:2016zex}; \AAmod{
+however, since the small $x$ structure of the $h_1$ function may be quite different from that of $g_1$ \cite{Kirschner:1996jj},}
+it would be interesting to extend those techniques to the transverse spin structure functions $g_T=g_1+g_2$ and $h_1$.
 
@@
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} 
-or fitted \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
-Furthermore, the bound
-\eqref{eq:ABbound} promises to improve future transversity fits. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
+or fitted \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa},
+\AAmod{
+% Furthermore, the bound
+% \eqref{eq:ABbound} promises to improve future transversity fits. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
+and information from the extended BC sum rule \eqref{eq:BC-sfn} promises to improve future transversity fits.
+Furthermore, as combined QCD fits of different distribution function have now become possible \cite{Ethier:2017zbq}, the jet mass $M_q$ could also be considered as a free parameter in a combined helicity and transversity PDF fit.
+Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
+}
 
 We should also note that the $\mj$ jet mass parameter can
-also be experimentally measured, \eg, in electron-positron collisions.
+be experimentally measured, \eg, in electron-positron collisions.
 A promising avenue is through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
-production from the same hemisphere, $e^+ e^- \to h h X$, see~Fig.\ref{fig:epl_emn_h}.
+production from the same hemisphere, $e^+ e^- \to h h X$, see~Fig.~\ref{fig:epl_emn_h}.
 In single-hadron production, the fragmentation functions 
@@
 leads to a difference in the expression of the structure function $g_2$ in
-inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter $\mj={\cal O}$(100 MeV)
+inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter
+\AAmod{ $\mj={\cal O}$(10-100 MeV) }
 and to the transversity distribution function. This new term
@@
 Burkhardt--Cottingham and Efremov--Teryaev--Leader sum rules. This is yet another example of how surprising
-and rich the phenomenology of polarized inclusive DIS can be.
+and rich the phenomenology of polarized inclusive DIS can be,
+\AAmod{that offers a new direction for theoretical studies and experimental investigations of spin physics over a wide range in $x$, from the valence and sea regions at Jefferson Lab \cite{Dudek:2012vr} to the small-$x$ region at the future Electron-Ion Collider \cite{Accardi:2012qut}.}
 

### 2017-07-26 1607 - JMC for g2/Paper/Reply_to_Referee.txt
Reply to referee v1.1

We thank the reviewer for the thoughtful comments and questions about our work, that we have carefully considered and incorporated in the revised version of our paper. In the following, we comment upon each point raised by the reviewer, and refer to the appropriate place in the text where major changes have occurred. (As the numbering of the equations has changed slightly in the revision, in our answers we refer to the new numbering.) We are confident the new version wil satsify the Referee, but will be glad to make further improvements should teh discusssions need to be clarified further.

> 1. The new term, the last term in Eq. (21), has the non-perturbative
> mass scale M_q and the (perturbative) current quark mass m_q come in
> on the same footing. Have the authors tried to verify their
> conclusions in an explicit calculation? For instance, perhaps
> calculating the correlator \Xi from (4) in some non-perturbative model
> may help illustrate the fact that M_q - m_q is in fact non-zero.

We have indeed checked the behavior of the Mq term in a model with a pseudoscalar Yukawa interaction modeling the uark fragmentation process. This clearly show that Mq>mq. We added a comment to this effect at the end of Section II together with a revised discussion of the estimate of the magnitude of Mq, see next.

> 2. If I understood the arguments above Eq. (9) correctly,
> strictly-speaking the conclusion there is that M_q < O (100 MeV), not
> equal to O (100 MeV) as Eq. (9) has. In fact, {\bar J}_2 can be very
> small as far as one can tell, leading to M_q = m_q. Some
> clarifications would help here.

The Referee is right in noticing that nothing a pripori prevents Mq to become smaller than ~100 MeV. Our estimate was based on the fact that one can expect the two-particle continuum to open up at (mq+m_pi)~m_pi~Lambda_QCD, and therefore the value of mu averaged over the J2 distribution should be around our originally quoted value. We have revised this estimate taking also into acocunt that a quark is in fact not a physical asymptotic state, and Mq could be smaller than that, and now quotw Mq~10-100 MeV.

Note that, having exactly Mq=mq would imply the existence of a so far unknown symmetry or otherwise general constraint that would be extremely interesting on its own. Although we judge this unlikely, our paper may, if nothing else, encourage people to prove us wrong and discover a new feature of QCD.

The modified discussion, incorporating alsocomment #1, can be found at the end of Section II.

> 3. The sum rule (31) raises the question of whether the integral on
> its right-hand side is finite. It is hard for me to imagine a
> realistic scenario in which it is. In perturbation theory unpolarized
> TMDs at small x scale as (1/x)^{1+\epsilon_1}, where \epsilon_1 is an
> order-\alpha_s positive perturbative correction, while 1 in the power
> is ultimately determined by the gluon spin =1. Some polarized TMDs,
> such as helicity, scale as (1/x)^{\epsilon_2} at small x with
> \epsilon_2 an order-\sqrt{\alpha_s} positive perturbative correction,
> as found e.g. in Ref. [41]. Note that neither of those behaviors gives
> a finite right-hand side of (31). The scenario considered by the
> authors in Eq. (32) corresponds to negative \epsilon_2: while I know
> of no theorem requiring \epsilon_2 > 0, I also know of no perturbative
> calculation where \epsilon_2 < 0 either. (Furthermore, in N=4 SYM
> theory, where the unpolarized intercept is known to a very high order
> in perturbation theory, the series in \alpha_s changes sign only every
> other term, see Eq. (5.1) in 1504.06640.) Saturation effects at very
> low x can at most effectively put \epsilon_2 =0, still not making the
> right-hand side of (31) finite... So, as a friendly colleague I urge
> the authors to rethink their conclusions very carefully.

We agree with the referee, and in fact our original discussion was somewhat confusing. We have enlarged teh scope of the discussion and reviewed some perturbative and resummed results on the small x behavior of h1. The small-x physics of the h1 function in comparison to g1 is indeed an interesting topic of research, that can now also be accessed experimentally thanks to our extended WW and BC relations.

The modified discussion can be found in teh paragraph above Eq.()

> 4. Here are some minor corrections:
>
> -- Ref. [22] has 3 authors, but only two are mentioned explicitly in
>    the text three lines above Eq. (1).
>
> -- The kinematics of the diagrams in Fig. 1 is not defined: e.g., is
>    the proton moving in the light-cone "+" or "-" direction? This is
>    needed to better understand the discussion between Eqs. (6) and
>    (7).
>
> -- The equation in the text two lines above Eq. (9) should have m_q^2
>    (instead of m_q) inside the delta-function.

We thank the referee also for this level of attention to our work, that has indeed helped us to improve the article.

### 2017-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
Reply to referee v1.1

--- 2017-07-10 1607 - JMC for g2/Paper/JMC_dis.tex
@@
 can explain the discrepancy between recent calculations and fits of this
-quantity.
-It also provides an extension of the Burkhardt--Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
+quantity.  It also provides an extension of the Burkhardt--Cottingham sum rule, 
+providing new information on the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
 \end{abstract}
@@
 
-The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a non perturbative mass of order 100 MeV, much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes.
+The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a nonperturbative mass
+estimated in the 10-100 MeV range, potentially
+much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes.
 Here, we formalize this idea in the context of collinear factorization, and observe that jet correlators introduce a new
@@
 (a) it violates the Wandzura--Wilczek relation;
-(b) it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution;
+(b) it extends the Burkhardt--Cottingham sum rule, providing new useful information on behavior of the transversity distribution;
 (c) it also extends the Efremov--Teryaev--Leader sum rule, providing a novel way to measure the proton's tensor charge.
@@
 Accardi and Qiu \cite{Accardi:2008ne} have introduced in the LO handbag diagram 
-a ``jet correlator'', also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph}, that accounts for invariant mass production in the current region and ensures that leading twist calculations in collinear factorization are consistent with the $x_B<1$ requirement imposed by baryon number conservation.
+a ``jet correlator'', also called ``jet factor'' by Collins, Rogers, and Stasto in Ref.~\cite{Collins:2007ph}, that accounts for invariant mass production in the current region and ensures that leading twist calculations in collinear factorization are consistent with the $x_B<1$ requirement imposed by baryon number conservation.
 \cite{Accardi:2008ne}.
@@
   \caption{Diagrams contributing to inclusive DIS scattering up to twist-3, including a jet correlator in the top part.
-Note the gluon attaches to both the nucleon and jet correlators.
-The Hermitian conjugates of diagrams (b) and (c), i.e., with gluons attaching to the right of the cut, are not shown.
+The proton is moving dominantly in the light-cone plus direction, and the jet in the minus direction.
+In diagrams (b) and (c), the gluon attaches to both the nucleon and jet correlators.
+The Hermitian conjugates of these two diagrams, i.e., with gluons attaching to the right of the cut, are not shown.
   }
@@
 where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
-It is important to notice that while $\xi_2=1$ exactly due to CPT invariance
-(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined.
-From the analytic properties of the spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$ with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects.
-Taking into account that $J_1 < J_2$, we may therefore estimate
+
+It is important to notice that, while $\xi_2=1$ exactly due to CPT invariance
+(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass
+$\mj < \int d\mu^2 \mu \, J_2(\mu^2)$ is dynamically determined.
+From the analytic properties of the spectral functions we expect that $J_2(\mu^2) = Z \delta(\mu^2-m_q^2) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$, with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects, indicating $M_q=O(\Lambda_{QCD})$.
+However, in a dynamical confinement scenario, the spectral function $J_2$ needs not be positive definite \cite{Roberts:2016vyn} and we therefore estimate
+$
+  M_q\sim 10-100 \text{\ MeV}.
+$
+An experimental measurement of $M_q$ is anyway possible, as we discuss in Section~\ref{sec:moments}, and could shed some light on the confinement mechanism.
+We have also explicitly verified that $M_q>m_q$ in a model where quark fragmentation is simulated by a Yukawa pseudoscalar quark-meson interaction, already utilized, {\it e.g.}, in Ref.~\cite{Bacchetta:2001di}.
+
+Although $\mj$ is in general a nonperturbative quantity, it is interesting to
+notice that on the perturbative vacuum
 \begin{align}
-  \label{eq:mjet}
-  \mj = {\cal O}(100 \text{\ MeV}) \ .
+  \Xi^{\text{pert}}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + {\cal O}(\alpha_s) \ ,
 \end{align}
-Although $\mj$ is in general a nonperturbative quantity, it is interesting to
-notice that on the perturbative vacuum, 
-\begin{align*}
-  \Xi^\text{pert}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + {\cal O}(\alpha_s) \ ,
-\end{align*}
 where $\mq$ is the current quark mass; therefore $\mj^\text{pert}=m_q$, and one recovers the result of the calculation with the conventional handbag diagram.
-However, we are here considering non perturbative effects
+However, we are here considering nonperturbative effects
 in the quark propagation, and $\mj \gg \mq$. 
@@
 
-One should notice that since $h_1$ is slowly driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule is still satisfied at least
-asymptotically.
-At finite scales, however, the only way to preserve the validity of the
-BC sum rule is if
+One should notice that since $h_1$ is slowly driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule may still be satisfied at least asymptotically.
+At finite scales, however, the only way to preserve the validity of the BC sum rule is if
 $
@@
 Interestingly, one can show that this constraint, if valid at any given scale
-$Q_0$ is conserved through QCD evolution.
-However, we think that it is unlikely to be satisfied in general, since it is explicitly broken in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
-Then, if we assume that the BC sum rule is broken by a {\em finite} amount we obtain that $h_1(x)/x$ must be integrable, which implies the following bound on the small $x$ behavior of the transversity:
-\begin{align}
-  h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
-\label{eq:ABbound}
-\end{align}
-This bound can be very useful, \eg, in transversity fits, where the data at
-small $x$ is, as yet, very limited, and in general for proper extrapolations
-to $x_B=0$ when experimentally measuring moments.
-We also note that the small-$x$ behavior of the longitudinal spin structure function $g_1$ has been recently investigated in Ref.~\cite{Kovchegov:2016zex}; it would be interesting to extend those techniques to the transverse spin structure functions $g_T=g_1+g_2$ and $h_1$.
+$Q_0$, is conserved through QCD evolution. However, we think that it is unlikely to be satisfied in general, since the right hand side is different from zero
+in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
+A finite breaking of the BC sum rule would imply that $h_1(x)/x$ must be integrable, which is possible only if, at small $x$, the transversity goes as $h_1^q(x) \propto x^\epsilon$ with $\epsilon>0$.
+While $\epsilon=1$ in perturbative QCD \cite{Hayashigaki:1997dn,Vogelsang:1997ak}, the leading Regge contribution at small $x$ indicates that $\epsilon = 0$  \cite{Kirschner:1996jj}, and opens the door to a more drastic breaking of the sum rule.
+Finally, we note that the small-$x$ behavior of the longitudinal spin structure function $g_1$ has been recently studied in Ref.~\cite{Kovchegov:2016zex}; however, since the small $x$ structure of the $h_1$ function may be quite different from that of $g_1$ \cite{Kirschner:1996jj},
+it would be interesting to extend those techniques to the transverse spin structure functions $g_T=g_1+g_2$ and $h_1$, and investigate their role in the breaking of the BC sum rule.
 
@@
 \cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} 
-or fitted \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
-Furthermore, the bound
-\eqref{eq:ABbound} promises to improve future transversity fits. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
+or extracted form experimental data \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa},
+and information from the extended BC sum rule \eqref{eq:BC-sfn} promises to improve future transversity fits.
+Furthermore, as combined QCD fits of different distribution functions have now become possible \cite{Ethier:2017zbq}, the jet mass $M_q$ could also be considered as a free parameter in a combined helicity and transversity PDF fit.
+Therefore the pure twist-3 part can, in principle, be properly isolated and measured.
 
 We should also note that the $\mj$ jet mass parameter can
-also be experimentally measured, \eg, in electron-positron collisions.
+be experimentally measured, \eg, in electron-positron collisions.
 A promising avenue is through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
-production from the same hemisphere, $e^+ e^- \to h h X$, see~Fig.\ref{fig:epl_emn_h}.
+production from the same hemisphere, $e^+ e^- \to h h X$, see~Fig.~\ref{fig:epl_emn_h}.
 In single-hadron production, the fragmentation functions 
@@
 leads to a difference in the expression of the structure function $g_2$ in
-inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter $\mj={\cal O}$(100 MeV)
+inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter $\mj={\cal O}$(10-100 MeV)
 and to the transversity distribution function. This new term
@@
 Burkhardt--Cottingham and Efremov--Teryaev--Leader sum rules. This is yet another example of how surprising
-and rich the phenomenology of polarized inclusive DIS can be.
+and rich the phenomenology of polarized inclusive DIS can be,
+and offers a new direction for theoretical studies and experimental investigations of spin physics over a wide range in $x$, from the valence and sea regions at Jefferson Lab \cite{Dudek:2012vr} to the small-$x$ region at the future Electron-Ion Collider \cite{Accardi:2012qut}.
 

### 2017-07-28 1607 - JMC for g2/Paper/Reply_to_Referee.txt
PLB resubmission material

@@
-We thank the reviewer for the thoughtful comments and questions about our work, that we have carefully considered and incorporated in the revised version of our paper.
+​We thank the reviewer for the thoughtful comments and questions about our work, that we have carefully considered and incorporated in the revised version of our paper.
 In the following, we comment upon each point raised by the reviewer, and refer to the appropriate place in the text where major changes have occurred.
-(As the numbering of the equations has changed slightly in the revision, in our answers we refer to the new numbering.) We are confident the new version wil satsify the Referee, but will be glad to make further improvements should teh discusssions need to be clarified further.
+(As the numbering of the equations has changed slightly in the revision, in our answers we refer to the new numbering.) We are confident the new version will satisfy the Referee, but will be glad to make further improvements if needed.
 
@@
 
-We have indeed checked the behavior of the Mq term in a model with a pseudoscalar Yukawa interaction modeling the uark fragmentation process.
-This clearly show that Mq>mq.
+We have indeed checked the behavior of the Mq term in a model with a pseudoscalar Yukawa interaction modeling the quark fragmentation process (see Ref.
+[28]).
+This clearly shows that Mq>mq.
 We added a comment to this effect at the end of Section II together with a revised discussion of the estimate of the magnitude of Mq, see next.
@@
 
-The Referee is right in noticing that nothing a pripori prevents Mq to become smaller than ~100 MeV.
+The Referee is right in noticing that nothing a priori prevents Mq to become smaller than ~100 MeV.
 Our estimate was based on the fact that one can expect the two-particle continuum to open up at (mq+m_pi)~m_pi~Lambda_QCD, and therefore the value of mu averaged over the J2 distribution should be around our originally quoted value.
-We have revised this estimate taking also into acocunt that a quark is in fact not a physical asymptotic state, and Mq could be smaller than that, and now quotw Mq~10-100 MeV.
+We have revised this estimate taking also into account that a quark is in fact not a physical asymptotic state, and Mq could be smaller than that, and now quote Mq~10-100 MeV.
 
-Note that, having exactly Mq=mq would imply the existence of a so far unknown symmetry or otherwise general constraint that would be extremely interesting on its own.
-Although we judge this unlikely, our paper may, if nothing else, encourage people to prove us wrong and discover a new feature of QCD.
+Note that having exactly Mq=mq would imply the existence of a so far unknown symmetry or otherwise general constraint that would be extremely interesting on its own.
+Although we judge this unlikely, our paper may, if nothing else, ​​​encourage people to prove us wrong and discover a new feature of QCD.
 
-The modified discussion, incorporating alsocomment #1, can be found at the end of Section II.
+The modified discussion, incorporating also comment #1, can be found at the end of Section II.
 
@@
 We agree with the referee, and in fact our original discussion was somewhat confusing.
-We have enlarged teh scope of the discussion and reviewed some perturbative and resummed results on the small x behavior of h1.
-The small-x physics of the h1 function in comparison to g1 is indeed an interesting topic of research, that can now also be accessed experimentally thanks to our extended WW and BC relations.
+We have extended the scope of the discussion and reviewed some perturbative and resummed results on the small x behavior of h1.
+The small-x physics of the h1 function in comparison to g1 is indeed an interesting topic of research, that can now also be accessed experimentally ​in a new way thanks to our extended WW and BC relations.
 
-The modified discussion can be found in teh paragraph above Eq.()
+The modified discussion can be found in the paragraph above Eq.(32).
 
@@
 
-We thank the referee also for this level of attention to our work, that has indeed helped us to improve the article.
+We thank the referee also for this level of attention to our work, that has indeed helped us improving the article.​ The kinematic has been described in the caption of Figure 1, and the other two typos corrected.​

### 2017-09-11 1607 - JMC for g2/Paper/JMC_dis.tex
Corrected to published version; as resubmitted to arXiv.

@@
 The tensor charge is a fundamental property of the nucleon that is at
-present poorly constrained but of fundamental importance, not the least because its knowledge can also be used to put constraints on searches for physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
+present poorly constrained but of fundamental importance, not the least because its knowledge can also be used to put constraints on searches for physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa,Tomalak:2017owk,Yamanaka:2017mef}.
 The tensor charge has been estimated in lattice QCD (see, \eg,
@@
   \Xi(l) =  
-  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu\,\id + J_2 (\mu^2)\,\lslash \big] \,
-  \delta(l^2 -\mu^2) \ ,
+  \int d \sigma^2 \big[ J_1 (\sigma^2)\,\sigma\,\id + J_2 (\sigma^2)\,\lslash \big] \,
+  \delta(l^2 -\sigma^2) \ ,
 \label{e:jetspectral}
 \end{align}
-where $\mu^2$ can be interpreted as the invariant mass of the current jet, {\it
+where $\sigma^2$ can be interpreted as the invariant mass of the current jet, {\it
   i.e.}, of the particles going through the cut in the top blob of
@@
 \begin{align}
-  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
+  J_2(\sigma^2) \geq J_1(\sigma^2) \geq 0
   \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
-  \int d\mu^2 J_2(\mu^2) = 1 \ .
+  \int d\sigma^2 J_2(\sigma^2) = 1 \ .
 \label{eq:jetfnsprops}
@@
 \begin{align}
-\xi_1 &= \int d\mu^2 \frac{\mu}{\Lambda} J_1(\mu^2) 
+\xi_1 &= \int d\sigma^2 \frac{\sigma}{\Lambda} J_1(\sigma^2) 
        \equiv \frac{\mj}{\Lambda},
 &
-\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ ,
+\xi_2 &= \int d\sigma^2 J_2(\sigma^2) = 1 \ ,
 \end{align} 
@@
 (see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass
-$\mj < \int d\mu^2 \mu \, J_2(\mu^2)$ is dynamically determined.
-From the analytic properties of the spectral functions we expect that $J_2(\mu^2) = Z \delta(\mu^2-m_q^2) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$, with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects, indicating $M_q=O(\Lambda_{QCD})$.
+$\mj < \int d\sigma^2 \sigma \, J_2(\sigma^2)$ is dynamically determined.
+From the analytic properties of the spectral functions we expect that $J_2(\sigma^2) = Z \delta(\sigma^2-m_q^2) + \bar J_2(\sigma^2) \theta (\sigma^2-m_\pi^2)$, with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects, indicating $M_q=O(\Lambda_{QCD})$.
 However, in a dynamical confinement scenario, the spectral function $J_2$ needs not be positive definite \cite{Roberts:2016vyn} and we therefore estimate
@@
 Measurements in the asymptotically large $Q^2$ regime will provide access to the integral of the $J_1$ jet function, i.e., to the jet-mass parameter $\mj$, and therefore (in conjunction with precise measurements or lattice QCD calculations of the first $h_1$ moment) also of the target's tensor charge through the modified ETL sum rule.
-Equally interesting is the possibility to experimentally measure, at finite values of $Q^2$, the momentum dependence of the jet functions $J_1$ and $J_2$, that enter structure functions integrated only up to $\mu^2=Q^2(1/x_B-1)$~\cite{Accardi:2008ne}.
+Equally interesting is the possibility to experimentally measure, at finite values of $Q^2$, the momentum dependence of the jet functions $J_1$ and $J_2$, that enter structure functions integrated only up to $\sigma^2=Q^2(1/x_B-1)$~\cite{Accardi:2008ne}.
 In other words, it may become possible to experimentally access also the quark's spectral function itself.
